### 2020-03-10 outline.tex
started outline

\section{Introduction}

\section{Dirichlet Series and Dirichlet Functors}

\begin{defn}
A \emph{Dirichlet functor} is a contraviariant functor $F : \Sa\op \to \Sa$
which (?is accessible and?) sends weakly contractible colimits to limits.

The category $\Dir$ of Dirichlet functors is the full subcategory of
$\Fun(\Sa\op,\, \Sa)$ spanned by the Dirichlet functors.
\end{defn}

\begin{defn}
A \emph{Dirichlet series} is a bundle $\pi : E \to B$ in $\Sa$. We think of this
as a family of homotopy types $E_b$ varying with $b : B$.

The category $\DirSeries$ is the arrow category $\Sa^{\downarrow}$ of $\Sa$.
\end{defn}

\begin{prop}
  There is a fully faithful inclusion $\bang_{(-)} : \Sa \to \DirSeries$ given by
  $$X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}$$
\end{prop}

\begin{defn}
To every Dirichlet series $\pi : E \to B$, we associate its \emph{extent}
$\term{ext}_{\pi} : \Sa\op \to \Sa$ given by
$$\term{ext}_{\pi}(S) :\equiv \DirSeries(\bang_S,\, \pi).$$
That is, $\term{ext} : \DirSeries \to \Fun(\Sa\op,\, \Sa)$ is the transpose of
$\DirSeries(\bang_{(-)}, -) : \Sa\op \times \DirSeries \to \Sa$.

In terms of type families, this is the functor
$$S \mapsto \sum_{b : B} E_b^S.$$
And it may be expressed as the composite
$$\Sa\op \xto{B^{\ast}\op} (\Sa_{/B})\op \xto{[-,\pi]} \Sa_{/B} \xto{B_{\ast}}
\Sa.$$
\end{defn}

\begin{prop}
The functor $\term{ext} : \DirSeries \to \Fun(\Sa\op,\, \Sa)$ has a left exact
left adjoint given by
$$D \mapsto \begin{tikzcd} D(\ast) \arrow[d, "D\bang_0"] \\ D(0) \end{tikzcd}$$
The counit of this adjunction is an equivalence, and so $\term{ext}$ is fully faithful.
\end{prop}
\begin{proof}
\emph{Idea:} Type-theoretically, we see that for $\pi : E \to B$,
\begin{align*}
  \term{ext}(\pi)(\ast) &= \sum_{b : B}E_b^\ast\\
  &\simeq \sum_{b : B} E_b\\
  &= E\\
  \term{ext}(\pi)(0) &= \sum_{b : B}E_b^0\\
  &\simeq \sum_{b : B} \ast\\
    &= B
\end{align*}
The counit is this evident equivalence. On the other hand, the unit can be
described by
\begin{align*}
  \eta_S : D(S) &\to \sum_{b : D(0)} D(1)^S\\
  z &\mapsto (D!_0(z), \lam{s} D\const_s(z)).
\end{align*}
\end{proof}

\begin{lem}\label{lem:cone.initial.equivalence}
Let $\Ca$ be an $\infty$-category with an initial object. For any simplicial set
$S$, let $\Ca^{S^{\triangleleft}}_{\ast}$ be the $\infty$-category of
  $S^{\triangleleft}$-shaped diagrams whose apex is at the initial object; that
  is, the following pullback:
  \[
    \begin{tikzcd}
      \Ca^{S} \arrow[drr, bend left] \arrow[ddr, bend right] \arrow[dr,
      dotted, "\sim"] & & \\
      & \Ca^{S^{\triangleleft}}_{\ast} \arrow[d] \arrow[r] \arrow[dr, phantom,
      "\ulcorner" very near start] & \Ca^{S^{\triangleleft}} \arrow[d,
      "\term{ev}_{\term{apex}}"] \\
      & \ast \arrow[r, "0"'] & \Ca
    \end{tikzcd}
  \]
The the dotted inclusion $\Ca^{S} \to \Ca^{S^{\triangleleft}}_{\ast}$ is an equivalence.
\end{lem}

\begin{lem}\label{lem:every.type.weakly.contractible.colimit}
  Every $S$ in $\Sa$ is the colimit of the diagram $S^{\triangleleft} \to \Sa$
sending the apex to $0$ and every other element to $\ast$; that is, the
composite
$$S^{\triangleleft} \xto{\bang^{\triangleleft}} \ast^{\triangleleft} \xto{0 \to
  1} \Sa.$$
\end{lem}
\begin{proof}
\emph{Idea:} By Lemma \label{lem:cone.initial.equivalence}, this diagram
corresponds to the terminal diagram $\ast : S \to \Sa$, and $S$ is well known to
be the colimit of this diagram (see Lurie, probably).
\end{proof}

\begin{thm}\label{thm:dirichlet.series.functors.equivalence}
  A contravariant functor is Dirichlet if and only if it is the extent of a
  Dirichlet series. That is, the adjunction $\term{ext} \dashv (-)\bang_0 : \DirSeries \leftrightarrows
  \Fun(\Sa\op,\, \Sa)$ restricts to an equivalence $\DirSeries \simeq \Dir$. As
  a corollary, $\Dir$ is an $\infty$-topos
\end{thm}
\begin{proof}
  First, we show that the extent of a Dirichlet series is a Dirichlet functor.
  \emph{Idea:} Weakly contractible limits commute with dependent sums. More
  fully: the extent of a Dirichlet series $\pi : E \to B$ can be expressed as
  the composite
  $$\Sa\op \xto{B^{\ast}\op} (\Sa_{/B})\op \xto{[-,\pi]} \Sa_{/B} \xto{B_{\ast}}
  \Sa.$$
  The first functor in this composite has both adjoints, and so in particular
  preserves all limits. The second is part of a two-variable adjunction, and so
  also preserves all limits. Finally, the last functor is the forgetful functor
  $\Sa_{/B} \to \Sa$, and by Lemma 2.2.7 of \cite{GHK:Analytic.Monads}, these
  functors always create weakly contractible limits.

  Now, we show that if a functor $D$ is Dirichlet, then the unit $D \Rightarrow
  \term{ext}_{D\bang_0}$ is an equivalence.
  \emph{Idea:} We note that every $S \in \Sa$ is the colimit of the diagram
  $S^{\triangleleft} \to \Sa$ sending the apex of the cone to $0$ and every
  element of $S$ to $\ast$ (see Lemma
  \ref{lem:every.type.weakly.contractible.colimit}). This is a weakly
  contractible colimit, and so it is preserved by $D$; therefore, $D(S)$ is the
  limit of the diagram
  $$S^{\triangleleft}\op \xto{\bang^{\triangleleft}\op}
  \ast^{\triangleleft}\op \xto{\bang_0\op} \Sa\op \xto{D} \Sa$$
  But so is $\DirSeries(!_S,\, D!_0)$.
\end{proof}

\section{Cartisian Morphisms of Dirichlet Series and Functors}

\begin{defn}
A map $\pi \to \pi'$ of Dirichlet series is \emph{cartesian} if it
is a pullback:
\[
  \begin{tikzcd}
    E \arrow[d, "\pi"'] \arrow[r] \arrow[dr, phantom, "\ulcorner" very near
    start] & E' \arrow[d, "\pi'"] \\
    B \arrow[r] & B'
  \end{tikzcd}
\]
We denote by $\DirSeries_{\term{Cart}}$ the $\infty$-category of Dirichlet
series and cartesian morphisms between them.

A natural transformation $F \Rightarrow F'$ is \emph{cartesian} if its
naturality squares are pullbacks. We denote by $\Fun_{\term{Cart}}(\Sa\op, \Sa)$
the $\infty$-category of (contravariant) functors and cartesian natural transformations.
\end{defn}

\begin{prop}
The equivalence of Theorem \ref{thm:dirichlet.series.functors.equivalence}
restricts to an equivalence
$$\Dir_{\term{Cart}} \simeq \DirSeries_{\term{Cart}}.$$
\end{prop}

\begin{thm}\label{thm:formal.mellin.transform}
We have an equivalence $\DirSeries_{\type{Cart}} \simeq
\type{PolyEnd}_{\type{Cart}}$ between the $\infty$-category of Dirichlet series
and cartesian morphisms and the $\infty$-category of polynomial endofunctors of
$\Sa$ and cartesian morphisms. This gives us an equivalence
$$\Dir_{\term{Cart}} \simeq \type{PolyEnd}_{\term{Cart}}$$
which we call the \emph{formal Mellin transform} -- since it can be seen as
acting on the ``basis'' of representables by
$$N^S \mapsto S^N.$$
\end{thm}
\begin{proof}
The $\infty$-category $\DirSeries_{\term{Cart}}$ is equivalent to the $\infty$-category
$\type{Poly}_{\term{Cart}}$ of $(\ast,\, \ast)$-polynomials, so this follows immediately from Proposition 2.4.13 of \cite{GHK:Analytic.Monads}.
\end{proof}

\begin{cor}
Let $D$ be a Dirichlet functor. Then the $\infty$-category $\Dir_{/_{\term{Cart}} D}$
(and equivalently the $\infty$-category $\DirSeries_{/_{\term{Cart}} D!_0}$ of
Dirichlet series cartesian over $D!_0$) of
Dirichlet functors cartesian over $D$ is an $\infty$-topos.
\end{cor}
\begin{proof}
  We note that
  $$\Dir_{/_{\term{Cart}} D} \simeq \Dir_{\term{Cart}/D}$$
  the $\infty$-category of Dirichlet functors cartesian over $D$ and the
  $\infty$-category of Dirichlet functors cartesian over $D$ an \emph{cartesian}
  natural transformations between them are equivalence by pullback pasting.
  Then, by Theorem \ref{thm:formal.mellin.transform}, we have an equivalence
  $$\Dir_{\term{Cart}/D} \simeq \type{PolyEnd}_{\term{Cart}/P}$$
  where $P$ is the formal Mellin transform of $D$. By Theorem 2.6.1 of
  \cite{GHK:Analytic.Monads}, $\type{PolyEnd}_{\term{Cart}/P}$ is an $\infty$-topos.
\end{proof}

\section{Ordinary, Extraordinary, and Exponential Dirichlet Series}

We will now consider a few restricted classes of Dirichlet series (and,
equivalently, Dirichlet functors). Each can be expressed as Dirichlet series
cartesian over a fixed series.
\[
  \begin{tabular}{|c|c|c|}
    \hline
    Name & Form & Base Series \\\hline\hline
    Exponential & $\displaystyle \sum_{n : \Nb} a_n\frac{n^{-s}}{n!}$ & $\type{FinTorsor} \to \type{FinGroup}$ \\ \hline
    Ordinary & $\displaystyle \sum_{n : \Nb} a_n n^{-s} $ & $\type{LocallyFin}_{0,\ast} \to \type{LocallyFin}_0$ \\ \hline
    Negative Exponential & $\displaystyle \sum_{n : \Nb} a_n \frac{n^s}{n!}$ & $\type{Fin}_{\ast} \to \type{Fin}$\\ \hline
  \end{tabular}
\]

\section{Characters and Dirichlet $L$-Functors}

\section{Functional Equations}

### 2020-03-13 outline.tex
small change

@@
   $$X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}$$
+  This functor preserves all limits and weakly contractible colimits
 \end{prop}
+\begin{proof}
+  This functor preserves all limits because it has a left adjoint given by sending $\pi : E \to B$ to $E$ (in terms of families, this sends the family $E_b$ to the sum $\sum_{b : B} E_b$).
+
+  To see that it preserves weakly contractible colimits, recall that colimits in $H^{\downarrow}$ are calculated pointwise. It remains to show, then, that the map
+  \[
+    \begin{tikzcd}
+    \colim S_i \arrow[r, equals] \arrow[d] & \colim S_i \arrow[d] \\
+    \colim \ast \arrow[r] & \ast 
+    \end{tikzcd}
+  \]
+  is an equivalence in $H^{\downarrow}$, for which it suffices to show that $\colim \ast$ is contractible.
+But the colimit of the terminal diagram is the (Kan-fibrant replacement of) its indexing simplicial set -- since we assumed the diagram was weakly contractible, $\colim \ast$ is contractible.
+\end{proof}
 

### 2020-03-29 outline.tex
updated outline

@@
 
+Before we come to the theory of Dirichlet series and Dirichlet functors, lets
+review the theory of polynomials and polynomial functors as developed by
+\cite{GHK:Analytic.Monads}.
+
+A \emph{polynomial functor} is a functor of the form
+\begin{equation}\label{eq:polynomial.functor.type.theoretic}
+X \mapsto \sum_{b : B}X^{E_b} : \Ha \to \Ha
+\end{equation}
+for some family of \emph{exponent} types $E_{(-)} : B \to \Type$ indexed by a
+homotopy type $B$. We refer to this family of exponents as the
+\emph{polynomial}, and the associated functor as its \emph{extent}. If the exponents $E_b$ are finite sets, then we can collect
+terms to express the value of this functor at a homotopy type $X$ (non-canonically) as
+$$\sum_{n : \Nb} B_n \times X^n \sslash n!$$
+which now looks like a power series in $X$. It is, however, much better to work
+with the ``coordinate-invariant'' presentation $\sum_{b : B} X^{E_b}$.
+
+The family of exponents $E_{(-)} : B \to \Type$ can also be expressed as the
+projection $\fst : \sum_{b : B} E_b \to B$ from its total space. Defining $E
+:\equiv \sum_{b : B} E_b$, we see that a \emph{polynomial} may equivalently be
+defined as a map $\pi : E \to B$ whose fibers are now seen as the exponents
+$E_b$. The extent if $\pi : E \to B$ may then be described as the composite
+$$\Ha \xto{E^{\ast}} \Ha_{/B} \xto{\pi_{\bang}} \Ha_{/B} \xto{B_{\ast}} \Ha$$
+
+A map between polynomials should induce a map between their extents. Seeing that
+the exponents $E_b$ occupy a contravariant position in the polynomial functor
+formula Eq. \ref{eq:polynomial.functor.type.theoretic}, we may define a morphism
+from $\pi : E \to B$ to $\pi' : E' \to B'$ to be a map $f : B \to B'$ on the
+indexing types, together with a fiberwise map $f_{\sharp} : \dprod{b : B} E'_{f
+  b} \to E_b$ going ``backwards'' on the exponents. In terms of the maps, this is a diagram of
+the form:
+\[
+  \begin{tikzcd}
+    E \arrow[d, "\pi"'] \arrow[r, leftarrow, "f_{\sharp}"] & \bullet \arrow[d] \arrow[r]
+    \arrow[dr, phantom, "\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
+    B \arrow[r, equals] & B \arrow[r, "f"'] & B'
+  \end{tikzcd}
+\]
+
+GHK characterize the functors which are the extents of polynomials, and show
+that this gives an equivalence of $\infty$-categories.
+\begin{thm}
+A functor $F : \Ha \to \Ha$ is the extent of a polynomial if and only if it is
+accessible and preserves weakly contractible limits.
+\end{thm}
+
+We will prove an analogous theorem in this section for the contravariant
+analogue of polynomial functors: Dirichlet functors. These are functors of the
+form
+$$S \mapsto \sum_{b : B} E_b^S$$
+for $E_{(-)} : B \to \Type$ a family of \emph{bases}. In Section
+\ref{sec:ordinary.dirichlet.series}, we will see how these functors categorify
+Dirichlet series. For now, we will prove the following theorem:
+\begin{thm}
+The category of Dirichlet functors $D : \Ha\op \to \Ha$ is equivalent to the
+category $\Ha^{\downarrow}$ of Dirichlet series. It is, in particular, an $\infty$-topos.
+\end{thm}
+
 \begin{defn}
-A \emph{Dirichlet functor} is a contraviariant functor $F : \Sa\op \to \Sa$
-which (?is accessible and?) sends weakly contractible colimits to limits.
+A \emph{Dirichlet functor} is a contraviariant functor $F : \Ha\op \to \Ha$
+which preserves weakly contractible limits.
 
 The category $\Dir$ of Dirichlet functors is the full subcategory of
-$\Fun(\Sa\op,\, \Sa)$ spanned by the Dirichlet functors.
+$\Fun(\Ha\op,\, \Ha)$ spanned by the Dirichlet functors.
 \end{defn}
@@
 \begin{defn}
-A \emph{Dirichlet series} is a bundle $\pi : E \to B$ in $\Sa$. We think of this
+A \emph{Dirichlet series} is a bundle $\pi : E \to B$ in $\Ha$. We think of this
 as a family of homotopy types $E_b$ varying with $b : B$.
 
-The category $\DirSeries$ is the arrow category $\Sa^{\downarrow}$ of $\Sa$.
+The category $\DirSeries$ is the arrow category $\Ha^{\downarrow}$ of $\Ha$.
 \end{defn}
@@
 \begin{prop}
-  There is a fully faithful inclusion $\bang_{(-)} : \Sa \to \DirSeries$ given by
-  $$X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}$$
-  This functor preserves all limits and weakly contractible colimits
+  There is an adjoint quintuple:
+  \[
+    \begin{tikzcd}
+      \Ha \arrow[r, "\const"] \arrow[r, leftarrow, shift left = 5,
+      "\term{cod}"] \arrow[r, leftarrow, shift right = 5, "\term{dom}"]
+      \arrow[r, shift left = 10, "!^{(-)}"]  \arrow[r, shift right = 10, "!_{(-)}"] & \Ha^{\downarrow}
+    \end{tikzcd}
+  \]
+  All of the functors $\Ha \to \Ha^{\downarrow}$ are fully faithful.
 \end{prop}
 \begin{proof}
-  This functor preserves all limits because it has a left adjoint given by sending $\pi : E \to B$ to $E$ (in terms of families, this sends the family $E_b$ to the sum $\sum_{b : B} E_b$).
+There is an adjoint triple $\begin{tikzcd} \ast \arrow[r,leftarrow] \arrow[r,
+  bend left] \arrow[r, bend right] & \downarrow \end{tikzcd}$. The middle three
+functors are given by restricting along this adjoint triple; the outer two are
+given by Kan extending, or more concretely:
+  $$X \mapsto \begin{tikzcd} 0 \arrow[d, "!^X"] \\ X \end{tikzcd}$$
+  $$X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}$$
+It is easy to see that the unit $X \to \term{dom} !_{X}$ is an equivalence (it is in
+fact an identity), so $!_{(-)}$ is fully faithful. Therefore, all the functors
+going from $\Ha \to \Ha^{\downarrow}$ are fully faithful.
+\end{proof}
 
-  To see that it preserves weakly contractible colimits, recall that colimits in $H^{\downarrow}$ are calculated pointwise. It remains to show, then, that the map
+\begin{prop}
+  The functor $!_{(-)}$ preserves weakly contractible colimits.
+\end{prop}
+\begin{proof}
+  To see that $!_{(-)}$ preserves weakly contractible colimits, recall that colimits in $H^{\downarrow}$ are calculated pointwise. It remains to show, then, that the map
   \[
@@
 To every Dirichlet series $\pi : E \to B$, we associate its \emph{extent}
-$\term{ext}_{\pi} : \Sa\op \to \Sa$ given by
+$\term{ext}_{\pi} : \Ha\op \to \Ha$ given by
 $$\term{ext}_{\pi}(S) :\equiv \DirSeries(\bang_S,\, \pi).$$
-That is, $\term{ext} : \DirSeries \to \Fun(\Sa\op,\, \Sa)$ is the transpose of
-$\DirSeries(\bang_{(-)}, -) : \Sa\op \times \DirSeries \to \Sa$.
+That is, $\term{ext} : \DirSeries \to \Fun(\Ha\op,\, \Ha)$ is the transpose of
+$\DirSeries(\bang_{(-)}, -) : \Ha\op \times \DirSeries \to \Ha$.
 
@@
 And it may be expressed as the composite
-$$\Sa\op \xto{B^{\ast}\op} (\Sa_{/B})\op \xto{[-,\pi]} \Sa_{/B} \xto{B_{\ast}}
-\Sa.$$
+$$\Ha\op \xto{B^{\ast}\op} (\Ha_{/B})\op \xto{[-,\pi]} \Ha_{/B} \xto{B_{\ast}}
+\Ha.$$
 \end{defn}
@@
 \begin{prop}
-The functor $\term{ext} : \DirSeries \to \Fun(\Sa\op,\, \Sa)$ has a left exact
+The functor $\term{ext} : \DirSeries \to \Fun(\Ha\op,\, \Ha)$ has a left exact
 left adjoint given by
@@
 \begin{lem}\label{lem:every.type.weakly.contractible.colimit}
-  Every $S$ in $\Sa$ is the colimit of the diagram $S^{\triangleleft} \to \Sa$
+  Every $S$ in $\Ha$ is the colimit of the diagram $S^{\triangleleft} \to \Ha$
 sending the apex to $0$ and every other element to $\ast$; that is, the
@@
 $$S^{\triangleleft} \xto{\bang^{\triangleleft}} \ast^{\triangleleft} \xto{0 \to
-  1} \Sa.$$
+  1} \Ha.$$
 \end{lem}
@@
 \emph{Idea:} By Lemma \label{lem:cone.initial.equivalence}, this diagram
-corresponds to the terminal diagram $\ast : S \to \Sa$, and $S$ is well known to
+corresponds to the terminal diagram $\ast : S \to \Ha$, and $S$ is well known to
 be the colimit of this diagram (see Lurie, probably).
@@
   Dirichlet series. That is, the adjunction $\term{ext} \dashv (-)\bang_0 : \DirSeries \leftrightarrows
-  \Fun(\Sa\op,\, \Sa)$ restricts to an equivalence $\DirSeries \simeq \Dir$. As
+  \Fun(\Ha\op,\, \Ha)$ restricts to an equivalence $\DirSeries \simeq \Dir$. As
   a corollary, $\Dir$ is an $\infty$-topos
@@
   the composite
-  $$\Sa\op \xto{B^{\ast}\op} (\Sa_{/B})\op \xto{[-,\pi]} \Sa_{/B} \xto{B_{\ast}}
-  \Sa.$$
+  $$\Ha\op \xto{B^{\ast}\op} (\Ha_{/B})\op \xto{[-,\pi]} \Ha_{/B} \xto{B_{\ast}}
+  \Ha.$$
   The first functor in this composite has both adjoints, and so in particular
@@
   also preserves all limits. Finally, the last functor is the forgetful functor
-  $\Sa_{/B} \to \Sa$, and by Lemma 2.2.7 of \cite{GHK:Analytic.Monads}, these
+  $\Ha_{/B} \to \Ha$, and by Lemma 2.2.7 of \cite{GHK:Analytic.Monads}, these
   functors always create weakly contractible limits.
@@
   \term{ext}_{D\bang_0}$ is an equivalence.
-  \emph{Idea:} We note that every $S \in \Sa$ is the colimit of the diagram
-  $S^{\triangleleft} \to \Sa$ sending the apex of the cone to $0$ and every
+  \emph{Idea:} We note that every $S \in \Ha$ is the colimit of the diagram
+  $S^{\triangleleft} \to \Ha$ sending the apex of the cone to $0$ and every
   element of $S$ to $\ast$ (see Lemma
@@
   $$S^{\triangleleft}\op \xto{\bang^{\triangleleft}\op}
-  \ast^{\triangleleft}\op \xto{\bang_0\op} \Sa\op \xto{D} \Sa$$
-  But so is $\DirSeries(!_S,\, D!_0)$.
+  \ast^{\triangleleft}\op \xto{\bang_0\op} \Ha\op \xto{D} \Ha$$
+  But so is $\DirSeries(!_S,\, D!_0)$, since
+  \begin{align*}
+    \DirSeries(!_S, D!_0) &=  \DirSeries(!_{\colim (S^{\triangleleft} \to \ast^{\triangleleft} \to \Ha)}, D!_0) \\
+    &\simeq \DirSeries(\colim (S^{\triangleleft} \to \ast^{\triangleleft} \to \Ha \xto{!_{(-)}} \DirSeries), D!_0) \\
+    &\simeq \lim (S^{\triangleleft}\op \xto{\bang^{\triangleleft}\op}
+  \ast^{\triangleleft}\op \xto{\bang_0\op} \Ha\op \xto{!_{(-)}} \DirSeries\op \xto{\DirSeries(-, D!_0)} \Ha)\\
+    &\simeq \lim (S^{\triangleleft}\op \xto{\bang^{\triangleleft}\op}
+  \ast^{\triangleleft}\op \xto{\bang_0\op} \Ha\op \xto{D} \Ha) 
+  \end{align*}
 \end{proof}
@@
 A natural transformation $F \Rightarrow F'$ is \emph{cartesian} if its
-naturality squares are pullbacks. We denote by $\Fun_{\term{Cart}}(\Sa\op, \Sa)$
+naturality squares are pullbacks. We denote by $\Fun_{\term{Cart}}(\Ha\op, \Ha)$
 the $\infty$-category of (contravariant) functors and cartesian natural transformations.
@@
 and cartesian morphisms and the $\infty$-category of polynomial endofunctors of
-$\Sa$ and cartesian morphisms. This gives us an equivalence
+$\Ha$ and cartesian morphisms. This gives us an equivalence
 $$\Dir_{\term{Cart}} \simeq \type{PolyEnd}_{\term{Cart}}$$

### 2020-03-31 draft.tex
added draft

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% First Intro
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

There are two basic sorts of generating functions in prevalent use in
combinatorics. There are the \emph{analytic} generating functions arising from power
series
$$\sum_{n \in \Nb} a_n x^n$$
and the \emph{Dirichlet} generating functions arising from Dirichlet series
$$\sum_{n \in \Nb} a_n n^{-s}.$$
The sequence of coefficients $a_n$ counts the amount of objects $A_n$ associated to an
$n$-element set $\underline{n} := \{0,\ldots, n-1\}$. For example, if $A_n$ is
the set of injections from $\underline{n}$ to $\underline{k}$, then $a_n = {k
  \choose n}$.

The power of the generating function formalism lies in way that algebraic and
analytic operations on the generating functions shadow combinatorial operations
on the sets that their coefficients count. This ``shadowing'' can be seen as an
instance of \emph{decategorification}. In his seminal paper \emph{Une
  th{\'e}orie combinatoire de s{\'e}ries formelles}
\cite{J:combinatorial.species}, Joyal defines a combinatorial species to be a
functor $A$ from the groupoid of finite sets and bijections to the category of
sets, assigning every set $\underline{n}$ a set $A_n$ isovariantly. One
associates a series to a combinatorial species by taking the cardinality of the
$A_n$ and from there derive a generating function. But one can proceed in
another way by first making a \emph{generating functor}\footnote{In truth, one
  derives what is known as an \emph{analtyic} functor from this operation, and
  not a polynomial functor. This is because one must also quotient by the action
  of the symmetric groups on $A_n$. This difficulty is rectified when passing to
  homotopy types, where analytic functors are polynomial due to the better
  behavior of homotopy colimits.}
 $$X \mapsto \sum_{n \in \Nb} A_n \times X^n$$
from the category of sets to itself, and then taking the action of this functor
on cardinalities.

Such functors $\Set \to \Set$ are sums of representable functors, and are
therefore examples of \emph{polynomial functors}. Polynomial functors are well
studied objects with a beautiful theory. They are important in computer science
for the study of data types (cite), as a way of describing operads (cite), and
for the development of opetopic approaches to higher categories (cite). The
class of polynomial functors can be described in a number of equivalent ways:
\begin{thm}[cite something]
  Let $P : \Set \to \Set$ be a functor. Then the following are equivalent:
  \begin{enumerate}
  \item $P$ is polynomial.
  \item $P$ is a sum of representables.
  \item $P$ is accessible and preserves connected limits.
  \item There is a bundle $\pi : E \to B$ of sets, and $P$ is the composite
    $$\Set \xto{E^{\ast}} \Set_{/E} \xto{\pi_{!}} \Set_{/B} \xto{B_{\ast}}.$$
  \item $P$ is a local right adjoint.
  \end{enumerate}
\end{thm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Second Intro
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A polynomial functor $P : \Set \to \Set$ is a sum of representables
$$P(X) := \sum_{b \in B} X^{E_b}$$
and therefore depends on a $B$-indexed family of sets $E_b$. This data is known
in the computer science literature as a ``container'', but as such an indexed
family of sets can be represented by as a function
\[
  \begin{tikzcd}
    E \arrow[d, "\pi"] \\
    B
  \end{tikzcd}
\]
we will refer to it as a \emph{bundle}. We think of a bundle as a categorified
Young diagram:

\[
[image]
\]

$B$ is the set of rows and $E_b$ is the set of boxes in row $b$ (possibly empty,
for generalities sake). We can see the polynomial functor
$$P(X) := \sum_{b \in B} X^{E_b}$$
as sending a set $X$ to the set of ways to label a row of the correponding Young
diagram with elements of $X$.

Remarkably, all natural transformations between polynomial functors can be
represented in terms of their associated bundles. A natural transformation $P
\to P'$ corresponds to a pair of functions
\[
\left( f : B \to B',\, f^{\sharp} : \dprod{b : B} E'_{fb} \to E_b \right)
\]
(using depented type syntax) acting covariantly on rows and contravariantly on
boxes in each row. In terms of bundles, this is a diagram of the following sort:

\[
  \begin{tikzcd}
    E \arrow[d, "\pi"'] \arrow[r, leftarrow, "f_{\sharp}"] & \bullet \arrow[d] \arrow[r]
    \arrow[dr, phantom, "\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
    B \arrow[r, equals] & B \arrow[r, "f"'] & B'
  \end{tikzcd}
\]
We refer to these special spans as \emph{contravariant} morphisms of bundles.

\begin{thm}[cite]
The category of polynomial functors and natural transformations is equivalent to
the category of bundles and contravariant morphisms.
\end{thm}

This begs the question: what, then, are we to make of the more obvious,
\emph{covariant} morphisms of bundles
\[
  \begin{tikzcd}
E \arrow[r, "\term{tot}(f_{\sharp})"] \arrow[d, "\pi"'] & E' \arrow[d, "\pi'"] \\
B \arrow[r, "f"']                                       & B'                  
\end{tikzcd}
\]
which, in terms of Young diagrams, are covariant on both the rows and the boxes
in each row.

It turns out that these covariant maps of bundles correspond to natural
transformations between the appropriate sums of \emph{contravariant}
representables:
$$D(X) := \sum_{b \in B} E_b^X$$
In terms of Young diagrams, such a functor takes a set $X$ to the set of ways to
place the elements of $X$ in the boxes of a row.

Polynomial functors get their name because when $B$ and $E$ are finite, one may
organize the exponents $E_b$ by cardinality, yielding a function
$\term{card}E_{(-)} : B \to \Nb$. Letting $B_n := (\term{card}E_{(-)})\inv(n)$,
we find that the cardinality
$$|P(X)| = \sum_{n \in \Nb} |B_n||X|^n$$
is a polynomial in the cardinality of $X$. Similarly,
$$|D(X)| = \sum_{n \in \Nb} |B_n|n^{|X|}$$
resembles a Dirichlet series in the cardinalty of $X$. Accoringly, we call such
sums of contravariant representables \emph{Dirichlet functors}.

We will show in this paper that Dirichlet functors are, quite robustly, the
contravariant analogue of polynomial functors. In particular, the many ways to
say that a functor is polynomial have contravariant analogues.
\begin{thm}[cite]\label{thm:polynomial.set.characterization}
  Let $P : \Set \to \Set$ be a functor. Then the following are equivalent.
  \begin{enumerate}
  \item $P$ is polynomial.
  \item $P$ is the sum of representables.
  \item There is a bundle $\pi : E \to B$ together with a natural isomorphism
    $$P(X) \cong \sum_{b \in B} X^{E_b}.$$
    Or, equivalently, a natural isomorphism of $P$ with the composite
    $$\Set \xto{E^{\ast}} \Set_{/E} \xto{\pi_!} \Set_{/B} \xto{B_\ast} \Set.$$
  \item $P$ is accessible and preserves connected limits.
  \end{enumerate}
\end{thm}

Analogously, we will prove the following theorem.
\begin{thm}\label{thm:dirichlet.set.characterization}
Let $D : \Set\op \to \Set$ be a contravariant functor. Then the following are
equivalent.
\begin{enumerate}
\item $D$ is Dirichlet.
\item $D$ is the sum of contravariant representables.
\item There is a bundle $\pi : E \to B$ together with a natural isomorphism
  $$D(X) \cong \sum_{b \in B} E_b^X.$$
  Or, equivalently, a natural isomorphism of $D$ with the composite
  $$\Set\op \xto{(B^{\ast})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
  \xto{B_{\ast}} \Set.$$
\item $D$ preserves connected limits.
\end{enumerate}
\end{thm}

Note that we no longer need to assume accessiblity. This is a general feature of
the theory of Dirichlet functors; it is a bit ``smaller'' and more maneageable
than that of polynomials. In particular, a Dirichlet functor is determined by
its action on the terminal morphism $!_0 : 0 \to \ast$ of the empty set. As a corollary, Dirichlet functors form a topos.

\begin{thm}\label{thm:dirichlet.set.equivalence}
The functor $\Set^{\downarrow} \to \type{Fun}(\Set\op, \Set)$ sending $\pi : E
\to B$ to the induced Dirichlet functor $X \mapsto \sum_{b \in B} E_b^X$ is
fully faithful, and so gives an equivalence
$$\Set^{\downarrow} \simeq \Dir$$
between bundles and Dirichlet functors, with inverse given by evalutation at
$!_0 : 0 \to \ast$.
\end{thm}

Now, object-wise, a Dirichlet functor and a polynomial functor are determined by
the same data --- a bundle $\pi : E \to B$ of sets. Accordingly, one would
expect a transformation
$$X^N \mapsto N^X$$
turning polynomial functors into Dirichlet functors, and vice versa. But the
natural transformations between each sort of functor induce different morphisms
between the bundles; natural tranformations between polynomial functors induce
contravariant bundle morphisms, while natural transformations betwee Dirichlet
functors induce covariant bundle morphisms. However, if we restrict to those
morphisms of bundles which are \emph{isovariant} on the fibers --- that is, the
pullback diagrams of the form
\[
  \begin{tikzcd}
E \arrow[r, "\term{tot}(f_{\sharp})"] \arrow[d, "\pi"'] \arrow[dr, phantom,
"\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
B \arrow[r, "f"']                                       & B'                  
\end{tikzcd}
\]
which preserve the number of boxes in each row --- we find that such a morphism
is both a co- and contravariant morphism of bundles. It is well known that such
\emph{cartesian} morphisms of bundles correspond to \emph{cartesian} natural
transformations between polynomial functors (cite) --- those whose naturality
squares are pullbacks. This is true as well for Dirichlet functors.
\begin{thm}
A natural transformation $D \to D'$ of Dirichlet functors is Cartesian if and
only if the corresponding bundle map
\[
  \begin{tikzcd}
E \arrow[r, "\term{tot}(f_{\sharp})"] \arrow[d, "\pi"'] \arrow[dr, phantom,
"\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
B \arrow[r, "f"']                                       & B'                  
\end{tikzcd}
\]
is a pullback. As a corollary, we have an equivalence of categories
$$\Poly_{\ulcorner} \simeq \Dir_{\ulcorner}$$
between polynomial functors with cartesian natural transfromations and Dirichlet
functors with cartesian natural transfromations.
\end{thm}

This story occupies Section \ref{sec:set.level} of our paper.

Polynomial functors play another very important role: they are \emph{generating
  functors} for flat combinatorial species. That is, we have a (non-canonical)
identification
$$P(X) \cong \sum_{n \in \Nb} C_n \times X^n/n!$$
for sets $C_n$ on which the symmetric groups $\Aut(\underline{n})$ act freely.
The generating functors for general combinatorial species --- the \emph{analytic
functors} --- are not in general polynomial due to a loss of information when
quotienting out by the action of the symmetric groups. This can be fixed by
instead taking \emph{homotopy quotients} of these actions.

In other words, we need to move to homotopy types to make sense of the
fractional coefficients that arise in the exponential power series form
$$\sum_{n \in \Nb} a_n \frac{x^n}{n!}.$$
As we will see, moving to homotopy types also allows us to express the negative
exponent in the Dirichlet series form
$$\sum_{n \in \Nb} a_n n^{-s}.$$

In \emph{$\infty$-Operads as Analytic Monads} \cite{GHK:Analytic.Monads},
Gepner, Haugseng, and Kock take this approach and develop the theory of
polynomial functors on homotopy types. In this setting, being analtyic is a
property of a polynomial functors, and is equivalent to admitting a cartesian
map to the functor $\type{Sym}$ given by
$$X \mapsto \sum_{n : \Nb} X^n \sslash n!$$

GHK prove $\infty$-categorical analogues of the above Theorem
\ref{thm:polynomial.set.characterization}.
\begin{thm}[\cite{GHK:Analytic.Monads}]\label{thm:polynomial.type.characterization}
Let $P : \Ha \to \Ha$ be a functor on the $\infty$-category of homotopy types.
Then the following are equivalent:
  \begin{enumerate}
  \item $P$ is polynomial.
  \item There is a bundle $\pi : E \to B$ of homotopy types together with a natural equivalence
    $$P(X) \simeq \sum_{b : B} X^{E_b}.$$
    Or, equivalently, a natural equivalence of $P$ with the composite
    $$\Ha \xto{E^{\ast}} \Ha_{/E} \xto{\pi_!} \Ha_{/B} \xto{B_\ast} \Ha.$$
  \item $P$ is accessible and preserves weakly contractible limits.
  \end{enumerate}
\end{thm}

Note that while this is a strong analogue, it is not a direct generalization:
not all connected limits are weakly contractible.

In Section \ref{sec:type.level}, we will prove analogues of Theorems
\ref{thm:dirichlet.set.characterization} and
\ref{thm:dirichlet.set.equivalence}. In particular, we will prove the following.

\begin{thm}\label{thm:dirichlet.type.characterization}
Let $D : \Set\op \to \Set$ be a contravariant functor. Then the following are
equivalent.
\begin{enumerate}
\item $D$ is Dirichlet.
\item There is a bundle $\pi : E \to B$ of homotopy types together with a natural equivalence
  $$D(X) \cong \sum_{b \in B} E_b^X.$$
  Or, equivalently, a natural equivalence of $D$ with the composite
  $$\Ha\op \xto{(B^{\ast})\op} (\Ha_{/B})\op \xto{[-, \pi]} \Ha_{/B}
  \xto{B_{\ast}} \Ha.$$
\item $D$ preserves weakly contractible limits.
\end{enumerate}
\end{thm}

In Section \ref{sec:ordinary.dirichlet.functors}, we will introduce the notion
of an \emph{ordinary} Dirichlet functor, a categorification of a Dirichlet
series
$$\sum_{n \in \Nb} a_n n^{-s}.$$
In the last installment of his blog \emph{This Week's Finds} (cite), Baez (joint with
Dolan) presents a functor of groupoids categorifying the Riemann Zeta function.
In later, unpublished work (cite), Baez and Dolan give an analogous
categorification of Hasse-Weil Zeta functions. We will recall some facts about
homotopy cardinality and construct these Zeda functors as ordinary Dirichlet
functors in our setting. We leave the investigation of Euler product formulas
and functional equations on the objective level to future work.

\begin{acknowledgements}

\end{acknowledgements}

\section{Dirichlet Functors on Sets} \label{sec:set.level}

Before diving in to the theory of Dirichlet functors, let's first consider the
category $\Set^{\downarrow}$ of bundles of sets.

\begin{prop}
  There is an adjoint quintuple:
  \[
    \begin{tikzcd}
      \Set \arrow[r, "\const"] \arrow[r, leftarrow, shift left = 5,
      "\term{cod}"] \arrow[r, leftarrow, shift right = 5, "\term{dom}"]
      \arrow[r, shift left = 10, "!^{(-)}"]  \arrow[r, shift right = 10, "!_{(-)}"] & \Set^{\downarrow}
    \end{tikzcd}
  \]
  All of the functors $\Set \to \Set^{\downarrow}$ are fully faithful.
\end{prop}
\begin{proof}
There is an adjoint triple $\begin{tikzcd} \ast \arrow[r,leftarrow] \arrow[r,
  bend left] \arrow[r, bend right] & \downarrow \end{tikzcd}$. The middle three
functors are given by restricting along this adjoint triple; the outer two are
given by Kan extending, or more concretely:
  $$X \mapsto \begin{tikzcd} 0 \arrow[d, "!^X"] \\ X \end{tikzcd}$$
  $$X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}$$
It is easy to see that the unit $X \to \term{dom} !_{X}$ is an isomorphism (it is in
fact an identity), so $!_{(-)}$ is fully faithful. Therefore, all the functors
going from $\Set \to \Set^{\downarrow}$ are fully faithful.
\end{proof}

We prove a quick fact we will use later.
\begin{lem}\label{lem:bang.preserves.connected.colimits}
  The functor $!_{(-)}$ preserves connected colimits.
\end{lem}
\begin{proof}
  To see that $!_{(-)}$ preserves connected colimits, recall that colimits in $\Set^{\downarrow}$ are calculated pointwise. It remains to show, then, that the map
  \[
    \begin{tikzcd}
    \colim S_i \arrow[r, equals] \arrow[d] & \colim S_i \arrow[d] \\
    \colim \ast \arrow[r] & \ast 
    \end{tikzcd}
  \]
  is an isomorphism in $\Set^{\downarrow}$, for which it suffices to show that
  $\colim \ast$ is terminal. But the colimit of the terminal diagram is the set
  of connected components of its indexing diagram -- since we assumed the
  indexing diagram was connected, this contains a single element.
\end{proof}

Now we will define the \emph{extent} of a bundle, the Dirichlet functor it
corresponds to. This sends a bundle
$\pi : E \to B$ to the functor
$$X \mapsto \sum_{b \in B} E_b^X.$$
We will, however, give a more abstract definition of the extent, and then
calculate a number of presentations of it.

\begin{defn}
  The functor $!_0 : \downarrow \to \Set\op$ picking out the terminal morphism
  $!_0 : 0 \to 1$ by precomposition an evaluation functor
  $$\Set^{\downarrow} \xleftarrow{\ev_{!_0}} \Fun(\Set\op, \Set).$$
  This functor admits a right adjoint by right Kan extension; we define the
  \emph{Dirichlet extent} functor $\ext : \Set^{\downarrow} \to \Fun(\Set\op,
  \Set)$ to be this right adjoint:
  $$\ext_{\pi} :\equiv \term{ran}_{!_0} \pi.$$
\end{defn}

\begin{prop}
  The functor $\ext$ is fully faithful, giving an equivalence
  $$\Set^{\downarrow} \simeq \Dir$$
  where $\Dir$ is the category of Dirichlet functors and natural transformations.
\end{prop}
\begin{proof}
Since $!_0 : \downarrow \to \Set\op$ is fully faithful, the counit of the
$\ev_{!_0} \vdash \ext$ adjunction --- which is the universal cell defining the
right Kan extension --- is an isomorphism. 
\end{proof}

\begin{prop}\label{prop:set.characterizing.extent}
  Let $\pi : E \to B$ be a bundle. The following are equivalent:
  \begin{enumerate}
  \item The extent $\ext_{\pi} : \Set\op \to \Set$ of $\pi$.
  \item The functor
    $$S \mapsto \sum_{b \in B} E_b^S,$$
    or equivalently the composite
  $$\Set\op \xto{(B^{\ast})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
  \xto{B_{\ast}} \Set.$$
\item The functor restricted representable functor
  $\Set^{\downarrow}(!_{(-)}, \pi)$.
\item The functor
  $$S \mapsto \lim(\Hom_{\Set}(!_0, S) \to \downarrow \xto{\pi} \Set)$$
  where $\Hom_{\Set}(!_0, S)$ is the slice category of $!_0 : \downarrow \to
  \Set$ over $S$.
\item The functor
  $$S \mapsto \lim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft}
  \xto{\pi} \Set)$$
  where $(-)^{\triangleleft}$ is the \emph{left cone} 2-functor, adjoining an initial object.
  \end{enumerate}
\end{prop}
\begin{proof}
We have presented these results in order of most understandable to most
computational; we will prove it a somewhat opposite order.

First, we note that 
$$S \mapsto \lim(\Hom_{\Set\op}(S, !_0) \to \downarrow \xto{\pi} \Set)$$
is the standard right Kan extension formulat for $\ext_{\pi} \equiv
\term{ran}_{!_0} \pi$. Noting that $\Hom_{\Set}(!_0, S) = \Hom_{\Set\op}(S,
!_0)$, we see that (1) is equivalent to (4). Furthermore, noting that
$\Hom_{\Set}(!_0, S)$ simply adjoins an initial object to (the discrete
category) $S$, we see that (4) is equivalent to (5).

Now, we note that every set $S$ is the colimit of the diagram $S^{\triangleleft}
\xto{\ast^{\triangleleft}} \xto{!_0} \Set$, namely:
\[
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBoBGAXVJADcBDAGwFcYkRyQBfU9TXfIRTkK1Ok1btOPPtjwEiAZlE0GLNog7deIDHMFEALCvHqp22QIUoATCbWTNAHScBjKBBwIZu-vKHIdjZiDhogxBa++taBpMQhEmEAGtxiMFAA5vBEoABmAE4QALZIAKw0OBBIxD4FxWUVVYjktYUliOUglUg2rfUdjUiKfe1kXU0AbCNIIuNIUzp17XZziAt5bUODa1yUXEA
\begin{tikzcd}
              &              & S                                               &              &               \\
1 \arrow[rru] & 1 \arrow[ru] & \cdots                                          & 1 \arrow[lu] & 1 \arrow[llu] \\
              &              & 0 \arrow[llu] \arrow[lu] \arrow[ru] \arrow[rru] &              &              
\end{tikzcd}
\]
Since, by Lemma \ref{lem:bang.preserves.connected.colimits}, $!_{(-)}$
preserves connected colimits, {\color{red} TODO}.
\end{proof}

Now we are ready to intrinsically characterize the Dirichlet functors.
\begin{thm}
A functor $D : \Set\op \to \Set$ is Dirichlet if and only if it preserves
connected limits. 
\end{thm}
\begin{proof}
First, we show that Dirichlet functors preserve connected limits. If $D$ is
Dirichlet, then by Prop \ref{prop:set.characterizing.extent}, $D$ is naturally
isomorphic to the composite
$$\Set\op \xto{(B^{\ast})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
\xto{B_\ast}.$$
As $(B^{\ast})\op$ is a right adjoint, it commutes with all limits, and as $[-,\pi]$
is part of a multivariable adjunction, it also commutes with all limits.
Finally, we note that $B_{\ast}$ commutes with connected limits.

Now, we show that if $D$ commutes with connected limits, then the unit
$D \to \ext_{D!_0}$ is an isomorphism. By Prop
\ref{prop:set.characterizing.extent}, 
  $$\ext_{D!_0}(S) = \lim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft}
  \xto{D!_0} \Set).$$

Every set is the connected colimit of the diagram $S^{\triangleleft} \to
\downarrow \xto{!_0} \Set$, and therefore if $D$ preserves this limit, then
$D(S)$ is precisely the above limit $\ext_{D!_0}(S)$.
\end{proof}

Next, we turn to cartesian morphisms.
\begin{prop}
A natural transformation $\phi : D \to D'$ between Dirichlet functors is
cartesian if and only if the induced bundle map $D!_0 \to D'!_0$ is a pullback.
\end{prop}
\begin{proof}
TODO
\end{proof}

\begin{thm}
  There is an equivalence of categories
  $$\type{Poly}_{\ulcorner} \simeq \Dir_{\ulcorner}$$
  between the category of polynomial functors and cartesian transformations and
  Dirichlet functors and cartesian transformations. This equivlalence sends
  representables to representables
  $$(-)^N \mapsto N^{(-)}.$$
\end{thm}
\begin{proof}
TODO
\end{proof}

\section{Dirichlet Functors on Homotopy Types} \label{sec:type.level}

\begin{prop}
  There is an adjoint quintuple:
  \[
    \begin{tikzcd}
      \Ha \arrow[r, "\const"] \arrow[r, leftarrow, shift left = 5,
      "\term{cod}"] \arrow[r, leftarrow, shift right = 5, "\term{dom}"]
      \arrow[r, shift left = 10, "!^{(-)}"]  \arrow[r, shift right = 10, "!_{(-)}"] & \Ha^{\downarrow}
    \end{tikzcd}
  \]
  All of the functors $\Ha \to \Ha^{\downarrow}$ are fully faithful.
\end{prop}
\begin{proof}
There is an adjoint triple $\begin{tikzcd} \ast \arrow[r,leftarrow] \arrow[r,
  bend left] \arrow[r, bend right] & \downarrow \end{tikzcd}$. The middle three
functors are given by restricting along this adjoint triple; the outer two are
given by Kan extending. By Lemma \ref{lem:kan.extending.cone.adds.initial}, we
may calculate these as
  $$X \mapsto \begin{tikzcd} 0 \arrow[d, "!^X"] \\ X \end{tikzcd}$$
  $$X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}$$
It is easy to see that the unit $X \to \term{dom} !_{X}$ is an equivalence (it is in
fact an identity), so $!_{(-)}$ is fully faithful. Therefore, all the functors
going from $\Ha \to \Ha^{\downarrow}$ are fully faithful.
\end{proof}

\begin{prop}\label{lem:bang.preserves.weakly.contractible.colimits}
  The functor $!_{(-)}$ preserves weakly contractible colimits.
\end{prop}
\begin{proof}
  To see that $!_{(-)}$ preserves weakly contractible colimits, recall that colimits in $H^{\downarrow}$ are calculated pointwise. It remains to show, then, that the map
  \[
    \begin{tikzcd}
    \colim S_i \arrow[r, equals] \arrow[d] & \colim S_i \arrow[d] \\
    \colim \ast \arrow[r] & \ast 
    \end{tikzcd}
  \]
  is an equivalence in $H^{\downarrow}$, for which it suffices to show that $\colim \ast$ is contractible. But the colimit of the terminal diagram is the (Kan-fibrant replacement of) its indexing simplicial set -- since we assumed the diagram was weakly contractible, $\colim \ast$ is contractible.
\end{proof}

Now we will define the \emph{extent} of a bundle, the Dirichlet functor it
corresponds to. This sends a bundle
$\pi : E \to B$ to the functor
$$X \mapsto \sum_{b : B} E_b^X.$$
We will, however, give a more abstract definition of the extent, and then
calculate a number of presentations of it.

\begin{defn}
  The functor $!_0 : \downarrow \to \Ha\op$ picking out the terminal morphism
  $!_0 : 0 \to 1$ by precomposition an evaluation functor
  $$\Ha^{\downarrow} \xleftarrow{\ev_{!_0}} \Fun(\Ha\op, \Ha).$$
  This functor admits a right adjoint by right Kan extension; we define the
  \emph{Dirichlet extent} functor $\ext : \Ha^{\downarrow} \to \Fun(\Ha\op,
  \Ha)$ to be this right adjoint:
  $$\ext_{\pi} :\equiv \term{ran}_{!_0} \pi.$$
\end{defn}

\begin{prop}
  The functor $\ext$ is fully faithful, giving an equivalence
  $$\Ha^{\downarrow} \simeq \Dir$$
  where $\Dir$ is the category of Dirichlet functors and natural transformations.
\end{prop}
\begin{proof}
Since $!_0 : \downarrow \to \Ha\op$ is fully faithful, the counit of the
$\ev_{!_0} \vdash \ext$ adjunction --- which is the universal cell defining the
right Kan extension --- is an equivalence by Proposition 9.4.4 of \cite{RV:Elements}. 
\end{proof}

\begin{prop}\label{prop:set.characterizing.extent}
  Let $\pi : E \to B$ be a bundle. The following are equivalent:
  \begin{enumerate}
  \item The extent $\ext_{\pi} : \Ha\op \to \Ha$ of $\pi$.
  \item The functor
    $$S \mapsto \sum_{b : B} E_b^S,$$
    or equivalently the composite
  $$\Ha\op \xto{(B^{\ast})\op} (\Ha_{/B})\op \xto{[-, \pi]} \Ha_{/B}
  \xto{B_{\ast}} \Ha.$$
\item The functor restricted representable functor
  $\Ha^{\downarrow}(!_{(-)}, \pi)$.
\item The functor
  $$S \mapsto \lim(\Hom_{\Ha}(!_0, S) \to \downarrow \xto{\pi} \Ha)$$
  where $\Hom_{\Ha}(!_0, S)$ is the slice category of $!_0 : \downarrow \to
  \Ha$ over $S$.
\item The functor
  $$S \mapsto \lim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft}
  \xto{\pi} \Ha)$$
  where $(-)^{\triangleleft}$ is the \emph{left cone}.
  \end{enumerate}
\end{prop}
\begin{proof}
We have presented these results in order of most understandable to most
computational; we will prove it a somewhat opposite order.

First, we note that 
$$S \mapsto \lim(\Hom_{\Ha\op}(S, !_0) \to \downarrow \xto{\pi} \Ha)$$
is the right Kan extension formula for $\ext_{\pi} \equiv
\term{ran}_{!_0} \pi$ --- see Corollary 9.5.3 of \cite{RV:Elements}. Noting that $\Hom_{\Ha}(!_0, S) = \Hom_{\Ha\op}(S,
!_0)$, we see that (1) is equivalent to (4). Furthermore, noting that
$\Hom_{\Ha}(!_0, S)$ simply adjoins an initial object to (the discrete
category) $S$, we see that (4) is equivalent to (5).

Now, we note that every set $S$ is the colimit of the diagram $S^{\triangleleft}
\xto{\ast^{\triangleleft}} \xto{!_0} \Ha$. Since, by Lemma \ref{lem:bang.preserves.weakly.contractible.colimits}, $!_{(-)}$
preserves weakly contractible colimits, {\color{red} TODO}.
\end{proof}

Now we are ready to intrinsically characterize the Dirichlet functors.
\begin{thm}
A functor $D : \Ha\op \to \Ha$ is Dirichlet if and only if it preserves
weakly contractible limits. 
\end{thm}
\begin{proof}
First, we show that Dirichlet functors preserve connected limits. If $D$ is
Dirichlet, then by Prop \ref{prop:set.characterizing.extent}, $D$ is naturally
isomorphic to the composite
$$\Ha\op \xto{(B^{\ast})\op} (\Ha_{/B})\op \xto{[-, \pi]} \Ha_{/B}
\xto{B_\ast}.$$
As $(B^{\ast})\op$ is a right adjoint, it commutes with all limits, and as $[-,\pi]$
is part of a multivariable adjunction, it also commutes with all limits.
Finally, we note that $B_{\ast}$ commutes with connected limits.

Now, we show that if $D$ commutes with connected limits, then the unit
$D \to \ext_{D!_0}$ is an equivalence. By Prop
\ref{prop:set.characterizing.extent}, 
  $$\ext_{D!_0}(S) = \lim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft}
  \xto{D!_0} \Ha).$$

Every set is the connected colimit of the diagram $S^{\triangleleft} \to
\downarrow \xto{!_0} \Ha$, and therefore if $D$ preserves this limit, then
$D(S)$ is precisely the above limit $\ext_{D!_0}(S)$.
\end{proof}

Next, we turn to cartesian morphisms.
\begin{prop}
A natural transformation $\phi : D \to D'$ between Dirichlet functors is
cartesian if and only if the induced bundle map $D!_0 \to D'!_0$ is a pullback.
\end{prop}
\begin{proof}
TODO
\end{proof}

\begin{thm}
  There is an equivalence of $\infty$-categories
  $$\type{Poly}_{\ulcorner} \simeq \Dir_{\ulcorner}$$
  between the category of polynomial functors and cartesian transformations and
  Dirichlet functors and cartesian transformations. This equivlalence sends
  representables to representables
  $$(-)^N \mapsto N^{(-)}.$$
\end{thm}
\begin{proof}
TODO
\end{proof}

\section{Ordinary Dirichlet Functors} \label{sec:ordinary.dirichlet.functors}

\section{Appendix}

\begin{lem}\label{lem:cone.initial.equivalence}
Let $\Ca$ be an $\infty$-category with an initial object. For any simplicial set
$J$, let $\Ca^{J^{\triangleleft}}_{\ast}$ be the $\infty$-category of
  $J^{\triangleleft}$-shaped diagrams whose apex is at the initial object; that
  is, the following pullback:
  \[
    \begin{tikzcd}
      \Ca^{J} \arrow[drr, bend left] \arrow[ddr, bend right] \arrow[dr,
      dotted, "\sim"] & & \\
      & \Ca^{J^{\triangleleft}}_{\ast} \arrow[d] \arrow[r] \arrow[dr, phantom,
      "\ulcorner" very near start] & \Ca^{J^{\triangleleft}} \arrow[d,
      "\term{ev}_{\term{apex}}"] \\
      & \ast \arrow[r, "0"'] & \Ca
    \end{tikzcd}
  \]
The the dotted extension map  $\epsilon : \Ca^{J} \to \Ca^{J^{\triangleleft}}_{\ast}$ is an equivalence.
\end{lem}

\begin{lem}\label{lem:kan.extending.cone.adds.initial}
If $\Ca$ is an $\infty$-category with an initial object, then the restriction
$\Ca^{J^{\triangleleft}} \to \Ca^{J}$ has a left adjoint right inverse $\epsilon
: \Ca^J \to \Ca^{J^{\triangleleft}}$ extending a diagram by adjoining the
initial object. 
\end{lem}
\begin{proof}

\end{proof}

\begin{lem}
If $\Ca$ is an $\infty$-category with an initial object $0$, and $d : D \to
\Ca^J$ a family of diagrams with colimit $\colim d : D \to \Ca$, then the family
$D \xto{d} \Ca^J \xto{\epsilon} \Ca^{J^{\triangleleft}}$ has colimit $\colim d$.
\end{lem}
\begin{proof}
For $\colim d : D \to \Ca$ to be the colimit of $d : D \to \Ca^J$ means that 
\end{proof}

### 2020-03-31 draft.tex
removed extra intro

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% First Intro
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-There are two basic sorts of generating functions in prevalent use in
-combinatorics. There are the \emph{analytic} generating functions arising from power
-series
-$$\sum_{n \in \Nb} a_n x^n$$
-and the \emph{Dirichlet} generating functions arising from Dirichlet series
-$$\sum_{n \in \Nb} a_n n^{-s}.$$
-The sequence of coefficients $a_n$ counts the amount of objects $A_n$ associated to an
-$n$-element set $\underline{n} := \{0,\ldots, n-1\}$. For example, if $A_n$ is
-the set of injections from $\underline{n}$ to $\underline{k}$, then $a_n = {k
-  \choose n}$.
-
-The power of the generating function formalism lies in way that algebraic and
-analytic operations on the generating functions shadow combinatorial operations
-on the sets that their coefficients count. This ``shadowing'' can be seen as an
-instance of \emph{decategorification}. In his seminal paper \emph{Une
-  th{\'e}orie combinatoire de s{\'e}ries formelles}
-\cite{J:combinatorial.species}, Joyal defines a combinatorial species to be a
-functor $A$ from the groupoid of finite sets and bijections to the category of
-sets, assigning every set $\underline{n}$ a set $A_n$ isovariantly. One
-associates a series to a combinatorial species by taking the cardinality of the
-$A_n$ and from there derive a generating function. But one can proceed in
-another way by first making a \emph{generating functor}\footnote{In truth, one
-  derives what is known as an \emph{analtyic} functor from this operation, and
-  not a polynomial functor. This is because one must also quotient by the action
-  of the symmetric groups on $A_n$. This difficulty is rectified when passing to
-  homotopy types, where analytic functors are polynomial due to the better
-  behavior of homotopy colimits.}
- $$X \mapsto \sum_{n \in \Nb} A_n \times X^n$$
-from the category of sets to itself, and then taking the action of this functor
-on cardinalities.
-
-Such functors $\Set \to \Set$ are sums of representable functors, and are
-therefore examples of \emph{polynomial functors}. Polynomial functors are well
-studied objects with a beautiful theory. They are important in computer science
-for the study of data types (cite), as a way of describing operads (cite), and
-for the development of opetopic approaches to higher categories (cite). The
-class of polynomial functors can be described in a number of equivalent ways:
-\begin{thm}[cite something]
-  Let $P : \Set \to \Set$ be a functor. Then the following are equivalent:
-  \begin{enumerate}
-  \item $P$ is polynomial.
-  \item $P$ is a sum of representables.
-  \item $P$ is accessible and preserves connected limits.
-  \item There is a bundle $\pi : E \to B$ of sets, and $P$ is the composite
-    $$\Set \xto{E^{\ast}} \Set_{/E} \xto{\pi_{!}} \Set_{/B} \xto{B_{\ast}}.$$
-  \item $P$ is a local right adjoint.
-  \end{enumerate}
-\end{thm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% Second Intro
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 A polynomial functor $P : \Set \to \Set$ is a sum of representables
@@
 \]
-(using depented type syntax) acting covariantly on rows and contravariantly on
+(using dependent type syntax) acting covariantly on rows and contravariantly on
 boxes in each row. In terms of bundles, this is a diagram of the following sort:

### 2020-03-31 draft.tex
typos

@@
 $$|D(X)| = \sum_{n \in \Nb} |B_n|n^{|X|}$$
-resembles a Dirichlet series in the cardinalty of $X$. Accoringly, we call such
+resembles a Dirichlet series in the cardinality of $X$. Accoringly, we call such
 sums of contravariant representables \emph{Dirichlet functors}.
@@
 between the bundles; natural tranformations between polynomial functors induce
-contravariant bundle morphisms, while natural transformations betwee Dirichlet
+contravariant bundle morphisms, while natural transformations between Dirichlet
 functors induce covariant bundle morphisms. However, if we restrict to those
@@
 $$P(X) \cong \sum_{n \in \Nb} C_n \times X^n/n!$$
-for sets $C_n$ on which the symmetric groups $\Aut(\underline{n})$ act freely.
+for sets $C_n$ on which the symmetric groups $\Aut(\underline{n})$ act freely
+(for \emph{finitary} $P$, commuting with filtered colimits).
 The generating functors for general combinatorial species --- the \emph{analytic
@@
 Gepner, Haugseng, and Kock take this approach and develop the theory of
-polynomial functors on homotopy types. In this setting, being analtyic is a
+polynomial functors on homotopy types. In this setting, being analytic is a
 property of a polynomial functors, and is equivalent to admitting a cartesian
@@
   \xto{B_{\ast}} \Set.$$
-\item The functor restricted representable functor
+\item The restricted representable functor
   $\Set^{\downarrow}(!_{(-)}, \pi)$.
@@
 $$\Set\op \xto{(B^{\ast})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
-\xto{B_\ast}.$$
+\xto{B_\ast} \Set.$$
 As $(B^{\ast})\op$ is a right adjoint, it commutes with all limits, and as $[-,\pi]$
@@
   \xto{B_{\ast}} \Ha.$$
-\item The functor restricted representable functor
+\item The restricted representable functor
   $\Ha^{\downarrow}(!_{(-)}, \pi)$.
@@
 Dirichlet, then by Prop \ref{prop:set.characterizing.extent}, $D$ is naturally
-isomorphic to the composite
+equivalent to the composite
 $$\Ha\op \xto{(B^{\ast})\op} (\Ha_{/B})\op \xto{[-, \pi]} \Ha_{/B}
-\xto{B_\ast}.$$
+\xto{B_\ast} \Ha.$$
 As $(B^{\ast})\op$ is a right adjoint, it commutes with all limits, and as $[-,\pi]$

### 2020-04-01 draft.tex
kept writing

@@
 preserves connected colimits, {\color{red} TODO}.
+
+Finally, we note that the set $\Set^{\downarrow}(!_X, \pi)$ is naturally
+isomorphic to the set $\sum_{b \in B} E_b^X$.
 \end{proof}
@@
 cartesian if and only if the induced bundle map $D!_0 \to D'!_0$ is a pullback.
+
+As a corllary, the equivalence $\Dir \simeq \Set^{\downarrow}$ restricts to an
+equivalence
+$$\Dir_{\ulcorner} \simeq \Set^{\downarrow}_{\ulcorner}$$
+between Dirichlet functors and cartesian natural transformations and bundles and
+pullback sqaures.
 \end{prop}
 \begin{proof}
-TODO
+We want to show that for any $f\colon D\to D'$ the square
+\begin{equation}\label{eqn.cart1}
+\begin{tikzcd}
+	D(1)\ar[r, "f_1"]\ar[d, "\pi"']&
+	D'(1)\ar[d, "\pi'"]\\
+	D(0)\ar[r, "f_0"']&
+	D'(0)
+\end{tikzcd}
+\end{equation}
+is a pullback in $\Set$ iff for all functions $g\colon X\to X'$, the naturality square
+\begin{equation}\label{eqn.cart2}
+\begin{tikzcd}
+  D(X')\ar[r, "f_{X'}"]\ar[d, "D(g)"']&
+  D'(X')\ar[d, "D'(g)"]\\
+  D(X)\ar[r, "f_X"']&
+  D'(X)
+\end{tikzcd}
+\end{equation}
+is a pullback in $\Set$. We will freely use the natural isomorphism
+$D(X)\cong\Set^{\downarrow}(!_X, D!_0)$ from
+\ref{prop:set.characterizing.extent}, which allows us to identify Diagram
+\ref{eqn.cart2} with
+\begin{equation}\label{eqn:cart3}
+\begin{tikzcd}
+ \Set^{\downarrow}(!_{X'}, D!_0)     \ar[r, "f_{!_0,\ast}"]\ar[d, "!_g^{\ast}"']& \Set^{\downarrow}(!_{X'}, D'!_0)
+  \ar[d, "!_{g}^{\ast}"]\\
+  \Set^{\downarrow}(!_{X}, D!_0)\ar[r, "f_{!_0, \ast}"']&
+ \Set^{\downarrow}(!_X, D'!_0) 
+\end{tikzcd}
+\end{equation}
+
+The square in Diagram \ref{eqn.cart1} is a
+special case of that in Diagram \ref{eqn.cart2}, namely for $g\coloneqq !_0$;
+this establishes the only-if direction.
+
+To complete the proof, suppose that Diagram \ref{eqn.cart1} is a pullback, take an arbitrary $g\colon X\to X'$, and suppose given a commutative solid-arrow diagram as shown:
+\[
+\begin{tikzcd}[sep=small]
+  X\ar[rr, "g"]\ar[dd]\ar[rd]&&
+  X'\ar[dr]\ar[dd]\ar[dl, dotted]\\&
+  D(1)\ar[rr, crossing over]&&
+  D'(1)\ar[dd]\\
+  1\ar[dr]\ar[rr, equal]&&
+  1\ar[dr]\ar[dl, dotted]\\&
+  D(0)\ar[from=uu, crossing over]\ar[rr]&&
+  D'(0)
+\end{tikzcd}
+\]
+We can interpret the statement that Diagram \ref{eqn.cart3} is a pullback as
+saying that there are unique dotted arrows making the diagram commute.
+So, we need to show that if the front face is a pullback, then there are unique diagonal dotted arrows as shown, making the diagram commute.
+This follows quickly from the universal property of the pullback.
 \end{proof}
 
-\begin{thm}
+\begin{thm}\label{thm:set.poly.cart.equiv.dir.cart}
   There is an equivalence of categories
@@
 TODO
+\end{proof}
+
+\begin{cor}
+  Let $D$ be a Dirichlet functor. Then the category
+  $\Dir_{/_{\ulcorner} D}$
+  of Dirichlet functors with a cartesian map to $D$ is a topos.
+\end{cor}
+\begin{proof}
+By Theorem \ref{thm:set.poly.cart.equiv.dir.cart}, this category is equivalent
+to $\type{Poly}_{/_{\ulcorner} P}$ for a polynomial $P$. But this is a topos as
+observed in Remark 2.6.2 of \cite{GHK:Analytic.Monads}.
 \end{proof}
@@
 preserves weakly contractible colimits, {\color{red} TODO}.
+
+Finally, we calculate $\Ha^{\downarrow}(!_{\ast}, \pi)$ homotopy type-theoretically:
+\begin{align*}
+\Ha^{\downarrow}(!_{\ast}, \pi) &= \sum_{b : \ast \to B} \sum_{f : X \to E}
+                                  (\pi \circ f = b \circ !_X)\\
+                                &= \sum_{b : B} \sum_{f : X \to E} \prod_{x : X} (\pi (f x) = b) \\
+                                &= \sum_{b : B} \left( X \to \sum_{e : E} (\pi e = b) \right) \\
+                                  &\equiv \sum_{b : B}E_b^X.
+\end{align*}
 \end{proof}
@@
 is part of a multivariable adjunction, it also commutes with all limits.
-Finally, we note that $B_{\ast}$ commutes with connected limits.
+Finally, we note that $B_{\ast}$ commutes with weakly contractible limits by
+Lemma 2.2.7 of \cite{GHK:Analytic.Monads}.
 
-Now, we show that if $D$ commutes with connected limits, then the unit
+Now, we show that if $D$ commutes with weakly contractible limits, then the unit
 $D \to \ext_{D!_0}$ is an equivalence. By Prop
@@
 
-Every set is the connected colimit of the diagram $S^{\triangleleft} \to
-\downarrow \xto{!_0} \Ha$, and therefore if $D$ preserves this limit, then
+Every homotopy type $S$ is the weakly contractible colimit of the diagram $S^{\triangleleft} \to
+\downarrow \xto{!_0} \Ha$ because it is the colimit of the diagram $S \to \ast
+\xto{\ast} \Ha$ and we are extending this diagram with an initial object (see
+Lemma \ref{lem:extending.diagram.with.initial.object.has.same.colimit}). Therefore if $D$ preserves this limit, then
 $D(S)$ is precisely the above limit $\ext_{D!_0}(S)$.
@@
 Next, we turn to cartesian morphisms.
-\begin{prop}
+\begin{prop}\label{prop:type.dirichlet.cartesian.iff.bundle.cartesian}
 A natural transformation $\phi : D \to D'$ between Dirichlet functors is
 cartesian if and only if the induced bundle map $D!_0 \to D'!_0$ is a pullback.
+
+As a corllary, the equivalence $\Dir \simeq \Ha^{\downarrow}$ restricts to an
+equivalence
+$$\Dir_{\ulcorner} \simeq \Ha^{\downarrow}_{\ulcorner}$$
+between Dirichlet functors and cartesian natural transformations and bundles and
+pullback sqaures.
 \end{prop}
@@
 
-\begin{thm}
+\begin{thm}\label{thm:type.poly.cart.equiv.dir.cart}
   There is an equivalence of $\infty$-categories
@@
 \begin{proof}
-TODO
+This follows by composing the equivalence of $\Dir_{\ulcorner}$ with
+$\Ha^{\downarrow}$ from Prop
+\ref{prop:type.dirichlet.cartesian.iff.bundle.cartesian} with that of
+Proposition 2.4.13 of \cite{GHK:Analytic.Monads}, noting that
+$\Ha^{\downarrow}_{\ulcorner}$ is the category of $(\ast,\ast)$-polynomials. 
+\end{proof}
+
+\begin{cor}
+  Let $D$ be a Dirichlet functor. Then the $\infty$-category
+  $\Dir_{/_{\ulcorner} D}$
+  of Dirichlet functors with a cartesian map to $D$ is an $\infty$-topos.
+\end{cor}
+\begin{proof}
+By Theorem \ref{thm:type.poly.cart.equiv.dir.cart}, this $\infty$-category is equivalent
+to $\type{Poly}_{/_{\ulcorner} P}$ for a polynomial $P$. But this is an
+$\infty$-topos by Theorem 2.6.1 of \cite{GHK:Analytic.Monads}.
 \end{proof}
@@
 
-\begin{lem}
+\begin{lem}\label{lem:extending.diagram.with.initial.object.has.same.colimit}
 If $\Ca$ is an $\infty$-category with an initial object $0$, and $d : D \to

### 2020-04-01 draft.tex
added warning

@@
 \ref{eqn.cart2} with
-\begin{equation}\label{eqn:cart3}
+\begin{equation}\label{eqn.cart3}
 \begin{tikzcd}
@@
 \end{align*}
+{\color{red} But I need a better argument to show that this is a natural
+  equivalence of functors --- something involving cartesian fibrations etc etc etc}
 \end{proof}
@@
 \begin{proof}
-TODO
+We want to show that for any $f\colon D\to D'$ the square
+\begin{equation}\label{eqn.type.cart1}
+\begin{tikzcd}
+	D(1)\ar[r, "f_1"]\ar[d, "\pi"']&
+	D'(1)\ar[d, "\pi'"]\\
+	D(0)\ar[r, "f_0"']&
+	D'(0)
+\end{tikzcd}
+\end{equation}
+is a pullback in $\Set$ iff for all functions $g\colon X\to X'$, the naturality square
+\begin{equation}\label{eqn.type.cart2}
+\begin{tikzcd}
+  D(X')\ar[r, "f_{X'}"]\ar[d, "D(g)"']&
+  D'(X')\ar[d, "D'(g)"]\\
+  D(X)\ar[r, "f_X"']&
+  D'(X)
+\end{tikzcd}
+\end{equation}
+is a pullback in $\Set$. We will freely use the natural isomorphism
+$D(X)\cong\Set^{\downarrow}(!_X, D!_0)$ from
+\ref{prop:set.characterizing.extent}, which allows us to identify Diagram
+\ref{eqn.type.cart2} with
+\begin{equation}\label{eqn.cart3}
+\begin{tikzcd}
+ \Set^{\downarrow}(!_{X'}, D!_0)     \ar[r, "f_{!_0,\ast}"]\ar[d, "!_g^{\ast}"']& \Set^{\downarrow}(!_{X'}, D'!_0)
+  \ar[d, "!_{g}^{\ast}"]\\
+  \Set^{\downarrow}(!_{X}, D!_0)\ar[r, "f_{!_0, \ast}"']&
+ \Set^{\downarrow}(!_X, D'!_0) 
+\end{tikzcd}
+\end{equation}
+
+The square in Diagram \ref{eqn.type.cart1} is a
+special case of that in Diagram \ref{eqn.type.cart2}, namely for $g\coloneqq !_0$;
+this establishes the only-if direction.
+
+To complete the proof, suppose that Diagram \ref{eqn.type.cart1} is a pullback, take an arbitrary $g\colon X\to X'$, and suppose given a commutative solid-arrow diagram as shown:
+\[
+\begin{tikzcd}[sep=small]
+  X\ar[rr, "g"]\ar[dd]\ar[rd]&&
+  X'\ar[dr]\ar[dd]\ar[dl, dotted]\\&
+  D(1)\ar[rr, crossing over]&&
+  D'(1)\ar[dd]\\
+  1\ar[dr]\ar[rr, equal]&&
+  1\ar[dr]\ar[dl, dotted]\\&
+  D(0)\ar[from=uu, crossing over]\ar[rr]&&
+  D'(0)
+\end{tikzcd}
+\]
+We can interpret the statement that Diagram \ref{eqn.type.cart3} is a pullback as
+saying that there are unique dotted arrows making the diagram commute. So, we
+need to show that if the front face is a pullback, then there are unique
+diagonal dotted arrows as shown in the homotopy type-theoretical sense.
+{\color{red} TODO} 
 \end{proof}

### 2020-04-01 draft.tex
added preamble

@@
 is a pullback. As a corollary, we have an equivalence of categories
-$$\Poly_{\ulcorner} \simeq \Dir_{\ulcorner}$$
+$$\type{Poly}_{\ulcorner} \simeq \Dir_{\ulcorner}$$
 between polynomial functors with cartesian natural transfromations and Dirichlet

### 2020-04-02 draft.tex
edits; hope not stepping on toes, hope it compiles; does for me!

@@
 $$P(X) := \sum_{b \in B} X^{E_b}$$
-and therefore depends on a $B$-indexed family of sets $E_b$. This data is known
-in the computer science literature as a ``container'', but as such an indexed
+and therefore depends on a family of sets $E_b$ depending on $b\in B$. This data is known
+in the computer science literature as a ``container'', but since such an indexed
 family of sets can be represented by as a function
@@
 for generalities sake). We can see the polynomial functor
-$$P(X) := \sum_{b \in B} X^{E_b}$$
+\begin{equation}\label{eqn.poly}
+P(X) := \sum_{b \in B} X^{E_b}
+\end{equation}
 as sending a set $X$ to the set of ways to label a row of the correponding Young
@@
 represented in terms of their associated bundles. A natural transformation $P
-\to P'$ corresponds to a pair of functions
+\to P'$ corresponds to a pair of functions%
+\footnote{We use dependent type syntax, in particular Idris$^?$.}
 \[
@@
 \]
-(using dependent type syntax) acting covariantly on rows and contravariantly on
-boxes in each row. In terms of bundles, this is a diagram of the following sort:
-
+noting that $f$ acts covariantly on \dis{columns, right?} and $f^\sharp$ acts contravariantly on
+boxes in each row. We refer to these special spans as \dis{can we say \emph{bivariant?}} \emph{contravariant} morphisms of bundles.
+In terms of bundles, this is a diagram of the following sort:
 \[
@@
 \]
-We refer to these special spans as \emph{contravariant} morphisms of bundles.
 
@@
 This begs the question: what, then, are we to make of the more obvious,
-\emph{covariant} morphisms of bundles
+\emph{\dis{univariant?}} morphisms of bundles
 \[
-  \begin{tikzcd}
+  \begin{tikzcd}[column sep=large]
 E \arrow[r, "\term{tot}(f_{\sharp})"] \arrow[d, "\pi"'] & E' \arrow[d, "\pi'"] \\
@@
 \]
-which, in terms of Young diagrams, are covariant on both the rows and the boxes
+for which $f$ is covariant in the rows and $f_\sharp$ is again covariant
 in each row.
+%which, in terms of Young diagrams, are covariant on both the rows and the boxes
+%in each row?
 
@@
 
-Polynomial functors get their name because when $B$ and $E$ are finite, one may
-organize the exponents $E_b$ by cardinality, yielding a function
-$\term{card}E_{(-)} : B \to \Nb$. Letting $B_n := (\term{card}E_{(-)})\inv(n)$,
-we find that the cardinality
+Polynomial functors as in \eqref{eqn.poly} get their name from the case in which $B$ and $E$ are finite sets.
+Consider the function $\term{card}~E_{(-)} : B \to \Nb$, which takes the cardinality of each column $E_b$.
+Letting $B_n := (\term{card}E_{(-)})\inv(n)$, i.e.\ $B_n$ is the set of columns with $n$ elements,
+we find that the for any set $X$, the cardinality
 $$|P(X)| = \sum_{n \in \Nb} |B_n||X|^n$$
@@
 $$|D(X)| = \sum_{n \in \Nb} |B_n|n^{|X|}$$
-resembles a Dirichlet series in the cardinality of $X$. Accoringly, we call such
+resembles a Dirichlet series in the cardinality of $X$. Accordingly, we call such
 sums of contravariant representables \emph{Dirichlet functors}.
+Readers who prefer more traditional algebraic notation can see \cite{SpivakMyers}, which was the set-theoretic inspiration for the present paper.\dis{Agree?}
 
 We will show in this paper that Dirichlet functors are, quite robustly, the
-contravariant analogue of polynomial functors. In particular, the many ways to
+contravariant analogue of polynomial functors. In particular, the many equivalent ways to
 say that a functor is polynomial have contravariant analogues.
@@
   \item $P$ is polynomial.
-  \item $P$ is the sum of representables.
+  \item $P$ is the sum of covariant representables.
   \item There is a bundle $\pi : E \to B$ together with a natural isomorphism
@@
 \begin{thm}\label{thm:dirichlet.set.equivalence}
-The functor $\Set^{\downarrow} \to \type{Fun}(\Set\op, \Set)$ sending $\pi : E
-\to B$ to the induced Dirichlet functor $X \mapsto \sum_{b \in B} E_b^X$ is
+The functor $\Set^{\down} \to \type{Fun}(\Set\op, \Set)$, given by sending $\pi : E
+\to B$ to the induced Dirichlet functor $X \mapsto \sum_{b \in B} E_b^X$, is
 fully faithful, and so gives an equivalence
-$$\Set^{\downarrow} \simeq \Dir$$
+$$\Set^{\down} \simeq \Dir$$
 between bundles and Dirichlet functors, with inverse given by evalutation at
@@
 \[
-  \begin{tikzcd}
+  \begin{tikzcd}[column sep=large]
 E \arrow[r, "\term{tot}(f_{\sharp})"] \arrow[d, "\pi"'] \arrow[dr, phantom,
@@
 polynomial functors on homotopy types. In this setting, being analytic is a
-property of a polynomial functors, and is equivalent to admitting a cartesian
+property of \dis{some?} polynomial functors, and is equivalent to admitting a cartesian
 map to the functor $\type{Sym}$ given by
-$$X \mapsto \sum_{n : \Nb} X^n \sslash n!$$
+$$\type{Sym}X := \sum_{n : \Nb} X^n \sslash n!$$
 
@@
 Before diving in to the theory of Dirichlet functors, let's first consider the
-category $\Set^{\downarrow}$ of bundles of sets.
+category $\Set^{\down}$ of bundles of sets.
 
@@
       "\term{cod}"] \arrow[r, leftarrow, shift right = 5, "\term{dom}"]
-      \arrow[r, shift left = 10, "!^{(-)}"]  \arrow[r, shift right = 10, "!_{(-)}"] & \Set^{\downarrow}
+      \arrow[r, shift left = 10, "!^{(-)}"]  \arrow[r, shift right = 10, "!_{(-)}"] & \Set^{\down}
     \end{tikzcd}
   \]
-  All of the functors $\Set \to \Set^{\downarrow}$ are fully faithful.
+  All of the functors $\Set \to \Set^{\down}$ are fully faithful.
 \end{prop}
@@
 There is an adjoint triple $\begin{tikzcd} \ast \arrow[r,leftarrow] \arrow[r,
-  bend left] \arrow[r, bend right] & \downarrow \end{tikzcd}$. The middle three
+  bend left] \arrow[r, bend right] & \down \end{tikzcd}$. The middle three
 functors are given by restricting along this adjoint triple; the outer two are
@@
 fact an identity), so $!_{(-)}$ is fully faithful. Therefore, all the functors
-going from $\Set \to \Set^{\downarrow}$ are fully faithful.
+going from $\Set \to \Set^{\down}$ are fully faithful.
 \end{proof}
@@
 \begin{proof}
-  To see that $!_{(-)}$ preserves connected colimits, recall that colimits in $\Set^{\downarrow}$ are calculated pointwise. It remains to show, then, that the map
+  To see that $!_{(-)}$ preserves connected colimits, recall that colimits in $\Set^{\down}$ are calculated pointwise. It remains to show, then, that the map
   \[
@@
   \]
-  is an isomorphism in $\Set^{\downarrow}$, for which it suffices to show that
+  is an isomorphism in $\Set^{\down}$, for which it suffices to show that
   $\colim \ast$ is terminal. But the colimit of the terminal diagram is the set
@@
 \begin{defn}
-  The functor $!_0 : \downarrow \to \Set\op$ picking out the terminal morphism
+  The functor $!_0 : \down \to \Set\op$ picking out the terminal morphism
   $!_0 : 0 \to 1$ by precomposition an evaluation functor
-  $$\Set^{\downarrow} \xleftarrow{\ev_{!_0}} \Fun(\Set\op, \Set).$$
+  $$\Set^{\down} \xleftarrow{\ev_{!_0}} \Fun(\Set\op, \Set).$$
   This functor admits a right adjoint by right Kan extension; we define the
-  \emph{Dirichlet extent} functor $\ext : \Set^{\downarrow} \to \Fun(\Set\op,
+  \emph{Dirichlet extent} functor $\ext : \Set^{\down} \to \Fun(\Set\op,
   \Set)$ to be this right adjoint:
@@
   The functor $\ext$ is fully faithful, giving an equivalence
-  $$\Set^{\downarrow} \simeq \Dir$$
+  $$\Set^{\down} \simeq \Dir$$
   where $\Dir$ is the category of Dirichlet functors and natural transformations.
@@
 \begin{proof}
-Since $!_0 : \downarrow \to \Set\op$ is fully faithful, the counit of the
+Since $!_0 : \down \to \Set\op$ is fully faithful, the counit of the
 $\ev_{!_0} \vdash \ext$ adjunction --- which is the universal cell defining the
@@
 \item The restricted representable functor
-  $\Set^{\downarrow}(!_{(-)}, \pi)$.
+  $\Set^{\down}(!_{(-)}, \pi)$.
 \item The functor
-  $$S \mapsto \lim(\Hom_{\Set}(!_0, S) \to \downarrow \xto{\pi} \Set)$$
-  where $\Hom_{\Set}(!_0, S)$ is the slice category of $!_0 : \downarrow \to
+  $$S \mapsto \lim(\Hom_{\Set}(!_0, S) \to \down \xto{\pi} \Set)$$
+  where $\Hom_{\Set}(!_0, S)$ is the slice category of $!_0 : \down \to
   \Set$ over $S$.
@@
 First, we note that 
-$$S \mapsto \lim(\Hom_{\Set\op}(S, !_0) \to \downarrow \xto{\pi} \Set)$$
+$$S \mapsto \lim(\Hom_{\Set\op}(S, !_0) \to \down \xto{\pi} \Set)$$
 is the standard right Kan extension formulat for $\ext_{\pi} \equiv
@@
 
-Finally, we note that the set $\Set^{\downarrow}(!_X, \pi)$ is naturally
+Finally, we note that the set $\Set^{\down}(!_X, \pi)$ is naturally
 isomorphic to the set $\sum_{b \in B} E_b^X$.
@@
 Every set is the connected colimit of the diagram $S^{\triangleleft} \to
-\downarrow \xto{!_0} \Set$, and therefore if $D$ preserves this limit, then
+\down \xto{!_0} \Set$, and therefore if $D$ preserves this limit, then
 $D(S)$ is precisely the above limit $\ext_{D!_0}(S)$.
@@
 
-As a corllary, the equivalence $\Dir \simeq \Set^{\downarrow}$ restricts to an
+As a corllary, the equivalence $\Dir \simeq \Set^{\down}$ restricts to an
 equivalence
-$$\Dir_{\ulcorner} \simeq \Set^{\downarrow}_{\ulcorner}$$
+$$\Dir_{\ulcorner} \simeq \Set^{\down}_{\ulcorner}$$
 between Dirichlet functors and cartesian natural transformations and bundles and
@@
 is a pullback in $\Set$. We will freely use the natural isomorphism
-$D(X)\cong\Set^{\downarrow}(!_X, D!_0)$ from
+$D(X)\cong\Set^{\down}(!_X, D!_0)$ from
 \ref{prop:set.characterizing.extent}, which allows us to identify Diagram
@@
 \begin{tikzcd}
- \Set^{\downarrow}(!_{X'}, D!_0)     \ar[r, "f_{!_0,\ast}"]\ar[d, "!_g^{\ast}"']& \Set^{\downarrow}(!_{X'}, D'!_0)
+ \Set^{\down}(!_{X'}, D!_0)     \ar[r, "f_{!_0,\ast}"]\ar[d, "!_g^{\ast}"']& \Set^{\down}(!_{X'}, D'!_0)
   \ar[d, "!_{g}^{\ast}"]\\
-  \Set^{\downarrow}(!_{X}, D!_0)\ar[r, "f_{!_0, \ast}"']&
- \Set^{\downarrow}(!_X, D'!_0) 
+  \Set^{\down}(!_{X}, D!_0)\ar[r, "f_{!_0, \ast}"']&
+ \Set^{\down}(!_X, D'!_0) 
 \end{tikzcd}
@@
       "\term{cod}"] \arrow[r, leftarrow, shift right = 5, "\term{dom}"]
-      \arrow[r, shift left = 10, "!^{(-)}"]  \arrow[r, shift right = 10, "!_{(-)}"] & \Ha^{\downarrow}
+      \arrow[r, shift left = 10, "!^{(-)}"]  \arrow[r, shift right = 10, "!_{(-)}"] & \Ha^{\down}
     \end{tikzcd}
   \]
-  All of the functors $\Ha \to \Ha^{\downarrow}$ are fully faithful.
+  All of the functors $\Ha \to \Ha^{\down}$ are fully faithful.
 \end{prop}
@@
 fact an identity), so $!_{(-)}$ is fully faithful. Therefore, all the functors
-going from $\Ha \to \Ha^{\downarrow}$ are fully faithful.
+going from $\Ha \to \Ha^{\down}$ are fully faithful.
 \end{proof}
@@
 \begin{proof}
-  To see that $!_{(-)}$ preserves weakly contractible colimits, recall that colimits in $H^{\downarrow}$ are calculated pointwise. It remains to show, then, that the map
+  To see that $!_{(-)}$ preserves weakly contractible colimits, recall that colimits in $H^{\down}$ are calculated pointwise. It remains to show, then, that the map
   \[
@@
   \]
-  is an equivalence in $H^{\downarrow}$, for which it suffices to show that $\colim \ast$ is contractible.
+  is an equivalence in $H^{\down}$, for which it suffices to show that $\colim \ast$ is contractible.
 But the colimit of the terminal diagram is the (Kan-fibrant replacement of) its indexing simplicial set -- since we assumed the diagram was weakly contractible, $\colim \ast$ is contractible.
@@
 \begin{defn}
-  The functor $!_0 : \downarrow \to \Ha\op$ picking out the terminal morphism
+  The functor $!_0 : \down \to \Ha\op$ picking out the terminal morphism
   $!_0 : 0 \to 1$ by precomposition an evaluation functor
-  $$\Ha^{\downarrow} \xleftarrow{\ev_{!_0}} \Fun(\Ha\op, \Ha).$$
+  $$\Ha^{\down} \xleftarrow{\ev_{!_0}} \Fun(\Ha\op, \Ha).$$
   This functor admits a right adjoint by right Kan extension; we define the
-  \emph{Dirichlet extent} functor $\ext : \Ha^{\downarrow} \to \Fun(\Ha\op,
+  \emph{Dirichlet extent} functor $\ext : \Ha^{\down} \to \Fun(\Ha\op,
   \Ha)$ to be this right adjoint:
@@
   The functor $\ext$ is fully faithful, giving an equivalence
-  $$\Ha^{\downarrow} \simeq \Dir$$
+  $$\Ha^{\down} \simeq \Dir$$
   where $\Dir$ is the category of Dirichlet functors and natural transformations.
@@
 \begin{proof}
-Since $!_0 : \downarrow \to \Ha\op$ is fully faithful, the counit of the
+Since $!_0 : \down \to \Ha\op$ is fully faithful, the counit of the
 $\ev_{!_0} \vdash \ext$ adjunction --- which is the universal cell defining the
@@
 \item The restricted representable functor
-  $\Ha^{\downarrow}(!_{(-)}, \pi)$.
+  $\Ha^{\down}(!_{(-)}, \pi)$.
 \item The functor
-  $$S \mapsto \lim(\Hom_{\Ha}(!_0, S) \to \downarrow \xto{\pi} \Ha)$$
-  where $\Hom_{\Ha}(!_0, S)$ is the slice category of $!_0 : \downarrow \to
+  $$S \mapsto \lim(\Hom_{\Ha}(!_0, S) \to \down \xto{\pi} \Ha)$$
+  where $\Hom_{\Ha}(!_0, S)$ is the slice category of $!_0 : \down \to
   \Ha$ over $S$.
@@
 First, we note that 
-$$S \mapsto \lim(\Hom_{\Ha\op}(S, !_0) \to \downarrow \xto{\pi} \Ha)$$
+$$S \mapsto \lim(\Hom_{\Ha\op}(S, !_0) \to \down \xto{\pi} \Ha)$$
 is the right Kan extension formula for $\ext_{\pi} \equiv
@@
 
-Finally, we calculate $\Ha^{\downarrow}(!_{\ast}, \pi)$ homotopy type-theoretically:
+Finally, we calculate $\Ha^{\down}(!_{\ast}, \pi)$ homotopy type-theoretically:
 \begin{align*}
-\Ha^{\downarrow}(!_{\ast}, \pi) &= \sum_{b : \ast \to B} \sum_{f : X \to E}
+\Ha^{\down}(!_{\ast}, \pi) &= \sum_{b : \ast \to B} \sum_{f : X \to E}
                                   (\pi \circ f = b \circ !_X)\\
@@
 Every homotopy type $S$ is the weakly contractible colimit of the diagram $S^{\triangleleft} \to
-\downarrow \xto{!_0} \Ha$ because it is the colimit of the diagram $S \to \ast
+\down \xto{!_0} \Ha$ because it is the colimit of the diagram $S \to \ast
 \xto{\ast} \Ha$ and we are extending this diagram with an initial object (see
@@
 
-As a corllary, the equivalence $\Dir \simeq \Ha^{\downarrow}$ restricts to an
+As a corllary, the equivalence $\Dir \simeq \Ha^{\down}$ restricts to an
 equivalence
-$$\Dir_{\ulcorner} \simeq \Ha^{\downarrow}_{\ulcorner}$$
+$$\Dir_{\ulcorner} \simeq \Ha^{\down}_{\ulcorner}$$
 between Dirichlet functors and cartesian natural transformations and bundles and
@@
 This follows by composing the equivalence of $\Dir_{\ulcorner}$ with
-$\Ha^{\downarrow}$ from Prop
+$\Ha^{\down}$ from Prop
 \ref{prop:type.dirichlet.cartesian.iff.bundle.cartesian} with that of
 Proposition 2.4.13 of \cite{GHK:Analytic.Monads}, noting that
-$\Ha^{\downarrow}_{\ulcorner}$ is the category of $(\ast,\ast)$-polynomials. 
+$\Ha^{\down}_{\ulcorner}$ is the category of $(\ast,\ast)$-polynomials. 
 \end{proof}

### 2020-04-02 draft.tex
questions and minor edits

@@
+\section{Introduction}
 A polynomial functor $P : \Set \to \Set$ is a sum of representables
-$$P(X) := \sum_{b \in B} X^{E_b}$$
+\begin{equation}\label{eqn.poly}
+P(X) := \sum_{b \in B} X^{E_b}
+\end{equation}
 and therefore depends on a family of sets $E_b$ depending on $b\in B$. This data is known
@@
 $B$ is the set of rows and $E_b$ is the set of boxes in row $b$ (possibly empty,
-for generalities sake). We can see the polynomial functor
-\begin{equation}\label{eqn.poly}
-P(X) := \sum_{b \in B} X^{E_b}
-\end{equation}
+for generalities sake). We can see the polynomial functor \eqref{eqn.poly}
 as sending a set $X$ to the set of ways to label a row of the correponding Young
@@
 sums of contravariant representables \emph{Dirichlet functors}.
-Readers who prefer more traditional algebraic notation can see \cite{SpivakMyers}, which was the set-theoretic inspiration for the present paper.\dis{Agree?}
+Readers who prefer more traditional algebraic notation can see \cite{SpivakMyers}, which was the set-theoretic inspiration for the present paper.\dis{Agree?
+Maybe there's a better place to put this?}
 
@@
     Or, equivalently, a natural isomorphism of $P$ with the composite
-    $$\Set \xto{E^{\ast}} \Set_{/E} \xto{\pi_!} \Set_{/B} \xto{B_\ast} \Set.$$
+    $$\Set \xto{\dis{\Delta_{!_E}}} \Set_{/E} \xto{\dis{\Pi_\pi}} \Set_{/B} \xto{\dis{\Sigma_{!_B}}} \Set.$$
   \item $P$ is accessible and preserves connected limits.
@@
   Or, equivalently, a natural isomorphism of $D$ with the composite
-  $$\Set\op \xto{(B^{\ast})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
-  \xto{B_{\ast}} \Set.$$
+  $$\Set\op \xto{(\Delta_{!_B})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
+  \xto{\Sigma_{!_B}} \Set.$$
 \item $D$ preserves connected limits.
@@
 Note that we no longer need to assume accessiblity. This is a general feature of
-the theory of Dirichlet functors; it is a bit ``smaller'' and more maneageable
+the theory of Dirichlet functors; it is a bit ``smaller'' and more manageable
 than that of polynomials. In particular, a Dirichlet functor is determined by
-its action on the terminal morphism $!_0 : 0 \to \ast$ of the empty set. As a corollary, Dirichlet functors form a topos.
+its action on the terminal morphism $!_0 : 0 \to \ast$ of the empty set \dis{also the terminal twisted arrow; any relation to GHK?}. As a corollary, Dirichlet functors form a topos.
 
@@
 $$\Set^{\down} \simeq \Dir$$
-between bundles and Dirichlet functors, with inverse given by evalutation at
+between the topos of bundles and the category of Dirichlet functors, with inverse given by evalutation at
 $!_0 : 0 \to \ast$.
@@
 the same data --- a bundle $\pi : E \to B$ of sets. Accordingly, one would
-expect a transformation
+expect for any set $N$ a transformation
 $$X^N \mapsto N^X$$
@@
 natural transformations between each sort of functor induce different morphisms
-between the bundles; natural tranformations between polynomial functors induce
+between the bundles; natural transformations between polynomial functors induce
 contravariant bundle morphisms, while natural transformations between Dirichlet
@@
 for sets $C_n$ on which the symmetric groups $\Aut(\underline{n})$ act freely
-(for \emph{finitary} $P$, commuting with filtered colimits).
+(for \emph{finitary} functors $P$, i.e.\ those that commute with filtered colimits).
 The generating functors for general combinatorial species --- the \emph{analytic
@@
 $$\type{Sym}X := \sum_{n : \Nb} X^n \sslash n!$$
+\dis{This is the homotopy quotient?}
 
-GHK prove $\infty$-categorical analogues of the above Theorem
+Let $\Ha$ be the $\infty$-category of homotopy types. GHK prove $\infty$-categorical analogues of the above Theorem
 \ref{thm:polynomial.set.characterization}.
 \begin{thm}[\cite{GHK:Analytic.Monads}]\label{thm:polynomial.type.characterization}
-Let $P : \Ha \to \Ha$ be a functor on the $\infty$-category of homotopy types.
-Then the following are equivalent:
+For any functor $P : \Ha \to \Ha$, the following are equivalent:
   \begin{enumerate}
@@
 
-Note that while this is a strong analogue, it is not a direct generalization:
-not all connected limits are weakly contractible.
+Note that while this is a strong analogue, it is not a direct generalization of \cref{thm:polynomial.set.characterization}:
+though it is true that in 1-categories all connected limits are weakly contractible, this is not true in general.
 
@@
 \ref{thm:dirichlet.set.characterization} and
-\ref{thm:dirichlet.set.equivalence}. In particular, we will prove the following.
+\ref{thm:dirichlet.set.equivalence}. \dis{What analogue of \ref{thm:dirichlet.set.equivalence} are we proving?} In particular, we will prove the following.
 
 \begin{thm}\label{thm:dirichlet.type.characterization}
-Let $D : \Set\op \to \Set$ be a contravariant functor. Then the following are
+Let $D : \Set\op \to \Set$ \dis{Do you mean $\Ha$ here?} be a contravariant functor. Then the following are
 equivalent.
 \begin{enumerate}
-\item $D$ is Dirichlet.
+\item $D$ is Dirichlet. \dis{In what sense?}
 \item There is a bundle $\pi : E \to B$ of homotopy types together with a natural equivalence
@@
 categorification of Hasse-Weil Zeta functions. We will recall some facts about
-homotopy cardinality and construct these Zeda functors as ordinary Dirichlet
+homotopy cardinality and construct these Zeta functors as ordinary Dirichlet
 functors in our setting. We leave the investigation of Euler product formulas
@@
 Before diving in to the theory of Dirichlet functors, let's first consider the
-category $\Set^{\down}$ of bundles of sets.
+category $\Set^{\down}$ of bundles of sets and univariant bundle maps.
 
@@
   \]
-  All of the functors $\Set \to \Set^{\down}$ are fully faithful.
+  All three functors $\Set \to \Set^{\down}$ are fully faithful.\dis{I had six; why leave one off?}
 \end{prop}
@@
   bend left] \arrow[r, bend right] & \down \end{tikzcd}$. The middle three
-functors are given by restricting along this adjoint triple; the outer two are
+functors---$\term{cod}$, $\const$, and $\term{dom}$---are given by restricting along this adjoint triple; the outer two are
 given by Kan extending, or more concretely:
-  $$X \mapsto \begin{tikzcd} 0 \arrow[d, "!^X"] \\ X \end{tikzcd}$$
-  $$X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}$$
-It is easy to see that the unit $X \to \term{dom} !_{X}$ is an isomorphism (it is in
-fact an identity), so $!_{(-)}$ is fully faithful. Therefore, all the functors
+  \begin{equation}\label{eqn.bangbang}
+  X \mapsto \begin{tikzcd} 0 \arrow[d, "!^X"] \\ X \end{tikzcd}
+  \qquad\text{and}\qquad
+  X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}
+  \end{equation}
+\dis{Shouldn't the notation $!^X$ and $!_X$ be switched, so that $X$ is contravariant in $X\to \ast$ and covariant in $0\to X$?
+It also matches the side of the arrow that $X$ is on in \eqref{eqn.bangbang}.} It is easy to see that the unit $X \to \term{dom} !_{X}$ is an isomorphism (it is in
+fact an identity), so $!_{(-)}$ is fully faithful. Therefore, all three functors
 going from $\Set \to \Set^{\down}$ are fully faithful.
@@
 \begin{lem}\label{lem:bang.preserves.connected.colimits}
-  The functor $!_{(-)}$ preserves connected colimits.
+  The functor $!_{(-)}\colon\Set\to\Set^{\down}$ from \eqref{eqn.bangbang} preserves connected colimits.
 \end{lem}
 \begin{proof}
-  To see that $!_{(-)}$ preserves connected colimits, recall that colimits in $\Set^{\down}$ are calculated pointwise. It remains to show, then, that the map
+  To see that $!_{(-)}$ preserves connected colimits, recall that colimits in $\Set^{\down}$ are calculated pointwise. It remains to show, then, that the map of bundles
   \[
@@
   is an isomorphism in $\Set^{\down}$, for which it suffices to show that
-  $\colim \ast$ is terminal. But the colimit of the terminal diagram is the set
-  of connected components of its indexing diagram -- since we assumed the
-  indexing diagram was connected, this contains a single element.
+  $\colim \ast$ is terminal. But the colimit of a diagram of terminal objects is the set
+  of connected components of its indexing category. Since we assumed the
+  indexing category was connected, this contains a single element.
 \end{proof}
 
-Now we will define the \emph{extent} of a bundle, the Dirichlet functor it
+Now we will define the \emph{extent} of a bundle $\pi$ to be the Dirichlet functor $\ext_\pi: \Set\to\Set$ that it
 corresponds to. This sends a bundle
@@
 
-\begin{defn}
-  The functor $!_0 : \down \to \Set\op$ picking out the terminal morphism
-  $!_0 : 0 \to 1$ by precomposition an evaluation functor
+\begin{defn}\label{def.extent}
+  Consider the functor $!_0 : \down \to \Set\op$ picking out the unique morphism $1\to 0$ in $\Set\op$. Sending a functor $\Set\op\to\Set$ to its precomposition with $!_0$ gives an evaluation functor
   $$\Set^{\down} \xleftarrow{\ev_{!_0}} \Fun(\Set\op, \Set).$$
-  This functor admits a right adjoint by right Kan extension; we define the
+  \dis{I worry about the size of $\Fun(\Set\op,\Set)$.}
+  This functor admits a right adjoint by right Kan extension along $!_0$; we define the
   \emph{Dirichlet extent} functor $\ext : \Set^{\down} \to \Fun(\Set\op,
-  \Set)$ to be this right adjoint:
+  \Set)$ to be this right adjoint. It sends any bundle $\pi$ to
   $$\ext_{\pi} :\equiv \term{ran}_{!_0} \pi.$$
@@
   \begin{enumerate}
-  \item The extent $\ext_{\pi} : \Set\op \to \Set$ of $\pi$.
+  \item The extent $\ext_{\pi} : \Set\op \to \Set$ of $\pi$ from \cref{def.extent}.
+\item \dis{Add this?} The pullback functor sending a set $S$ to 
+\[
+\begin{tikzcd}
+	\ext_\pi(S)\ar[r]\ar[d]\arrow[dr, phantom,
+      "\ulcorner" very near start]&
+	B\ar[d]\\
+	\Set(S,E)\ar[r]&
+	\Set(S,B)
+\end{tikzcd}
+\]
   \item The functor
@@
   where $\Hom_{\Set}(!_0, S)$ is the slice category of $!_0 : \down \to
-  \Set$ over $S$.
+  \Set$ over $S$.\dis{Is this Emily's notation for comma category?}
 \item The functor
@@
 $$S \mapsto \lim(\Hom_{\Set\op}(S, !_0) \to \down \xto{\pi} \Set)$$
-is the standard right Kan extension formulat for $\ext_{\pi} \equiv
-\term{ran}_{!_0} \pi$. Noting that $\Hom_{\Set}(!_0, S) = \Hom_{\Set\op}(S,
+is the standard right Kan extension formula for $\ext_{\pi} \equiv
+\term{ran}_{!_0} \pi$ as a conical limit. Noting that $\Hom_{\Set}(!_0, S) = \Hom_{\Set\op}(S,
 !_0)$, we see that (1) is equivalent to (4). Furthermore, noting that
@@
 Now, we note that every set $S$ is the colimit of the diagram $S^{\triangleleft}
-\xto{\ast^{\triangleleft}} \xto{!_0} \Set$, namely:
+\xto{\ast^{\triangleleft}}\down \xto{!_0} \Set$, namely:
 \[
@@
 Finally, we note that the set $\Set^{\down}(!_X, \pi)$ is naturally
-isomorphic to the set $\sum_{b \in B} E_b^X$.
+isomorphic to the set $\sum_{b \in B} E_b^X$.\dis{add pullback?}
 \end{proof}
@@
 
-Every set is the connected colimit of the diagram $S^{\triangleleft} \to
+Every set $S$ is the connected colimit of the diagram $S^{\triangleleft} \to
 \down \xto{!_0} \Set$, and therefore if $D$ preserves this limit, then
@@
 $$\Dir_{\ulcorner} \simeq \Set^{\down}_{\ulcorner}$$
-between Dirichlet functors and cartesian natural transformations and bundles and
-pullback sqaures.
+between Dirichlet functors with cartesian natural transformations and bundles with
+pullback squares.
 \end{prop}
@@
 \end{proof}
-
+\dis{How does this topos compare to the topos $\Dir_{/D}$?}
 \section{Dirichlet Functors on Homotopy Types} \label{sec:type.level}
@@
   \]
-  All of the functors $\Ha \to \Ha^{\down}$ are fully faithful.
+  All three functors $\Ha \to \Ha^{\down}$ are fully faithful.
 \end{prop}
@@
 may calculate these as
-  $$X \mapsto \begin{tikzcd} 0 \arrow[d, "!^X"] \\ X \end{tikzcd}$$
-  $$X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}$$
+  $$X \mapsto \begin{tikzcd} 0 \arrow[d, "!^X"] \\ X \end{tikzcd}
+  \qquad\text{and}\qquad
+  X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}$$
 It is easy to see that the unit $X \to \term{dom} !_{X}$ is an equivalence (it is in
@@
 \begin{defn}
-  The functor $!_0 : \down \to \Ha\op$ picking out the terminal morphism
-  $!_0 : 0 \to 1$ by precomposition an evaluation functor
+Consider the functor $!_0 : \down \to \Ha\op$ picking out the unique morphism $1\to 0$ in $\Ha\op$. Sending a functor $\Ha\op\to\Ha$ to its precomposition with $!_0$ gives an evaluation functor
   $$\Ha^{\down} \xleftarrow{\ev_{!_0}} \Fun(\Ha\op, \Ha).$$
@@
   $$\Ha^{\down} \simeq \Dir$$
-  where $\Dir$ is the category of Dirichlet functors and natural transformations.
+  where $\Dir$ is the category of Dirichlet functors and natural transformations.\dis{What is $\Dir$; have we defined Dirichlet functors in this context?}
 \end{prop}

### 2020-04-02 draft.tex
definition of arrow (for things to come)

--- 2020-04-01 draft.tex
@@
 category $\Set^{\downarrow}$ of bundles of sets.
+
+\begin{defn}
+  We let $\downarrow$ be the walking arrow --- the category $\term{dom} \to
+  \term{cod}$ consisting of a single morphism. We denote by $\sigma : \downarrow
+  \to \downarrow\op$ the self-dualizing isomorphism of $\downarrow$, and note
+  that $\sigma\inv = \sigma\op$.
+\end{defn}
 
@@
 
+In this section, we will categorify Dirichlet series
+$$\sum_{n \in \Nb} a_n n^{-s}.$$
+
+First, we review the notion of \emph{homotopy cardinality}.
+
+\begin{defn}
+Let $B$ be a homotopy type. We define the \emph{homotopy cardinality} $#B$ to be
+the following sum:
+$$#B := \sum_{[b] \in \pi_0(B)} \prod_{n = 1}^{\infty} |\pi_n(B, b)|^{(-1)^n}$$
+
+We note that
+$$#B = \sum_{[b] \in \pi_0(B)} \frac{1}{#\Omega(B, b)}$$
+\end{defn}
+
+We will leave questions concerning the convergence and well-definedness of the
+homotopy cardinality of a type, noting only that if a type $B$ is totally finite in
+that it has finitely many connected components, its homotopy groups are finite,
+and they eventually vanish, then $#B$ is a finite sum of a finite product and so
+is well defined.
+
+The main lemma concerning homotopy cardinality is its behavior with respect to
+fibrations.
+\begin{lem}
+Let $\pi : E \to B$ be a map of homotopy types, and let $E_b$ denote the fiber
+over $b : B$. Then
+$$#E = \sum_{[b] \in \pi_0(B)}\frac{#E_b}{#\Omega(B, b)}.$$
+As a corollary:
+\begin{enumerate}
+\item $#(A \times B) = #A \cdot #B$ and so $#(B^n) = (#B)^n$.
+\item If $B$ is pointed and connected and $F$ is the fiber of $\pi$ over the
+  basepoint, then $#E = #F \cdot #B$.
+\item If $A_n$ is a family of types for $n : \Nb$, then $#(\sum_n A_n) = \sum_n #A_n$.
+\end{enumerate}
+\end{lem}
+\begin{proof}
+  We note that by the long exact sequence of homotopy groups, we have that
+  $$|\pi_n(E, e)| = |\pi_n(E_{\pi e}, e)|\cdot |\pi_n(B, \pi e)|$$
+  Therefore, we may calculate
+  \begin{align*}
+    #E &= \sum_{[e] \in \pi_0(E)}\prod_{n=1}^{\infty} |\pi_n(E, e)|^{(-1)^n}\\
+    &= \sum_{[b] \in \pi_0(B)} \sum_{[e] \in \pi_0(E_b)} \prod_{n=1}^{\infty} (|\pi_n(E_{b}, e)|\cdot |\pi_n(B, b)|)^{(-1)^n}\\
+    &= \sum_{[b] \in \pi_0(B)}\prod_{n=1}^{\infty} |\pi_n(B, b)|^{(-1)^n} \sum_{[e] \in \pi_0(E_b)} \prod_{n=1}^{\infty} |\pi_n(E_{b}, e)|^{(-1)^n}\\
+    &= \sum_{[b] \in \pi_0(B)}\frac{#E_b}{\frac{#\Omega(B, b)}}.
+  \end{align*}
+
+  We may then take various maps $\pi : E \to B$ to recover the corollaries:
+  \begin{enumerate}
+  \item Take the projection $A \times B \to B$.
+  \item Take the map $\pi : E \to B$, noting that if $B$ is pointed connected then $#B =
+    \frac{1}{\Omega B}$.
+  \item Take the projection $\sum_n A_n \to \Nb$.
+  \end{enumerate}
+\end{proof}
+
+Now, we note that if $B$ is connected, then $#B = \frac{1}{#\Omega(B, b)}$ for
+any point $b : B$. Therefore, if $B$ is connected with finite homs of
+cardinality $n$, then $#B = \frac{1}{n}$ and so $#(B^s) = n^{-s}$. This is the
+observation --- originally due to Baez and Dolan in \emph{This Weeks Finds}
+(cite) --- that we will use to categorify Dirichlet series.
+
+\begin{defn}
+A homotopy type $B$ is \emph{locally finite and connected}, or \emph{lfc}, if it
+is $0$-connected and its homs are finite.
+
+We denote by $\type{lfc}$ the homotopy type of lfc types, and note that the
+bundle $\fst : \type{lfc}_{\ast} \to \type{lfc}$ forgetting the point of a
+pointed lfc type classifies maps with lfc fibers.
+\end{defn}
+
 \section{Appendix}

### 2020-04-02 draft.tex

--- 2020-04-02 draft.tex
@@
 Before diving in to the theory of Dirichlet functors, let's first consider the
-category $\Set^{\down}$ of bundles of sets and univariant bundle maps.
+category $\Set^{\down}$ of bundles of sets and univariant bundle maps. For our
+proofs to go smoothly, we will need to explicitly keep track of the
+self-dualizing isomorphism $\downarrow \xto{\sim} \downarrow\op$ on the walking arrow.
+
+\begin{defn}
+  We let $\downarrow$ be the walking arrow --- the category $\term{dom} \to
+  \term{cod}$ consisting of a single morphism. We denote by $\sigma : \downarrow
+  \to \downarrow\op$ the self-dualizing isomorphism of $\downarrow$, and note
+  that $\sigma\inv = \sigma\op$.
+\end{defn}
 
@@
 
-We prove a quick fact we will use later.
+We prove a few quick facts we will use later.
 \begin{lem}\label{lem:bang.preserves.connected.colimits}
@@
 
+\begin{lem}
+The Yoneda embedding $\yo : \downarrow\op \to \Set^{\downarrow}$ is equal to the
+composite $$\downarrow\op \xto{\sigma\op} \downarrow \xto{!_{0}} \Set
+\xto{!_{(-)}} \Set^{\downarrow}.$$
+
+As a corollary, any $\pi : \downarrow \to \Set$ equals the composite
+$$\downarrow \xto{\sigma} \downarrow\op \xto{!_0\op} \Set\op \xto{!_{(-)}\op}
+(\Set^{\downarow})\op \xto{\Set^{\downarrow}(-, \pi)} \Set$$
+by the Yoneda lemma.
+\end{lem}
+\begin{proof}
+One checks directly.
+\end{proof}
+
 Now we will define the \emph{extent} of a bundle $\pi$ to be the Dirichlet functor $\ext_\pi: \Set\to\Set$ that it
@@
   $$\Set^{\down} \xleftarrow{\ev_{!_0}} \Fun(\Set\op, \Set).$$
-  \dis{I worry about the size of $\Fun(\Set\op,\Set)$.}
-  This functor admits a right adjoint by right Kan extension along $!_0$; we define the
+  \dis{I worry about the size of $\Fun(\Set\op,\Set)$.}\jaz{No need to worry,
+    you are extending functors with small domains along a functor with small
+    domains. Limits in any functor category (regardless of size) are calculated
+    pointwise, and we are taking small limits.} 
+  This functor admits a right adjoint by right Kan extension along $!_0\op \circ
+  \sigma : \downarrow \to \Set\op$; we define the
   \emph{Dirichlet extent} functor $\ext : \Set^{\down} \to \Fun(\Set\op,
   \Set)$ to be this right adjoint. It sends any bundle $\pi$ to
-  $$\ext_{\pi} :\equiv \term{ran}_{!_0} \pi.$$
+  $$\ext_{\pi} :\equiv \term{ran}_{!_0\op \circ \sigma} \pi.$$
 \end{defn}
@@
   \item The extent $\ext_{\pi} : \Set\op \to \Set$ of $\pi$ from \cref{def.extent}.
+  \item The functor
+    $$S \mapsto \sum_{b \in B} E_b^S,$$
+    or equivalently the composite
+  $$\Set\op \xto{(B^{\ast})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
+  \xto{B_{\ast}} \Set.$$
 \item \dis{Add this?} The pullback functor sending a set $S$ to 
@@
 \]
-  \item The functor
-    $$S \mapsto \sum_{b \in B} E_b^S,$$
-    or equivalently the composite
-  $$\Set\op \xto{(B^{\ast})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
-  \xto{B_{\ast}} \Set.$$
 \item The restricted representable functor
@@
   where $\Hom_{\Set}(!_0, S)$ is the slice category of $!_0 : \down \to
-  \Set$ over $S$.\dis{Is this Emily's notation for comma category?}
+  \Set$ over $S$.\dis{Is this Emily's notation for comma category?}\jaz{yes in
+    her Elements}
 \item The functor
@@
 \begin{proof}
+\jaz{We could slickly do this using the fact that vertical maps are orthogonal
+  to horizontal maps.}
+
 We want to show that for any $f\colon D\to D'$ the square
@@
 \dis{How does this topos compare to the topos $\Dir_{/D}$?}
+\jaz{The following story: it generalizes to $\infty$-categories, which is why
+  I'm writing it this way.}
+
+\begin{defn}
+A \emph{modality} on a category $\Ca$ is a stable orthogonal factorization
+system $(\La, \Ra)$. \jaz{see Anel Biederman Finster Joyal \cite{ABFJ:Blakers.Massey}}
+
+A modality is \emph{lex} if for any square
+\[
+  % https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAEEQBfU9TXfIRRkAjFVqMWbAELdeIDNjwEiI8uPrNWiEAGE5fJYNWkx1TVJ0ARbuJhQA5vCKgAZgCcIAWyRkQOCCQAJnNJbRBXAwjPH0QQ-0DEAGZQrTYHKI9vX2oApDUQBjoAIxgGAAV+ZSEQdywHAAscEFTLEAbMmPzcxJSJNJ0AaxbCkrLKoxUdOsbmrgouIA
+\begin{tikzcd}
+A \arrow[r, "h"] \arrow[d, "g"'] & C \arrow[d, "f"] \\
+B \arrow[r, "k"']                & D               
+\end{tikzcd}
+\]
+where $f$ and $g$ are in $\La$ and $h$ and $k$ are in $\Ra$ is a pullback. (See
+Theorem 3.11 of \cite{RSS:Modalties.in.HoTT}, condition (vii).)
+
+We say that a modality $(\La, \Ra)$ is \emph{contained in} $(\La', \Ra')$ ---
+written $(\La, \Ra) \leq (\La', \Ra')$ --- if $\Ra \subseteq \Ra'$.
+\end{defn}
+
+\begin{prop}
+If $(\La, \Ra)$ is a modality on $\Ca$, then there is an induced modality $(\La_X,
+\Ra_X)$ on $\Ca_{/X}$ \jaz{I'll flesh this out in a bit, see
+  \cite{ABFJ:Blakers.Massey}}. If $(\La, \Ra)$ is lex, then so is $(\La_X, \Ra_X)$.
+\end{prop}
+
+\begin{prop}
+There is an equivalence between the order of lex modalities on a topos and the
+order of subtoposes.
+\end{prop}
+\begin{proof}
+Idea: we take those objects whose terminal morphism is in $\Ra$.
+\end{proof}
+
+\begin{prop}
+The orthogonal factorization system $(\term{vertical}, \term{cartesian})$ on
+$\Set^{\downarrow}$ (given by the cartesian fibration $\Set\op \to \Set$) is a
+lex modality.
+\end{prop}
+
+\begin{thm}
+The left exact modality $(\term{vertical}_D, \term{cartesian}_D)$ on
+$\Set^{\downarrow}_{/\pi}$ exhibits $\Set^{\downarrow}_{/_{\ulcorner} \pi}$ as a
+subtopos.
+
+As a corollary, we have a subtopos inclusion $\Dir_{/_{\ulcorner} D}
+\hookrightarrow \Dir_{/D}$. \jaz{So $\Dir_{/D}$ is equivalently a presheaf topos
+  $\Set^{\downarrow/D}$; what is the topology that presents $\Dir_{/_{\ulcorner}
+  D}$ as a sheaf topos?}
+\end{thm}
+
 \section{Dirichlet Functors on Homotopy Types} \label{sec:type.level}
@@
 
+In this section, we will categorify Dirichlet series
+$$\sum_{n \in \Nb} a_n n^{-s}.$$
+
+First, we review the notion of \emph{homotopy cardinality}.
+
+\begin{defn}
+Let $B$ be a homotopy type. We define the \emph{homotopy cardinality} $\#B$ to be
+the following sum:
+$$\#B := \sum_{[b] \in \pi_0(B)} \prod_{n = 1}^{\infty} |\pi_n(B, b)|^{(-1)^n}$$
+
+We note that
+$$\#B = \sum_{[b] \in \pi_0(B)} \frac{1}{\#\Omega(B, b)}$$
+\end{defn}
+
+We will leave questions concerning the convergence and well-definedness of the
+homotopy cardinality of a type, noting only that if a type $B$ is totally finite in
+that it has finitely many connected components, its homotopy groups are finite,
+and they eventually vanish, then $\#B$ is a finite sum of a finite product and so
+is well defined.
+
+The main lemma concerning homotopy cardinality is its behavior with respect to
+fibrations.
+\begin{lem}
+Let $\pi : E \to B$ be a map of homotopy types, and let $E_b$ denote the fiber
+over $b : B$. Then
+$$\#E = \sum_{[b] \in \pi_0(B)}\frac{\#E_b}{\#\Omega(B, b)}.$$
+As a corollary:
+\begin{enumerate}
+\item $\#(A \times B) = \#A \cdot \#B$ and so $\#(B^n) = (\#B)^n$.
+\item If $B$ is pointed and connected and $F$ is the fiber of $\pi$ over the
+  basepoint, then $\#E = \#F \cdot \#B$.
+\item If $A_n$ is a family of types for $n : \Nb$, then $\#(\sum_n A_n) = \sum_n \#A_n$.
+\end{enumerate}
+\end{lem}
+\begin{proof}
+  We note that by the long exact sequence of homotopy groups, we have that
+  $$|\pi_n(E, e)| = |\pi_n(E_{\pi e}, e)|\cdot |\pi_n(B, \pi e)|$$
+  Therefore, we may calculate
+  \begin{align*}
+    \#E &= \sum_{[e] \in \pi_0(E)}\prod_{n=1}^{\infty} |\pi_n(E, e)|^{(-1)^n}\\
+    &= \sum_{[b] \in \pi_0(B)} \sum_{[e] \in \pi_0(E_b)} \prod_{n=1}^{\infty} (|\pi_n(E_{b}, e)|\cdot |\pi_n(B, b)|)^{(-1)^n}\\
+    &= \sum_{[b] \in \pi_0(B)}\prod_{n=1}^{\infty} |\pi_n(B, b)|^{(-1)^n} \sum_{[e] \in \pi_0(E_b)} \prod_{n=1}^{\infty} |\pi_n(E_{b}, e)|^{(-1)^n}\\
+    &= \sum_{[b] \in \pi_0(B)}\frac{\#E_b}{\#\Omega(B, b)}.
+  \end{align*}
+
+  We may then take various maps $\pi : E \to B$ to recover the corollaries:
+  \begin{enumerate}
+  \item Take the projection $A \times B \to B$.
+  \item Take the map $\pi : E \to B$, noting that if $B$ is pointed connected then $\#B =
+    \frac{1}{\Omega B}$.
+  \item Take the projection $\sum_n A_n \to \Nb$.
+  \end{enumerate}
+\end{proof}
+
+Now, we note that if $B$ is connected, then $\#B = \frac{1}{\#\Omega(B, b)}$ for
+any point $b : B$. Therefore, if $B$ is connected with finite homs of
+cardinality $n$, then $\#B = \frac{1}{n}$ and so $\#(B^s) = n^{-s}$. This is the
+observation --- originally due to Baez and Dolan in \emph{This Weeks Finds}
+(cite) --- that we will use to categorify Dirichlet series.
+
+\begin{defn}
+A homotopy type $B$ is \emph{locally finite and connected}, or \emph{lfc}, if it
+is $0$-connected and its homs are finite.
+
+We denote by $\type{lfc}$ the homotopy type of lfc types, and note that the
+bundle $\fst : \type{lfc}_{\ast} \to \type{lfc}$ forgetting the point of a
+pointed lfc type classifies maps with lfc fibers.
+\end{defn}
+
 \section{Appendix}

### 2020-04-02 draft.tex
MEs

@@
 \end{equation}
-and therefore depends on a family of sets $E_b$ depending on $b\in B$. This data is known
+where the family of sets $E_b$ depends on $b\in B$. This data is known
 in the computer science literature as a ``container'', but since such an indexed
@@
 $$\downarrow \xto{\sigma} \downarrow\op \xto{!_0\op} \Set\op \xto{!_{(-)}\op}
-(\Set^{\downarow})\op \xto{\Set^{\downarrow}(-, \pi)} \Set$$
+(\Set^{\downarrow})\op \xto{\Set^{\downarrow}(-, \pi)} \Set$$
 by the Yoneda lemma.

### 2020-04-03 draft.tex
fixed little bugs
more writing

@@
 \end{equation}
-where the family of sets $E_b$ depends on $b\in B$. This data is known
+and therefore depends on a family of sets $E_b$ depending on $b\in B$. This data is known
 in the computer science literature as a ``container'', but since such an indexed
@@
 
-\begin{lem}
+\begin{lem}\label{lem:set.bundle.yoneda}
 The Yoneda embedding $\yo : \downarrow\op \to \Set^{\downarrow}$ is equal to the
@@
 \begin{proof}
-TODO
+  \jaz{Need to find a good citation for this result --- that polynomial functors
+  and cartesian transforms are bundles and cartesian maps (for 1-cats).}
 \end{proof}
@@
 \dis{How does this topos compare to the topos $\Dir_{/D}$?}
-\jaz{The following story: it generalizes to $\infty$-categories, which is why
-  I'm writing it this way.}
-
-\begin{defn}
-A \emph{modality} on a category $\Ca$ is a stable orthogonal factorization
-system $(\La, \Ra)$. \jaz{see Anel Biederman Finster Joyal \cite{ABFJ:Blakers.Massey}}
-
-A modality is \emph{lex} if for any square
-\[
-  % https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAEEQBfU9TXfIRRkAjFVqMWbAELdeIDNjwEiI8uPrNWiEAGE5fJYNWkx1TVJ0ARbuJhQA5vCKgAZgCcIAWyRkQOCCQAJnNJbRBXAwjPH0QQ-0DEAGZQrTYHKI9vX2oApDUQBjoAIxgGAAV+ZSEQdywHAAscEFTLEAbMmPzcxJSJNJ0AaxbCkrLKoxUdOsbmrgouIA
-\begin{tikzcd}
-A \arrow[r, "h"] \arrow[d, "g"'] & C \arrow[d, "f"] \\
-B \arrow[r, "k"']                & D               
-\end{tikzcd}
-\]
-where $f$ and $g$ are in $\La$ and $h$ and $k$ are in $\Ra$ is a pullback. (See
-Theorem 3.11 of \cite{RSS:Modalties.in.HoTT}, condition (vii).)
-
-We say that a modality $(\La, \Ra)$ is \emph{contained in} $(\La', \Ra')$ ---
-written $(\La, \Ra) \leq (\La', \Ra')$ --- if $\Ra \subseteq \Ra'$.
-\end{defn}
-
-\begin{prop}
-If $(\La, \Ra)$ is a modality on $\Ca$, then there is an induced modality $(\La_X,
-\Ra_X)$ on $\Ca_{/X}$ \jaz{I'll flesh this out in a bit, see
-  \cite{ABFJ:Blakers.Massey}}. If $(\La, \Ra)$ is lex, then so is $(\La_X, \Ra_X)$.
-\end{prop}
-
-\begin{prop}
-There is an equivalence between the order of lex modalities on a topos and the
-order of subtoposes.
-\end{prop}
-\begin{proof}
-Idea: we take those objects whose terminal morphism is in $\Ra$.
-\end{proof}
-
-\begin{prop}
-The orthogonal factorization system $(\term{vertical}, \term{cartesian})$ on
-$\Set^{\downarrow}$ (given by the cartesian fibration $\Set\op \to \Set$) is a
-lex modality.
-\end{prop}
-
-\begin{thm}
-The left exact modality $(\term{vertical}_D, \term{cartesian}_D)$ on
-$\Set^{\downarrow}_{/\pi}$ exhibits $\Set^{\downarrow}_{/_{\ulcorner} \pi}$ as a
-subtopos.
-
-As a corollary, we have a subtopos inclusion $\Dir_{/_{\ulcorner} D}
-\hookrightarrow \Dir_{/D}$. \jaz{So $\Dir_{/D}$ is equivalently a presheaf topos
-  $\Set^{\downarrow/D}$; what is the topology that presents $\Dir_{/_{\ulcorner}
-  D}$ as a sheaf topos?}
-\end{thm}
+\jaz{See the $\infty$-categorical case. The same story can be told for
+  1-categories, but perhaps we should tell it some other way?}
 
@@
 
+\begin{lem}\label{lem:type.bundle.yoneda}
+The Yoneda embedding $\yo : \downarrow\op \to \Ha^{\downarrow}$ is equivalent to the
+composite $$\downarrow\op \xto{\sigma\op} \downarrow \xto{!_{0}} \Ha
+\xto{!_{(-)}} \Ha^{\downarrow}.$$
+
+As a corollary, for any $\pi : \downarrow \to \Ha$, $\down\op \xto{\sigma\op}
+\down \xto{\pi} \Ha$ equals the composite
+$$\down\op \xto{!_0\op} \Ha\op \xto{!_{(-)}\op}
+(\Ha^{\downarrow})\op \xto{\Ha^{\downarrow}(-, \pi)} \Ha$$
+by the Yoneda lemma.
+\end{lem}
+\begin{proof}
+  This follows from Lemma \ref{lem:set.bundle.yoneda}, since $\downarrow$ is a $1$-category.
+\end{proof}
+
 Now we will define the \emph{extent} of a bundle, the Dirichlet functor it
@@
   \xto{B_{\ast}} \Ha.$$
+\item The pullback functor sending a set $S$ to 
+\[
+\begin{tikzcd}
+	\ext_\pi(S)\ar[r]\ar[d]\arrow[dr, phantom,
+      "\ulcorner" very near start]&
+	B\ar[d]\\
+	\Ha(S,E)\ar[r]&
+	\Ha(S,B)
+\end{tikzcd}
+\]
 \item The restricted representable functor
@@
 \item The functor
-  $$S \mapsto \lim(\Hom_{\Ha}(!_0, S) \to \down \xto{\pi} \Ha)$$
+  $$S \mapsto \lim(\Hom_{\Ha}(!_0, S)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Ha)$$
   where $\Hom_{\Ha}(!_0, S)$ is the slice category of $!_0 : \down \to
@@
 \item The functor
-  $$S \mapsto \lim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft}
+  $$S \mapsto \lim(( S^{\triangleleft} )\op \xto{( !^{\triangleleft} )\op}
+  (\ast^{\triangleleft})\op \xto{\sigma\op} \down
   \xto{\pi} \Ha)$$
@@
 First, we note that 
-$$S \mapsto \lim(\Hom_{\Ha\op}(S, !_0) \to \down \xto{\pi} \Ha)$$
+$$S \mapsto \lim(\Hom_{\Ha\op}(S, !_0\op \circ \sigma) \to \down \xto{\pi} \Ha)$$
 is the right Kan extension formula for $\ext_{\pi} \equiv
-\term{ran}_{!_0} \pi$ --- see Corollary 9.5.3 of \cite{RV:Elements}. Noting that $\Hom_{\Ha}(!_0, S) = \Hom_{\Ha\op}(S,
-!_0)$, we see that (1) is equivalent to (4). Furthermore, noting that
-$\Hom_{\Ha}(!_0, S)$ simply adjoins an initial object to (the discrete
-category) $S$, we see that (4) is equivalent to (5).
+\term{ran}_{!_0} \pi$ --- see Corollary 9.5.3 of \cite{RV:Elements}. Now,
+$\Hom_{\Ha\op}(S, !_0\op \circ \sigma) \simeq \Hom_{\Ha}(!_0 \circ \sigma\op,
+S)\op$ over $\down$, which we may see by noting that $(-)\op : {\infty}\Cat \to {\infty}\Cat^{\term{co}}$ is a cosmological equivalence and therefore preserves
+comma squares. Furthermore, we have the following equivalence:
+\[
+% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAB12AJCAWwH1gnLnQC+ACgCE-YgAJOAYywAnBfPbYA5rzqcIaUrIDKASj1oQo0uky58hFGQCMVWoxZthfQcLFSZhqbmltYgGNh4BERO5K70zKyIHOxQEADuhFY2EfbRpC7U8R5JnKkZwaKuMFCa8ESgAGbKfEhkIDgQSDEgDHQARjAMAAq2kQ4gyliaABY4IIXuicnYvCGNzauIbR1IAExZIE0tiLvUO4gAzAsJnhpTOmuHG11nnZeVokA
+\begin{tikzcd}
+{\Hom_{\Ha}(!_0 \circ \sigma\op, S)\op} \arrow[d, "\sim"'] \arrow[r] & \down \arrow[d, "\sigma"] \\
+{\Hom_{\Ha}(!_0, S)\op} \arrow[r]                                    & \down\op                 
+\end{tikzcd}
+\]
+and therefore we may equivalently calculate this limit as 
+$$\lim(\Hom_{\Ha}(!_0, S)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Ha).$$
+This gives us the equivalence between (1) and (5). By Lemma
+\ref{lem:slice.cone.equiv}, we see also that (5) and (6) are equivalent.
 
-Now, we note that every set $S$ is the colimit of the diagram $S^{\triangleleft}
-\xto{\ast^{\triangleleft}} \xto{!_0} \Ha$. Since, by Lemma \ref{lem:bang.preserves.weakly.contractible.colimits}, $!_{(-)}$
-preserves weakly contractible colimits, {\color{red} TODO}.
+Now, using Lemmas \ref{lem:bang.preserves.weakly.contractible.colimits} and \ref{lem:type.bundle.yoneda}, we may make
+the following calculation identifying (4) with (6):
 
-Finally, we calculate $\Ha^{\down}(!_{\ast}, \pi)$ homotopy type-theoretically:
 \begin{align*}
-\Ha^{\down}(!_{\ast}, \pi) &= \sum_{b : \ast \to B} \sum_{f : X \to E}
-                                  (\pi \circ f = b \circ !_X)\\
-                                &= \sum_{b : B} \sum_{f : X \to E} \prod_{x : X} (\pi (f x) = b) \\
-                                &= \sum_{b : B} \left( X \to \sum_{e : E} (\pi e = b) \right) \\
-                                  &\equiv \sum_{b : B}E_b^X.
+  \Ha^{\down}(!_S, \pi) &= \Ha^{\down}(!_{\colim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft} \xto{!_0} \Ha)}, \pi) \\
+  &\simeq \Ha^{\down}(\colim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft} \xto{!_0} \Ha \xto{!_{(-)}} \Ha^{\down}), \pi)\\
+&\simeq \lim((S^{\down})\op \xto{(!^{\triangleleft})\op} (\ast^{\triangleleft})\op \xto{!_0\op} \Ha\op \xto{!_{(-)}} (\Ha^{\down})\op \xto{\Ha^{\down}(-, \pi)} \Ha) \\
+&\simeq \lim((S^{\down})\op \xto{(!^{\triangleleft})\op} (\ast^{\triangleleft})\op \xto{\sigma\op} \down \xto{\pi} \Ha).
 \end{align*}
-{\color{red} But I need a better argument to show that this is a natural
-  equivalence of functors --- something involving cartesian fibrations etc etc etc}
+
+\jaz{TODO: (3) with (4) and (2) and (4)}
 \end{proof}
@@
 Every homotopy type $S$ is the weakly contractible colimit of the diagram $S^{\triangleleft} \to
-\down \xto{!_0} \Ha$ because it is the colimit of the diagram $S \to \ast
-\xto{\ast} \Ha$ and we are extending this diagram with an initial object (see
-Lemma \ref{lem:extending.diagram.with.initial.object.has.same.colimit}). Therefore if $D$ preserves this limit, then
+\down \xto{!_0} \Ha$ by Lemma \ref{lem:every.type.weakly.contractible.colimit}. Therefore if $D$ preserves this limit, then
 $D(S)$ is precisely the above limit $\ext_{D!_0}(S)$.
@@
 \end{equation}
-is a pullback in $\Set$. We will freely use the natural isomorphism
-$D(X)\cong\Set^{\down}(!_X, D!_0)$ from
+is a pullback in $\Ha$. We will freely use the natural isomorphism
+$D(X)\cong\Ha^{\down}(!_X, D!_0)$ from
 \ref{prop:set.characterizing.extent}, which allows us to identify Diagram
 \ref{eqn.type.cart2} with
-\begin{equation}\label{eqn.cart3}
+\begin{equation}\label{eqn.type.cart3}
 \begin{tikzcd}
- \Set^{\down}(!_{X'}, D!_0)     \ar[r, "f_{!_0,\ast}"]\ar[d, "!_g^{\ast}"']& \Set^{\down}(!_{X'}, D'!_0)
+ \Ha^{\down}(!_{X'}, D!_0)     \ar[r, "f_{!_0,\ast}"]\ar[d, "!_g^{\ast}"']& \Ha^{\down}(!_{X'}, D'!_0)
   \ar[d, "!_{g}^{\ast}"]\\
-  \Set^{\down}(!_{X}, D!_0)\ar[r, "f_{!_0, \ast}"']&
- \Set^{\down}(!_X, D'!_0) 
+  \Ha^{\down}(!_{X}, D!_0)\ar[r, "f_{!_0, \ast}"']&
+ \Ha^{\down}(!_X, D'!_0) 
 \end{tikzcd}
@@
 
-To complete the proof, suppose that Diagram \ref{eqn.type.cart1} is a pullback, take an arbitrary $g\colon X\to X'$, and suppose given a commutative solid-arrow diagram as shown:
-\[
-\begin{tikzcd}[sep=small]
-  X\ar[rr, "g"]\ar[dd]\ar[rd]&&
-  X'\ar[dr]\ar[dd]\ar[dl, dotted]\\&
-  D(1)\ar[rr, crossing over]&&
-  D'(1)\ar[dd]\\
-  1\ar[dr]\ar[rr, equal]&&
-  1\ar[dr]\ar[dl, dotted]\\&
-  D(0)\ar[from=uu, crossing over]\ar[rr]&&
-  D'(0)
-\end{tikzcd}
-\]
-We can interpret the statement that Diagram \ref{eqn.type.cart3} is a pullback as
-saying that there are unique dotted arrows making the diagram commute. So, we
-need to show that if the front face is a pullback, then there are unique
-diagonal dotted arrows as shown in the homotopy type-theoretical sense.
-{\color{red} TODO} 
+For the if direction, note that Diagram \ref{eqn.type.cart3} is a pullback
+whenever Diagram \ref{eqn.type.cart1} is, as vertical maps are orthogonal to
+cartesian maps in $\Ha^{\down}$.
 \end{proof}
@@
 $\infty$-topos by Theorem 2.6.1 of \cite{GHK:Analytic.Monads}.
+\end{proof}
+
+Now, since $\Dir$ is a topos, so is $\Dir_{/D}$. And, as we saw above,
+$\Dir_{/_{\ulcorner} D}$ is a topos as well. What is the relationship between
+$\Dir_{/D}$ and $\Dir_{/_{\ulcorner} D}$?
+
+We will show that $\Dir_{/_{\ulcorner} D}$ is a subtopos of $\Dir_{/D}$ induced
+by a \emph{lex modality} on $\Dir_{/D}$. We will recall the definition of a lex
+modality and its basic theory here, before applying it to prove our desired
+theorem. Modalities were defined in Homotopy Type Theory in the HoTT Book
+\cite{UFP:HoTT.Book}, and their theory developed substantially in
+\cite{RSS:Modalities.in.HoTT}. This theory was externalized to
+$\infty$-toposes in \cite{ABFJ:Blakers.Massey} and \cite{ABFJ:Goodwillie} as a
+efficient way for working with localizations of $\infty$-toposes.
+
+\begin{defn}
+A \emph{modality} on an $\infty$-topos $\Ca$ is a stable orthogonal factorization
+system $(\La, \Ra)$. This is an orthogonal factorization system in which the
+left class is stable under pullback.
+
+A modality is \emph{lex} if for any square
+\[
+\begin{tikzcd}
+A \arrow[r, "h"] \arrow[d, "g"'] & C \arrow[d, "f"] \\
+B \arrow[r, "k"']                & D               
+\end{tikzcd}
+\]
+where $f$ and $g$ are in $\La$ and $h$ and $k$ are in $\Ra$ is a pullback. (See
+Theorem 3.11 of \cite{RSS:Modalties.in.HoTT}, condition (vii).)
+
+We say that a modality $(\La, \Ra)$ is \emph{contained in} $(\La', \Ra')$ ---
+written $(\La, \Ra) \leq (\La', \Ra')$ --- if $\Ra \subseteq \Ra'$.
+\end{defn}
+
+\begin{prop}
+If $(\La, \Ra)$ is a modality on $\Ca$, then there is an induced modality $(\La_X,
+\Ra_X)$ on $\Ca_{/X}$ where $\La_X$ (resp. $\Ra$) consists of those maps in $\Ca_{/X}$
+whose image under the forgetful functor to $\Ca$ is in $\La$ (resp. $\Ra$).
+
+If $(\La, \Ra)$ is lex, then so is $(\La_X, \Ra_X)$.
+\end{prop}
+\begin{proof}
+\jaz{That this forms an orthogonal factorization system is claimed without proof
+as Lemma 3.1.7 in \cite{ABFJ:Blakers.Massey}. TODO would be to prove this
+fully.}
+
+Recall that the forgetful functor $\Ca_{/X} \to \Ca$ creates pullbacks. Therefore,
+$(\La_X, \Ra_X)$ is a modality --- $\La_X$ is closed under pullback since $\La$
+is. Furthermore, if $(\La, \Ra)$ is lex, then so is $(\La_X, \Ra_X)$ because the
+necessary diagram is a pullback if and only if its underlying diagram in $\Ca$
+is one. 
+\end{proof}
+
+\begin{prop}
+  For any lex modality $(\La, \Ra)$ on an $\infty$-topos $\Ca$, we get a subtopos
+  consisting of those objects $X \in \Ca$ for which the terminal map $!_X : X
+  \to \ast$ is in $\Ra$. This includes the order of lex modalities into the
+  order of subcategories of $\Ca$ whose image consists of precisely the subtoposes.
+\end{prop}
+\begin{proof}
+\jaz{TODO. I
+  think I can find a citation for this --- it is certainly folklore. I'll check \cite{RSS:Modalities.in.HoTT}.}
+\end{proof}
+
+\begin{prop}
+The orthogonal factorization system $(\term{vertical}, \term{cartesian})$ on
+$\Ha^{\downarrow}$ (given by the cartesian fibration $\Ha\op \to \Ha$) is a
+lex modality.
+\end{prop}
+\begin{proof}
+\jaz{TODO: Cite a proof that this is an orthogonal factorization system.}
+
+  Vertical morphisms of bundles are closed under pullback since pullbacks are
+computed pointwise and the pullback of an equivalence is an equivalence. The
+modality is lex because in the following cube:
+\[
+    \begin{tikzcd}[row sep=1.5em, column sep = 1.5em]
+    A_1 \arrow[rr] \arrow[dr, crossing over] \arrow[dd,swap] \arrow[ddrr, phantom, "\ulcorner"
+    very near start] &&
+    C_1 \arrow[dd] \arrow[dr] \\
+    & B_1 \arrow[rr, crossing over]\arrow[dd, crossing over] \arrow[ddrr,
+    phantom, "\ulcorner" very near start]&&
+    D_1 \arrow[dd,"h"] \\
+    A_2 \arrow[rr,] \arrow[dr, "\sim"'] && C_2 \arrow[dr, "\sim"] \\
+    & B_2 \arrow[rr] && D_2 
+    \end{tikzcd}
+\]
+
+The bottom square is a pullback since its opposite faces are equivalences, and
+therefore the top face is also a pullback, so that the cube is a pullback in $\Ha^{\down}$.
+\end{proof}
+
+\begin{thm}
+The left exact modality $(\term{vertical}_D, \term{cartesian}_D)$ on
+$\Ha^{\downarrow}_{/\pi}$ exhibits $\Ha^{\downarrow}_{/_{\ulcorner} \pi}$ as a
+subtopos.
+
+As a corollary, we have a subtopos inclusion $\Dir_{/_{\ulcorner} D}
+\hookrightarrow \Dir_{/D}$. \jaz{So $\Dir_{/D}$ is equivalently a presheaf topos
+  $\Ha^{\downarrow/D}$; what is the topology that presents $\Dir_{/_{\ulcorner}
+  D}$ as a sheaf topos?}
+\end{thm}
+\begin{proof}
+We prove this for the equivalent categories $\Ha^{\down}_{/\pi}$. This then
+follows immediately from Proposition \ref{prop:lex.modalities.subtoposes} by
+noting that the objects of $\Ha^{\down}_{/_{\ulcorner} \pi}$ are precisely those objects
+in $\Ha^{\down}_{/\pi}$ whose terminal morphism is in $\term{cartesian}_{\pi}$.
 \end{proof}
@@
 \section{Appendix}
+\begin{lem}\label{lem:slice.cone.equiv}
+There is an equivalence $S^{\triangleleft} \simeq \Hom_{\Ha}(!_0, S)$ over
+$\down$, natural in $S$.
+\end{lem}
+\begin{proof}
+\jaz{TODO}
+\end{proof}
 
@@
 \end{lem}
+\begin{proof}
+\jaz{To Type}
+\end{proof}
 
@@
 \begin{proof}
-
+\jaz{TODO}
 \end{proof}
@@
 For $\colim d : D \to \Ca$ to be the colimit of $d : D \to \Ca^J$ means that
+\jaz{To Type}
 \end{proof}
+
+\begin{lem}\label{lem:every.type.weakly.contractible.colimit}
+Every homotopy type $S$ is the colimit of the weakly contractible diagram
+$S^{\triangleleft} \to \ast^{\triangleleft} \xto{!_0} \Ha$.
+\end{lem}
+\begin{proof}
+We note that $!_0$ is the extension of the diagram $\ast : \ast \to \Ha$ by an
+initial object. Therefore, by Lemma
+\ref{lem:extending.diagram.with.initial.object.has.same.colimit}, this diagram
+has the same colimit as $S \to \ast \xto{\ast} \Ha$. The colimit of this diagram
+is $S$, because $\Ha$ is generated by the point $\ast$ --- see (cite). 
+\end{proof}

### 2020-04-07 draft.tex
new thing

--- 2020-04-02 draft.tex
@@
 \end{equation}
-is a pullback in $\Set$ iff for all functions $g\colon X\to X'$, the naturality square
+is a pullback in $\Ha$ iff for all functions $g\colon X\to X'$, the naturality square
 \begin{equation}\label{eqn.cart2}
@@
 \dis{How does this topos compare to the topos $\Dir_{/D}$?}
-\jaz{The following story: it generalizes to $\infty$-categories, which is why
-  I'm writing it this way.}
-
-\begin{defn}
-A \emph{modality} on a category $\Ca$ is a stable orthogonal factorization
-system $(\La, \Ra)$. \jaz{see Anel Biederman Finster Joyal \cite{ABFJ:Blakers.Massey}}
-
-A modality is \emph{lex} if for any square
-\[
-  % https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAEEQBfU9TXfIRRkAjFVqMWbAELdeIDNjwEiI8uPrNWiEAGE5fJYNWkx1TVJ0ARbuJhQA5vCKgAZgCcIAWyRkQOCCQAJnNJbRBXAwjPH0QQ-0DEAGZQrTYHKI9vX2oApDUQBjoAIxgGAAV+ZSEQdywHAAscEFTLEAbMmPzcxJSJNJ0AaxbCkrLKoxUdOsbmrgouIA
-\begin{tikzcd}
-A \arrow[r, "h"] \arrow[d, "g"'] & C \arrow[d, "f"] \\
-B \arrow[r, "k"']                & D               
-\end{tikzcd}
-\]
-where $f$ and $g$ are in $\La$ and $h$ and $k$ are in $\Ra$ is a pullback. (See
-Theorem 3.11 of \cite{RSS:Modalties.in.HoTT}, condition (vii).)
-
-We say that a modality $(\La, \Ra)$ is \emph{contained in} $(\La', \Ra')$ ---
-written $(\La, \Ra) \leq (\La', \Ra')$ --- if $\Ra \subseteq \Ra'$.
-\end{defn}
-
-\begin{prop}
-If $(\La, \Ra)$ is a modality on $\Ca$, then there is an induced modality $(\La_X,
-\Ra_X)$ on $\Ca_{/X}$ \jaz{I'll flesh this out in a bit, see
-  \cite{ABFJ:Blakers.Massey}}. If $(\La, \Ra)$ is lex, then so is $(\La_X, \Ra_X)$.
-\end{prop}
-
-\begin{prop}
-There is an equivalence between the order of lex modalities on a topos and the
-order of subtoposes.
-\end{prop}
-\begin{proof}
-Idea: we take those objects whose terminal morphism is in $\Ra$.
-\end{proof}
-
-\begin{prop}
-The orthogonal factorization system $(\term{vertical}, \term{cartesian})$ on
-$\Set^{\downarrow}$ (given by the cartesian fibration $\Set\op \to \Set$) is a
-lex modality.
-\end{prop}
-
-\begin{thm}
-The left exact modality $(\term{vertical}_D, \term{cartesian}_D)$ on
-$\Set^{\downarrow}_{/\pi}$ exhibits $\Set^{\downarrow}_{/_{\ulcorner} \pi}$ as a
-subtopos.
-
-As a corollary, we have a subtopos inclusion $\Dir_{/_{\ulcorner} D}
-\hookrightarrow \Dir_{/D}$. \jaz{So $\Dir_{/D}$ is equivalently a presheaf topos
-  $\Set^{\downarrow/D}$; what is the topology that presents $\Dir_{/_{\ulcorner}
-  D}$ as a sheaf topos?}
-\end{thm}
-
-\section{Dirichlet Functors on Homotopy Types} \label{sec:type.level}
-
-\begin{prop}
-  There is an adjoint quintuple:
-  \[
-    \begin{tikzcd}
-      \Ha \arrow[r, "\const"] \arrow[r, leftarrow, shift left = 5,
-      "\term{cod}"] \arrow[r, leftarrow, shift right = 5, "\term{dom}"]
-      \arrow[r, shift left = 10, "!^{(-)}"]  \arrow[r, shift right = 10, "!_{(-)}"] & \Ha^{\down}
-    \end{tikzcd}
-  \]
-  All three functors $\Ha \to \Ha^{\down}$ are fully faithful.
-\end{prop}
-\begin{proof}
-There is an adjoint triple $\begin{tikzcd} \ast \arrow[r,leftarrow] \arrow[r,
-  bend left] \arrow[r, bend right] & \down \end{tikzcd}$. The middle three
-functors are given by restricting along this adjoint triple; the outer two are
-given by Kan extending. By Lemma \ref{lem:kan.extending.cone.adds.initial}, we
-may calculate these as
-  $$X \mapsto \begin{tikzcd} 0 \arrow[d, "!^X"] \\ X \end{tikzcd}
-  \qquad\text{and}\qquad
-  X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}$$
-It is easy to see that the unit $X \to \term{dom} !_{X}$ is an equivalence (it is in
-fact an identity), so $!_{(-)}$ is fully faithful. Therefore, all the functors
-going from $\Ha \to \Ha^{\down}$ are fully faithful.
-\end{proof}
-
-\begin{prop}\label{lem:bang.preserves.weakly.contractible.colimits}
-  The functor $!_{(-)}$ preserves weakly contractible colimits.
-\end{prop}
-\begin{proof}
-  To see that $!_{(-)}$ preserves weakly contractible colimits, recall that colimits in $H^{\down}$ are calculated pointwise. It remains to show, then, that the map
-  \[
-    \begin{tikzcd}
-    \colim S_i \arrow[r, equals] \arrow[d] & \colim S_i \arrow[d] \\
-    \colim \ast \arrow[r] & \ast 
-    \end{tikzcd}
-  \]
-  is an equivalence in $H^{\down}$, for which it suffices to show that $\colim \ast$ is contractible.
-But the colimit of the terminal diagram is the (Kan-fibrant replacement of) its indexing simplicial set -- since we assumed the diagram was weakly contractible, $\colim \ast$ is contractible.
-\end{proof}
-
-Now we will define the \emph{extent} of a bundle, the Dirichlet functor it
-corresponds to. This sends a bundle
-$\pi : E \to B$ to the functor
-$$X \mapsto \sum_{b : B} E_b^X.$$
-We will, however, give a more abstract definition of the extent, and then
-calculate a number of presentations of it.
-
-\begin{defn}
-Consider the functor $!_0 : \down \to \Ha\op$ picking out the unique morphism $1\to 0$ in $\Ha\op$. Sending a functor $\Ha\op\to\Ha$ to its precomposition with $!_0$ gives an evaluation functor
-  $$\Ha^{\down} \xleftarrow{\ev_{!_0}} \Fun(\Ha\op, \Ha).$$
-  This functor admits a right adjoint by right Kan extension; we define the
-  \emph{Dirichlet extent} functor $\ext : \Ha^{\down} \to \Fun(\Ha\op,
-  \Ha)$ to be this right adjoint:
-  $$\ext_{\pi} :\equiv \term{ran}_{!_0} \pi.$$
-\end{defn}
-
-\begin{prop}
-  The functor $\ext$ is fully faithful, giving an equivalence 
-  $$\Ha^{\down} \simeq \Dir$$
-  where $\Dir$ is the category of Dirichlet functors and natural transformations.\dis{What is $\Dir$; have we defined Dirichlet functors in this context?}
-\end{prop}
-\begin{proof}
-Since $!_0 : \down \to \Ha\op$ is fully faithful, the counit of the
-$\ev_{!_0} \vdash \ext$ adjunction --- which is the universal cell defining the
-right Kan extension --- is an equivalence by Proposition 9.4.4 of \cite{RV:Elements}. 
-\end{proof}
-
-\begin{prop}\label{prop:set.characterizing.extent}
-  Let $\pi : E \to B$ be a bundle. The following are equivalent:
-  \begin{enumerate}
-  \item The extent $\ext_{\pi} : \Ha\op \to \Ha$ of $\pi$.
-  \item The functor
-    $$S \mapsto \sum_{b : B} E_b^S,$$
-    or equivalently the composite
-  $$\Ha\op \xto{(B^{\ast})\op} (\Ha_{/B})\op \xto{[-, \pi]} \Ha_{/B}
-  \xto{B_{\ast}} \Ha.$$
-\item The restricted representable functor
-  $\Ha^{\down}(!_{(-)}, \pi)$.
-\item The functor
-  $$S \mapsto \lim(\Hom_{\Ha}(!_0, S) \to \down \xto{\pi} \Ha)$$
-  where $\Hom_{\Ha}(!_0, S)$ is the slice category of $!_0 : \down \to
-  \Ha$ over $S$.
-\item The functor
-  $$S \mapsto \lim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft}
-  \xto{\pi} \Ha)$$
-  where $(-)^{\triangleleft}$ is the \emph{left cone}.
-  \end{enumerate}
-\end{prop}
-\begin{proof}
-We have presented these results in order of most understandable to most
-computational; we will prove it a somewhat opposite order.
-
-First, we note that 
-$$S \mapsto \lim(\Hom_{\Ha\op}(S, !_0) \to \down \xto{\pi} \Ha)$$
-is the right Kan extension formula for $\ext_{\pi} \equiv
-\term{ran}_{!_0} \pi$ --- see Corollary 9.5.3 of \cite{RV:Elements}. Noting that $\Hom_{\Ha}(!_0, S) = \Hom_{\Ha\op}(S,
-!_0)$, we see that (1) is equivalent to (4). Furthermore, noting that
-$\Hom_{\Ha}(!_0, S)$ simply adjoins an initial object to (the discrete
-category) $S$, we see that (4) is equivalent to (5).
-
-Now, we note that every set $S$ is the colimit of the diagram $S^{\triangleleft}
-\xto{\ast^{\triangleleft}} \xto{!_0} \Ha$. Since, by Lemma \ref{lem:bang.preserves.weakly.contractible.colimits}, $!_{(-)}$
-preserves weakly contractible colimits, {\color{red} TODO}.
-
-Finally, we calculate $\Ha^{\down}(!_{\ast}, \pi)$ homotopy type-theoretically:
-\begin{align*}
-\Ha^{\down}(!_{\ast}, \pi) &= \sum_{b : \ast \to B} \sum_{f : X \to E}
-                                  (\pi \circ f = b \circ !_X)\\
-                                &= \sum_{b : B} \sum_{f : X \to E} \prod_{x : X} (\pi (f x) = b) \\
-                                &= \sum_{b : B} \left( X \to \sum_{e : E} (\pi e = b) \right) \\
-                                  &\equiv \sum_{b : B}E_b^X.
-\end{align*}
-{\color{red} But I need a better argument to show that this is a natural
-  equivalence of functors --- something involving cartesian fibrations etc etc etc}
-\end{proof}
-
-Now we are ready to intrinsically characterize the Dirichlet functors.
-\begin{thm}
-A functor $D : \Ha\op \to \Ha$ is Dirichlet if and only if it preserves
-weakly contractible limits. 
-\end{thm}
-\begin{proof}
-First, we show that Dirichlet functors preserve connected limits. If $D$ is
-Dirichlet, then by Prop \ref{prop:set.characterizing.extent}, $D$ is naturally
-equivalent to the composite
-$$\Ha\op \xto{(B^{\ast})\op} (\Ha_{/B})\op \xto{[-, \pi]} \Ha_{/B}
-\xto{B_\ast} \Ha.$$
-As $(B^{\ast})\op$ is a right adjoint, it commutes with all limits, and as $[-,\pi]$
-is part of a multivariable adjunction, it also commutes with all limits.
-Finally, we note that $B_{\ast}$ commutes with weakly contractible limits by
-Lemma 2.2.7 of \cite{GHK:Analytic.Monads}.
-
-Now, we show that if $D$ commutes with weakly contractible limits, then the unit
-$D \to \ext_{D!_0}$ is an equivalence. By Prop
-\ref{prop:set.characterizing.extent}, 
-  $$\ext_{D!_0}(S) = \lim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft}
-  \xto{D!_0} \Ha).$$
-
-Every homotopy type $S$ is the weakly contractible colimit of the diagram $S^{\triangleleft} \to
-\down \xto{!_0} \Ha$ because it is the colimit of the diagram $S \to \ast
-\xto{\ast} \Ha$ and we are extending this diagram with an initial object (see
-Lemma \ref{lem:extending.diagram.with.initial.object.has.same.colimit}). Therefore if $D$ preserves this limit, then
-$D(S)$ is precisely the above limit $\ext_{D!_0}(S)$.
-\end{proof}
-
-Next, we turn to cartesian morphisms.
-\begin{prop}\label{prop:type.dirichlet.cartesian.iff.bundle.cartesian}
-A natural transformation $\phi : D \to D'$ between Dirichlet functors is
-cartesian if and only if the induced bundle map $D!_0 \to D'!_0$ is a pullback.
-
-As a corllary, the equivalence $\Dir \simeq \Ha^{\down}$ restricts to an
-equivalence
-$$\Dir_{\ulcorner} \simeq \Ha^{\down}_{\ulcorner}$$
-between Dirichlet functors and cartesian natural transformations and bundles and
-pullback sqaures.
-\end{prop}
-\begin{proof}
-We want to show that for any $f\colon D\to D'$ the square
-\begin{equation}\label{eqn.type.cart1}
-\begin{tikzcd}
-	D(1)\ar[r, "f_1"]\ar[d, "\pi"']&
-	D'(1)\ar[d, "\pi'"]\\
-	D(0)\ar[r, "f_0"']&
-	D'(0)
-\end{tikzcd}
-\end{equation}
-is a pullback in $\Set$ iff for all functions $g\colon X\to X'$, the naturality square
-\begin{equation}\label{eqn.type.cart2}
-\begin{tikzcd}
-  D(X')\ar[r, "f_{X'}"]\ar[d, "D(g)"']&
-  D'(X')\ar[d, "D'(g)"]\\
-  D(X)\ar[r, "f_X"']&
-  D'(X)
-\end{tikzcd}
-\end{equation}
-is a pullback in $\Set$. We will freely use the natural isomorphism
-$D(X)\cong\Set^{\down}(!_X, D!_0)$ from
-\ref{prop:set.characterizing.extent}, which allows us to identify Diagram
-\ref{eqn.type.cart2} with
-\begin{equation}\label{eqn.cart3}
-\begin{tikzcd}
- \Set^{\down}(!_{X'}, D!_0)     \ar[r, "f_{!_0,\ast}"]\ar[d, "!_g^{\ast}"']& \Set^{\down}(!_{X'}, D'!_0)
-  \ar[d, "!_{g}^{\ast}"]\\
-  \Set^{\down}(!_{X}, D!_0)\ar[r, "f_{!_0, \ast}"']&
- \Set^{\down}(!_X, D'!_0) 
-\end{tikzcd}
-\end{equation}
-
-The square in Diagram \ref{eqn.type.cart1} is a
-special case of that in Diagram \ref{eqn.type.cart2}, namely for $g\coloneqq !_0$;
-this establishes the only-if direction.
-
-To complete the proof, suppose that Diagram \ref{eqn.type.cart1} is a pullback, take an arbitrary $g\colon X\to X'$, and suppose given a commutative solid-arrow diagram as shown:
-\[
-\begin{tikzcd}[sep=small]
-  X\ar[rr, "g"]\ar[dd]\ar[rd]&&
-  X'\ar[dr]\ar[dd]\ar[dl, dotted]\\&
-  D(1)\ar[rr, crossing over]&&
-  D'(1)\ar[dd]\\
-  1\ar[dr]\ar[rr, equal]&&
-  1\ar[dr]\ar[dl, dotted]\\&
-  D(0)\ar[from=uu, crossing over]\ar[rr]&&
-  D'(0)
-\end{tikzcd}
-\]
-We can interpret the statement that Diagram \ref{eqn.type.cart3} is a pullback as
-saying that there are unique dotted arrows making the diagram commute. So, we
-need to show that if the front face is a pullback, then there are unique
-diagonal dotted arrows as shown in the homotopy type-theoretical sense.
-{\color{red} TODO} 
-\end{proof}
-
-\begin{thm}\label{thm:type.poly.cart.equiv.dir.cart}
-  There is an equivalence of $\infty$-categories
-  $$\type{Poly}_{\ulcorner} \simeq \Dir_{\ulcorner}$$
-  between the category of polynomial functors and cartesian transformations and
-  Dirichlet functors and cartesian transformations. This equivlalence sends
-  representables to representables
-  $$(-)^N \mapsto N^{(-)}.$$
-\end{thm}
-\begin{proof}
-This follows by composing the equivalence of $\Dir_{\ulcorner}$ with
-$\Ha^{\down}$ from Prop
-\ref{prop:type.dirichlet.cartesian.iff.bundle.cartesian} with that of
-Proposition 2.4.13 of \cite{GHK:Analytic.Monads}, noting that
-$\Ha^{\down}_{\ulcorner}$ is the category of $(\ast,\ast)$-polynomials. 
-\end{proof}
-
-\begin{cor}
-  Let $D$ be a Dirichlet functor. Then the $\infty$-category
-  $\Dir_{/_{\ulcorner} D}$
-  of Dirichlet functors with a cartesian map to $D$ is an $\infty$-topos.
-\end{cor}
-\begin{proof}
-By Theorem \ref{thm:type.poly.cart.equiv.dir.cart}, this $\infty$-category is equivalent
-to $\type{Poly}_{/_{\ulcorner} P}$ for a polynomial $P$. But this is an
-$\infty$-topos by Theorem 2.6.1 of \cite{GHK:Analytic.Monads}.
-\end{proof}
-
-\section{Ordinary Dirichlet Functors} \label{sec:ordinary.dirichlet.functors}
-
-In this section, we will categorify Dirichlet series
-$$\sum_{n \in \Nb} a_n n^{-s}.$$
-
-First, we review the notion of \emph{homotopy cardinality}.
-
-\begin{defn}
-Let $B$ be a homotopy type. We define the \emph{homotopy cardinality} $\#B$ to be
-the following sum:
-$$\#B := \sum_{[b] \in \pi_0(B)} \prod_{n = 1}^{\infty} |\pi_n(B, b)|^{(-1)^n}$$
-
-We note that
-$$\#B = \sum_{[b] \in \pi_0(B)} \frac{1}{\#\Omega(B, b)}$$
-\end{defn}
-
-We will leave questions concerning the convergence and well-definedness of the
-homotopy cardinality of a type, noting only that if a type $B$ is totally finite in
-that it has finitely many connected components, its homotopy groups are finite,
-and they eventually vanish, then $\#B$ is a finite sum of a finite product and so
-is well defined.
-
-The main lemma concerning homotopy cardinality is its behavior with respect to
-fibrations.
-\begin{lem}
-Let $\pi : E \to B$ be a map of homotopy types, and let $E_b$ denote the fiber
-over $b : B$. Then
-$$\#E = \sum_{[b] \in \pi_0(B)}\frac{\#E_b}{\#\Omega(B, b)}.$$
-As a corollary:
-\begin{enumerate}
-\item $\#(A \times B) = \#A \cdot \#B$ and so $\#(B^n) = (\#B)^n$.
-\item If $B$ is pointed and connected and $F$ is the fiber of $\pi$ over the
-  basepoint, then $\#E = \#F \cdot \#B$.
-\item If $A_n$ is a family of types for $n : \Nb$, then $\#(\sum_n A_n) = \sum_n \#A_n$.
-\end{enumerate}
-\end{lem}
-\begin{proof}
-  We note that by the long exact sequence of homotopy groups, we have that
-  $$|\pi_n(E, e)| = |\pi_n(E_{\pi e}, e)|\cdot |\pi_n(B, \pi e)|$$
-  Therefore, we may calculate
-  \begin{align*}
-    \#E &= \sum_{[e] \in \pi_0(E)}\prod_{n=1}^{\infty} |\pi_n(E, e)|^{(-1)^n}\\
-    &= \sum_{[b] \in \pi_0(B)} \sum_{[e] \in \pi_0(E_b)} \prod_{n=1}^{\infty} (|\pi_n(E_{b}, e)|\cdot |\pi_n(B, b)|)^{(-1)^n}\\
-    &= \sum_{[b] \in \pi_0(B)}\prod_{n=1}^{\infty} |\pi_n(B, b)|^{(-1)^n} \sum_{[e] \in \pi_0(E_b)} \prod_{n=1}^{\infty} |\pi_n(E_{b}, e)|^{(-1)^n}\\
-    &= \sum_{[b] \in \pi_0(B)}\frac{\#E_b}{\#\Omega(B, b)}.
-  \end{align*}
-
-  We may then take various maps $\pi : E \to B$ to recover the corollaries:
-  \begin{enumerate}
-  \item Take the projection $A \times B \to B$.
-  \item Take the map $\pi : E \to B$, noting that if $B$ is pointed connected then $\#B =
-    \frac{1}{\Omega B}$.
-  \item Take the projection $\sum_n A_n \to \Nb$.
-  \end{enumerate}
-\end{proof}
-
-Now, we note that if $B$ is connected, then $\#B = \frac{1}{\#\Omega(B, b)}$ for
-any point $b : B$. Therefore, if $B$ is connected with finite homs of
-cardinality $n$, then $\#B = \frac{1}{n}$ and so $\#(B^s) = n^{-s}$. This is the
-observation --- originally due to Baez and Dolan in \emph{This Weeks Finds}
-(cite) --- that we will use to categorify Dirichlet series.
-
-\begin{defn}
-A homotopy type $B$ is \emph{locally finite and connected}, or \emph{lfc}, if it
-is $0$-connected and its homs are finite.
-
-We denote by $\type{lfc}$ the homotopy type of lfc types, and note that the
-bundle $\fst : \type{lfc}_{\ast} \to \type{lfc}$ forgetting the point of a
-pointed lfc type classifies maps with lfc fibers.
-\end{defn}
-
-\section{Appendix}
-
-\begin{lem}\label{lem:cone.initial.equivalence}
-Let $\Ca$ be an $\infty$-category with an initial object. For any simplicial set
-$J$, let $\Ca^{J^{\triangleleft}}_{\ast}$ be the $\infty$-category of
-  $J^{\triangleleft}$-shaped diagrams whose apex is at the initial object; that
-  is, the following pullback:
-  \[
-    \begin{tikzcd}
-      \Ca^{J} \arrow[drr, bend left] \arrow[ddr, bend right] \arrow[dr,
-      dotted, "\sim"] & & \\
-      & \Ca^{J^{\triangleleft}}_{\ast} \arrow[d] \arrow[r] \arrow[dr, phantom,
-      "\ulcorner" very near start] & \Ca^{J^{\triangleleft}} \arrow[d,
-      "\term{ev}_{\term{apex}}"] \\
-      & \ast \arrow[r, "0"'] & \Ca
-    \end{tikzcd}
-  \]
-The the dotted extension map  $\epsilon : \Ca^{J} \to \Ca^{J^{\triangleleft}}_{\ast}$ is an equivalence.
-\end{lem}
-
-\begin{lem}\label{lem:kan.extending.cone.adds.initial}
-If $\Ca$ is an $\infty$-category with an initial object, then the restriction
-$\Ca^{J^{\triangleleft}} \to \Ca^{J}$ has a left adjoint right inverse $\epsilon
-: \Ca^J \to \Ca^{J^{\triangleleft}}$ extending a diagram by adjoining the
-initial object. 
-\end{lem}
-\begin{proof}
-
-\end{proof}
-
-\begin{lem}\label{lem:extending.diagram.with.initial.object.has.same.colimit}
-If $\Ca$ is an $\infty$-category with an initial object $0$, and $d : D \to
-\Ca^J$ a family of diagrams with colimit $\colim d : D \to \Ca$, then the family
-$D \xto{d} \Ca^J \xto{\epsilon} \Ca^{J^{\triangleleft}}$ has colimit $\colim d$.
-\end{lem}
-\begin{proof}
-For $\colim d : D \to \Ca$ to be the colimit of $d : D \to \Ca^J$ means that 
-\end{proof}
+\jaz{See the $\infty$-categorical case. The same story can be told for
+  1-categories, but perhaps we should tell it some other way?}

### 2020-04-07 inftycats/draft.tex
new thing

\section{Introduction}
A polynomial functor $P : \Set \to \Set$ is a sum of representables
\begin{equation}\label{eqn.poly}
P(X) := \sum_{b \in B} X^{E_b}
\end{equation}
where the family of sets $E_b$ depends on $b\in B$. This data is known
in the computer science literature as a ``container'', but since such an indexed
family of sets can be represented by as a function
\[
  \begin{tikzcd}
    E \arrow[d, "\pi"] \\
    B
  \end{tikzcd}
\]
we will refer to it as a \emph{bundle}. We think of a bundle as a categorified
Young diagram:

\[
[image]
\]

$B$ is the set of rows and $E_b$ is the set of boxes in row $b$ (possibly empty,
for generalities sake). We can see the polynomial functor \eqref{eqn.poly}
as sending a set $X$ to the set of ways to label a row of the correponding Young
diagram with elements of $X$.

Remarkably, all natural transformations between polynomial functors can be
represented in terms of their associated bundles. A natural transformation $P
\to P'$ corresponds to a pair of functions%
\footnote{We use dependent type syntax, in particular Idris$^?$.}
\[
\left( f : B \to B',\, f^{\sharp} : \dprod{b : B} E'_{fb} \to E_b \right)
\]
noting that $f$ acts covariantly on \dis{columns, right?} and $f^\sharp$ acts contravariantly on
boxes in each row. We refer to these special spans as \dis{can we say \emph{bivariant?}} \emph{contravariant} morphisms of bundles.
In terms of bundles, this is a diagram of the following sort:
\[
  \begin{tikzcd}
    E \arrow[d, "\pi"'] \arrow[r, leftarrow, "f_{\sharp}"] & \bullet \arrow[d] \arrow[r]
    \arrow[dr, phantom, "\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
    B \arrow[r, equals] & B \arrow[r, "f"'] & B'
  \end{tikzcd}
\]

\begin{thm}[cite]
The category of polynomial functors and natural transformations is equivalent to
the category of bundles and contravariant morphisms.
\end{thm}

This begs the question: what, then, are we to make of the more obvious,
\emph{\dis{univariant?}} morphisms of bundles
\[
  \begin{tikzcd}[column sep=large]
E \arrow[r, "\term{tot}(f_{\sharp})"] \arrow[d, "\pi"'] & E' \arrow[d, "\pi'"] \\
B \arrow[r, "f"']                                       & B'                  
\end{tikzcd}
\]
for which $f$ is covariant in the rows and $f_\sharp$ is again covariant
in each row.
%which, in terms of Young diagrams, are covariant on both the rows and the boxes
%in each row?

It turns out that these covariant maps of bundles correspond to natural
transformations between the appropriate sums of \emph{contravariant}
representables:
$$D(X) := \sum_{b \in B} E_b^X$$
In terms of Young diagrams, such a functor takes a set $X$ to the set of ways to
place the elements of $X$ in the boxes of a row.

Polynomial functors as in \eqref{eqn.poly} get their name from the case in which $B$ and $E$ are finite sets. Consider the function $\term{card}~E_{(-)} : B \to \Nb$, which takes the cardinality of each column $E_b$. Letting $B_n := (\term{card}E_{(-)})\inv(n)$, i.e.\ $B_n$ is the set of columns with $n$ elements,
we find that the for any set $X$, the cardinality
$$|P(X)| = \sum_{n \in \Nb} |B_n||X|^n$$
is a polynomial in the cardinality of $X$. Similarly,
$$|D(X)| = \sum_{n \in \Nb} |B_n|n^{|X|}$$
resembles a Dirichlet series in the cardinality of $X$. Accordingly, we call such
sums of contravariant representables \emph{Dirichlet functors}. Readers who prefer more traditional algebraic notation can see \cite{SpivakMyers}, which was the set-theoretic inspiration for the present paper.\dis{Agree? Maybe there's a better place to put this?}

We will show in this paper that Dirichlet functors are, quite robustly, the
contravariant analogue of polynomial functors. In particular, the many equivalent ways to
say that a functor is polynomial have contravariant analogues.
\begin{thm}[cite]\label{thm:polynomial.set.characterization}
  Let $P : \Set \to \Set$ be a functor. Then the following are equivalent.
  \begin{enumerate}
  \item $P$ is polynomial.
  \item $P$ is the sum of covariant representables.
  \item There is a bundle $\pi : E \to B$ together with a natural isomorphism
    $$P(X) \cong \sum_{b \in B} X^{E_b}.$$
    Or, equivalently, a natural isomorphism of $P$ with the composite
    $$\Set \xto{\dis{\Delta_{!_E}}} \Set_{/E} \xto{\dis{\Pi_\pi}} \Set_{/B} \xto{\dis{\Sigma_{!_B}}} \Set.$$
  \item $P$ is accessible and preserves connected limits.
  \end{enumerate}
\end{thm}

Analogously, we will prove the following theorem.
\begin{thm}\label{thm:dirichlet.set.characterization}
Let $D : \Set\op \to \Set$ be a contravariant functor. Then the following are
equivalent.
\begin{enumerate}
\item $D$ is Dirichlet.
\item $D$ is the sum of contravariant representables.
\item There is a bundle $\pi : E \to B$ together with a natural isomorphism
  $$D(X) \cong \sum_{b \in B} E_b^X.$$
  Or, equivalently, a natural isomorphism of $D$ with the composite
  $$\Set\op \xto{(\Delta_{!_B})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
  \xto{\Sigma_{!_B}} \Set.$$
\item $D$ preserves connected limits.
\end{enumerate}
\end{thm}

Note that we no longer need to assume accessiblity. This is a general feature of
the theory of Dirichlet functors; it is a bit ``smaller'' and more manageable
than that of polynomials. In particular, a Dirichlet functor is determined by
its action on the terminal morphism $!_0 : 0 \to \ast$ of the empty set \dis{also the terminal twisted arrow; any relation to GHK?}. As a corollary, Dirichlet functors form a topos.

\begin{thm}\label{thm:dirichlet.set.equivalence}
The functor $\Set^{\down} \to \type{Fun}(\Set\op, \Set)$, given by sending $\pi : E
\to B$ to the induced Dirichlet functor $X \mapsto \sum_{b \in B} E_b^X$, is
fully faithful, and so gives an equivalence
$$\Set^{\down} \simeq \Dir$$
between the topos of bundles and the category of Dirichlet functors, with inverse given by evalutation at
$!_0 : 0 \to \ast$.
\end{thm}

Now, object-wise, a Dirichlet functor and a polynomial functor are determined by
the same data --- a bundle $\pi : E \to B$ of sets. Accordingly, one would
expect for any set $N$ a transformation
$$X^N \mapsto N^X$$
turning polynomial functors into Dirichlet functors, and vice versa. But the
natural transformations between each sort of functor induce different morphisms
between the bundles; natural transformations between polynomial functors induce
contravariant bundle morphisms, while natural transformations between Dirichlet
functors induce covariant bundle morphisms. However, if we restrict to those
morphisms of bundles which are \emph{isovariant} on the fibers --- that is, the
pullback diagrams of the form
\[
  \begin{tikzcd}[column sep=large]
E \arrow[r, "\term{tot}(f_{\sharp})"] \arrow[d, "\pi"'] \arrow[dr, phantom,
"\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
B \arrow[r, "f"']                                       & B'                  
\end{tikzcd}
\]
which preserve the number of boxes in each row --- we find that such a morphism
is both a co- and contravariant morphism of bundles. It is well known that such
\emph{cartesian} morphisms of bundles correspond to \emph{cartesian} natural
transformations between polynomial functors (cite) --- those whose naturality
squares are pullbacks. This is true as well for Dirichlet functors.
\begin{thm}
A natural transformation $D \to D'$ of Dirichlet functors is Cartesian if and
only if the corresponding bundle map
\[
  \begin{tikzcd}[column sep=large]
E \arrow[r, "\term{tot}(f_{\sharp})"] \arrow[d, "\pi"'] \arrow[dr, phantom,
"\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
B \arrow[r, "f"']                                       & B'                  
\end{tikzcd}
\]
is a pullback. As a corollary, we have an equivalence of categories
$$\type{Poly}_{\ulcorner} \simeq \Dir_{\ulcorner}$$
between polynomial functors with cartesian natural transfromations and Dirichlet
functors with cartesian natural transfromations.
\end{thm}

This story occupies Section \ref{sec:set.level} of our paper.

Polynomial functors play another very important role: they are \emph{generating
  functors} for flat combinatorial species. That is, we have a (non-canonical)
identification
$$P(X) \cong \sum_{n \in \Nb} C_n \times X^n/n!$$
for sets $C_n$ on which the symmetric groups $\Aut(\underline{n})$ act freely
(for \emph{finitary} functors $P$, i.e.\ those that commute with filtered colimits).
The generating functors for general combinatorial species --- the \emph{analytic
functors} --- are not in general polynomial due to a loss of information when
quotienting out by the action of the symmetric groups. This can be fixed by
instead taking \emph{homotopy quotients} of these actions.

In other words, we need to move to homotopy types to make sense of the
fractional coefficients that arise in the exponential power series form
$$\sum_{n \in \Nb} a_n \frac{x^n}{n!}.$$
As we will see, moving to homotopy types also allows us to express the negative
exponent in the Dirichlet series form
$$\sum_{n \in \Nb} a_n n^{-s}.$$

In \emph{$\infty$-Operads as Analytic Monads} \cite{GHK:Analytic.Monads},
Gepner, Haugseng, and Kock take this approach and develop the theory of
polynomial functors on homotopy types. In this setting, being analytic is a
property of \dis{some?} polynomial functors, and is equivalent to admitting a cartesian
map to the functor $\type{Sym}$ given by
$$\type{Sym}X := \sum_{n : \Nb} X^n \sslash n!$$
\dis{This is the homotopy quotient?}

Let $\Ha$ be the $\infty$-category of homotopy types. GHK prove $\infty$-categorical analogues of the above Theorem
\ref{thm:polynomial.set.characterization}.
\begin{thm}[\cite{GHK:Analytic.Monads}]\label{thm:polynomial.type.characterization}
For any functor $P : \Ha \to \Ha$, the following are equivalent:
  \begin{enumerate}
  \item $P$ is polynomial.
  \item There is a bundle $\pi : E \to B$ of homotopy types together with a natural equivalence
    $$P(X) \simeq \sum_{b : B} X^{E_b}.$$
    Or, equivalently, a natural equivalence of $P$ with the composite
    $$\Ha \xto{E^{\ast}} \Ha_{/E} \xto{\pi_!} \Ha_{/B} \xto{B_\ast} \Ha.$$
  \item $P$ is accessible and preserves weakly contractible limits.
  \end{enumerate}
\end{thm}

Note that while this is a strong analogue, it is not a direct generalization of \cref{thm:polynomial.set.characterization}:
though it is true that in 1-categories all connected limits are weakly contractible, this is not true in general.

In Section \ref{sec:type.level}, we will prove analogues of Theorems
\ref{thm:dirichlet.set.characterization} and
\ref{thm:dirichlet.set.equivalence}. \dis{What analogue of \ref{thm:dirichlet.set.equivalence} are we proving?} In particular, we will prove the following.

\begin{thm}\label{thm:dirichlet.type.characterization}
Let $D : \Set\op \to \Set$ \dis{Do you mean $\Ha$ here?} be a contravariant functor. Then the following are
equivalent.
\begin{enumerate}
\item $D$ is Dirichlet. \dis{In what sense?}
\item There is a bundle $\pi : E \to B$ of homotopy types together with a natural equivalence
  $$D(X) \cong \sum_{b \in B} E_b^X.$$
  Or, equivalently, a natural equivalence of $D$ with the composite
  $$\Ha\op \xto{(B^{\ast})\op} (\Ha_{/B})\op \xto{[-, \pi]} \Ha_{/B}
  \xto{B_{\ast}} \Ha.$$
\item $D$ preserves weakly contractible limits.
\end{enumerate}
\end{thm}

In Section \ref{sec:ordinary.dirichlet.functors}, we will introduce the notion
of an \emph{ordinary} Dirichlet functor, a categorification of a Dirichlet
series
$$\sum_{n \in \Nb} a_n n^{-s}.$$
In the last installment of his blog \emph{This Week's Finds} (cite), Baez (joint with
Dolan) presents a functor of groupoids categorifying the Riemann Zeta function.
In later, unpublished work (cite), Baez and Dolan give an analogous
categorification of Hasse-Weil Zeta functions. We will recall some facts about
homotopy cardinality and construct these Zeta functors as ordinary Dirichlet
functors in our setting. We leave the investigation of Euler product formulas
and functional equations on the objective level to future work.

\begin{acknowledgements}

\end{acknowledgements}

\section{Dirichlet Functors on Homotopy Types} \label{sec:type.level}

\begin{prop}
  There is an adjoint quintuple:
  \[
    \begin{tikzcd}
      \Ha \arrow[r, "\const"] \arrow[r, leftarrow, shift left = 5,
      "\term{cod}"] \arrow[r, leftarrow, shift right = 5, "\term{dom}"]
      \arrow[r, shift left = 10, "!^{(-)}"]  \arrow[r, shift right = 10, "!_{(-)}"] & \Ha^{\down}
    \end{tikzcd}
  \]
  All three functors $\Ha \to \Ha^{\down}$ are fully faithful.
\end{prop}
\begin{proof}
There is an adjoint triple $\begin{tikzcd} \ast \arrow[r,leftarrow] \arrow[r,
  bend left] \arrow[r, bend right] & \down \end{tikzcd}$. The middle three
functors are given by restricting along this adjoint triple; the outer two are
given by Kan extending. By Lemma \ref{lem:kan.extending.cone.adds.initial}, we
may calculate these as
  $$X \mapsto \begin{tikzcd} 0 \arrow[d, "!^X"] \\ X \end{tikzcd}
  \qquad\text{and}\qquad
  X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}$$
It is easy to see that the unit $X \to \term{dom} !_{X}$ is an equivalence (it is in
fact an identity), so $!_{(-)}$ is fully faithful. Therefore, all the functors
going from $\Ha \to \Ha^{\down}$ are fully faithful.
\end{proof}

\begin{prop}\label{lem:bang.preserves.weakly.contractible.colimits}
  The functor $!_{(-)}$ preserves weakly contractible colimits.
\end{prop}
\begin{proof}
  To see that $!_{(-)}$ preserves weakly contractible colimits, recall that colimits in $H^{\down}$ are calculated pointwise. It remains to show, then, that the map
  \[
    \begin{tikzcd}
    \colim S_i \arrow[r, equals] \arrow[d] & \colim S_i \arrow[d] \\
    \colim \ast \arrow[r] & \ast 
    \end{tikzcd}
  \]
  is an equivalence in $H^{\down}$, for which it suffices to show that $\colim \ast$ is contractible. But the colimit of the terminal diagram is the (Kan-fibrant replacement of) its indexing simplicial set -- since we assumed the diagram was weakly contractible, $\colim \ast$ is contractible.
\end{proof}

\begin{lem}\label{lem:type.bundle.yoneda}
The Yoneda embedding $\yo : \downarrow\op \to \Ha^{\downarrow}$ is equivalent to the
composite $$\downarrow\op \xto{\sigma\op} \downarrow \xto{!_{0}} \Ha
\xto{!_{(-)}} \Ha^{\downarrow}.$$

As a corollary, for any $\pi : \downarrow \to \Ha$, $\down\op \xto{\sigma\op}
\down \xto{\pi} \Ha$ equals the composite
$$\down\op \xto{!_0\op} \Ha\op \xto{!_{(-)}\op}
(\Ha^{\downarrow})\op \xto{\Ha^{\downarrow}(-, \pi)} \Ha$$
by the Yoneda lemma.
\end{lem}
\begin{proof}
  This follows from Lemma \ref{lem:set.bundle.yoneda}, since $\downarrow$ is a $1$-category.
\end{proof}

Now we will define the \emph{extent} of a bundle, the Dirichlet functor it
corresponds to. This sends a bundle
$\pi : E \to B$ to the functor
$$X \mapsto \sum_{b : B} E_b^X.$$
We will, however, give a more abstract definition of the extent, and then
calculate a number of presentations of it.

\begin{defn}
Consider the functor $!_0 : \down \to \Ha\op$ picking out the unique morphism $1\to 0$ in $\Ha\op$. Sending a functor $\Ha\op\to\Ha$ to its precomposition with $!_0$ gives an evaluation functor
  $$\Ha^{\down} \xleftarrow{\ev_{!_0}} \Fun(\Ha\op, \Ha).$$
  This functor admits a right adjoint by right Kan extension; we define the
  \emph{Dirichlet extent} functor $\ext : \Ha^{\down} \to \Fun(\Ha\op,
  \Ha)$ to be this right adjoint:
  $$\ext_{\pi} :\equiv \term{ran}_{!_0\op \circ \sigma} \pi.$$
\end{defn}

\begin{prop}
  The functor $\ext$ is fully faithful, giving an equivalence 
  $$\Ha^{\down} \simeq \Dir$$
  where $\Dir$ is the category of Dirichlet functors and natural transformations.\dis{What is $\Dir$; have we defined Dirichlet functors in this context?}
\end{prop}
\begin{proof}
Since $!_0 : \down \to \Ha\op$ is fully faithful, the counit of the
$\ev_{!_0} \vdash \ext$ adjunction --- which is the universal cell defining the
right Kan extension --- is an equivalence by Proposition 9.4.4 of \cite{RV:Elements}. 
\end{proof}

\begin{prop}\label{prop:set.characterizing.extent}
  Let $\pi : E \to B$ be a bundle. The following are equivalent:
  \begin{enumerate}
  \item The extent $\ext_{\pi} : \Ha\op \to \Ha$ of $\pi$.
  \item The functor
    $$S \mapsto \sum_{b : B} E_b^S,$$
    or equivalently the composite
  $$\Ha\op \xto{(B^{\ast})\op} (\Ha_{/B})\op \xto{[-, \pi]} \Ha_{/B}
  \xto{B_{\ast}} \Ha.$$
\item The following pullback in $\Fun(\Ha\op, \Ha)$: 
\[
\begin{tikzcd}
	\ext_\pi\ar[r]\ar[d]\arrow[dr, phantom,
      "\ulcorner" very near start]&
	B \ar[d]\\
	\Ha(-,E)\ar[r]&
	\Ha(-,B)
\end{tikzcd}
\]
\item The restricted representable functor
  $\Ha^{\down}(!_{(-)}, \pi)$.
\item The functor
  $$S \mapsto \lim(\Hom_{\Ha}(!_0, S)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Ha)$$
  where $\Hom_{\Ha}(!_0, S)$ is the slice category of $!_0 : \down \to
  \Ha$ over $S$.
\item The functor
  $$S \mapsto \lim(( S^{\triangleleft} )\op \xto{( !^{\triangleleft} )\op}
  (\ast^{\triangleleft})\op \xto{\sigma\op} \down
  \xto{\pi} \Ha)$$
  where $(-)^{\triangleleft}$ is the \emph{left cone}.
  \end{enumerate}
\end{prop}
\begin{proof}
We have presented these results in order of most understandable to most
computational; we will prove it a somewhat opposite order.

First, we note that 
$$S \mapsto \lim(\Hom_{\Ha\op}(S, !_0\op \circ \sigma) \to \down \xto{\pi} \Ha)$$
is the right Kan extension formula for $\ext_{\pi} \equiv
\term{ran}_{!_0} \pi$ --- see Corollary 9.5.3 of \cite{RV:Elements}. Now,
$\Hom_{\Ha\op}(S, !_0\op \circ \sigma) \simeq \Hom_{\Ha}(!_0 \circ \sigma\op,
S)\op$ over $\down$, which we may see by noting that $(-)\op : {\infty}\Cat \to {\infty}\Cat^{\term{co}}$ is a cosmological equivalence and therefore preserves
comma squares. Furthermore, we have the following equivalence:
\[
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAB12AJCAWwH1gnLnQC+ACgCE-YgAJOAYywAnBfPbYA5rzqcIaUrIDKASj1oQo0uky58hFGQCMVWoxZthfQcLFSZhqbmltYgGNh4BERO5K70zKyIHOxQEADuhFY2EfbRpC7U8R5JnKkZwaKuMFCa8ESgAGbKfEhkIDgQSDEgDHQARjAMAAq2kQ4gyliaABY4IIXuicnYvCGNzauIbR1IAExZIE0tiLvUO4gAzAsJnhpTOmuHG11nnZeVokA
\begin{tikzcd}
{\Hom_{\Ha}(!_0 \circ \sigma\op, S)\op} \arrow[d, "\sim"'] \arrow[r] & \down \arrow[d, "\sigma"] \\
{\Hom_{\Ha}(!_0, S)\op} \arrow[r]                                    & \down\op                 
\end{tikzcd}
\]
and therefore we may equivalently calculate this limit as 
$$\lim(\Hom_{\Ha}(!_0, S)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Ha).$$
This gives us the equivalence between (1) and (5). By Lemma
\ref{lem:slice.cone.equiv}, we see also that (5) and (6) are equivalent.

Now, using Lemmas \ref{lem:bang.preserves.weakly.contractible.colimits} and \ref{lem:type.bundle.yoneda}, we may make
the following calculation identifying (4) with (6):

\begin{align*}
  \Ha^{\down}(!_S, \pi) &= \Ha^{\down}(!_{\colim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft} \xto{!_0} \Ha)}, \pi) \\
  &\simeq \Ha^{\down}(\colim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft} \xto{!_0} \Ha \xto{!_{(-)}} \Ha^{\down}), \pi)\\
&\simeq \lim((S^{\down})\op \xto{(!^{\triangleleft})\op} (\ast^{\triangleleft})\op \xto{!_0\op} \Ha\op \xto{!_{(-)}} (\Ha^{\down})\op \xto{\Ha^{\down}(-, \pi)} \Ha) \\
&\simeq \lim((S^{\down})\op \xto{(!^{\triangleleft})\op} (\ast^{\triangleleft})\op \xto{\sigma\op} \down \xto{\pi} \Ha).
\end{align*}

We see that (3) is equivalent to (4) by Lemma
\ref{lem:hom.type.arrow}.\footnote{\jaz{This applies by using the module
    formalism to deal with this representable functors. I don't know how much I
    should go into this.}}
\end{proof}

Now we are ready to intrinsically characterize the Dirichlet functors.
\begin{thm}
A functor $D : \Ha\op \to \Ha$ is Dirichlet if and only if it preserves
weakly contractible limits. 
\end{thm}
\begin{proof}
First, we show that Dirichlet functors preserve connected limits. If $D$ is
Dirichlet, then by Prop \ref{prop:set.characterizing.extent}, $D$ is naturally
equivalent to the restricted representable functor $\Ha^{\down}(!_{-}, \pi)$.
Since, by Lemma \ref{lem:bang.preserves.weakly.contractible.colimits}, $!_{(-)}$
preserves weakly contractible colimits, $D$ sends weakly contractible colimits
to limits.

Now, we show that if $D$ commutes with weakly contractible limits, then the unit
$D \to \ext_{D!_0}$ is an equivalence. By Prop
\ref{prop:set.characterizing.extent}, 
  $$\ext_{D!_0}(S) = \lim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft}
  \xto{D!_0} \Ha).$$

Every homotopy type $S$ is the weakly contractible colimit of the diagram $S^{\triangleleft} \to
\down \xto{!_0} \Ha$ by Lemma \ref{lem:every.type.weakly.contractible.colimit}. Therefore if $D$ preserves this limit, then
$D(S)$ is precisely the above limit $\ext_{D!_0}(S)$.
\end{proof}

Next, we turn to cartesian morphisms.
\begin{prop}\label{prop:type.dirichlet.cartesian.iff.bundle.cartesian}
A natural transformation $\phi : D \to D'$ between Dirichlet functors is
cartesian if and only if the induced bundle map $D!_0 \to D'!_0$ is a pullback.

As a corllary, the equivalence $\Dir \simeq \Ha^{\down}$ restricts to an
equivalence
$$\Dir_{\ulcorner} \simeq \Ha^{\down}_{\ulcorner}$$
between Dirichlet functors and cartesian natural transformations and bundles and
pullback sqaures.
\end{prop}
\begin{proof}
We want to show that for any $f\colon D\to D'$ the square
\begin{equation}\label{eqn.type.cart1}
\begin{tikzcd}
	D(1)\ar[r, "f_1"]\ar[d, "\pi"']&
	D'(1)\ar[d, "\pi'"]\\
	D(0)\ar[r, "f_0"']&
	D'(0)
\end{tikzcd}
\end{equation}
is a pullback in $\Set$ iff for all functions $g\colon X\to X'$, the naturality square
\begin{equation}\label{eqn.type.cart2}
\begin{tikzcd}
  D(X')\ar[r, "f_{X'}"]\ar[d, "D(g)"']&
  D'(X')\ar[d, "D'(g)"]\\
  D(X)\ar[r, "f_X"']&
  D'(X)
\end{tikzcd}
\end{equation}
is a pullback in $\Ha$. We will freely use the natural isomorphism
$D(X)\cong\Ha^{\down}(!_X, D!_0)$ from
\ref{prop:set.characterizing.extent}, which allows us to identify Diagram
\ref{eqn.type.cart2} with
\begin{equation}\label{eqn.type.cart3}
\begin{tikzcd}
 \Ha^{\down}(!_{X'}, D!_0)     \ar[r, "f_{!_0,\ast}"]\ar[d, "!_g^{\ast}"']& \Ha^{\down}(!_{X'}, D'!_0)
  \ar[d, "!_{g}^{\ast}"]\\
  \Ha^{\down}(!_{X}, D!_0)\ar[r, "f_{!_0, \ast}"']&
 \Ha^{\down}(!_X, D'!_0) 
\end{tikzcd}
\end{equation}

The square in Diagram \ref{eqn.type.cart1} is a
special case of that in Diagram \ref{eqn.type.cart2}, namely for $g\coloneqq !_0$;
this establishes the only-if direction.

For the if direction, note that Diagram \ref{eqn.type.cart3} is a pullback
whenever Diagram \ref{eqn.type.cart1} is, as vertical maps are orthogonal to
cartesian maps in $\Ha^{\down}$.
\end{proof}

\begin{thm}\label{thm:type.poly.cart.equiv.dir.cart}
  There is an equivalence of $\infty$-categories
  $$\type{Poly}_{\ulcorner} \simeq \Dir_{\ulcorner}$$
  between the category of polynomial functors and cartesian transformations and
  Dirichlet functors and cartesian transformations. This equivlalence sends
  representables to representables
  $$(-)^N \mapsto N^{(-)}.$$
\end{thm}
\begin{proof}
This follows by composing the equivalence of $\Dir_{\ulcorner}$ with
$\Ha^{\down}$ from Prop
\ref{prop:type.dirichlet.cartesian.iff.bundle.cartesian} with that of
Proposition 2.4.13 of \cite{GHK:Analytic.Monads}, noting that
$\Ha^{\down}_{\ulcorner}$ is the category of $(\ast,\ast)$-polynomials. 
\end{proof}

\begin{cor}
  Let $D$ be a Dirichlet functor. Then the $\infty$-category
  $\Dir_{/_{\ulcorner} D}$
  of Dirichlet functors with a cartesian map to $D$ is an $\infty$-topos.
\end{cor}
\begin{proof}
By Theorem \ref{thm:type.poly.cart.equiv.dir.cart}, this $\infty$-category is equivalent
to $\type{Poly}_{/_{\ulcorner} P}$ for a polynomial $P$. But this is an
$\infty$-topos by Theorem 2.6.1 of \cite{GHK:Analytic.Monads}.
\end{proof}

Now, since $\Dir$ is a topos, so is $\Dir_{/D}$. And, as we saw above,
$\Dir_{/_{\ulcorner} D}$ is a topos as well. What is the relationship between
$\Dir_{/D}$ and $\Dir_{/_{\ulcorner} D}$?

We will show that $\Dir_{/_{\ulcorner} D}$ is a subtopos of $\Dir_{/D}$ induced
by a \emph{lex modality} on $\Dir_{/D}$. We will recall the definition of a lex
modality and its basic theory here, before applying it to prove our desired
theorem. Modalities were defined in Homotopy Type Theory in the HoTT Book
\cite{UFP:HoTT.Book}, and their theory developed substantially in
\cite{RSS:Modalities.in.HoTT}. This theory was externalized to
$\infty$-toposes in \cite{ABFJ:Blakers.Massey} and \cite{ABFJ:Goodwillie} as an
efficient way for working with localizations of $\infty$-toposes.

\begin{defn}
A \emph{modality} on an $\infty$-topos $\Ca$ is a stable orthogonal factorization
system $(\La, \Ra)$. This is an orthogonal factorization system in which the
left class is stable under pullback.

A modality is \emph{lex} if for any square
\[
\begin{tikzcd}
A \arrow[r, "h"] \arrow[d, "g"'] & C \arrow[d, "f"] \\
B \arrow[r, "k"']                & D               
\end{tikzcd}
\]
where $f$ and $g$ are in $\La$ and $h$ and $k$ are in $\Ra$ is a pullback. (See
Theorem 3.11 of \cite{RSS:Modalties.in.HoTT}, condition (vii).)

We say that a modality $(\La, \Ra)$ is \emph{contained in} $(\La', \Ra')$ ---
written $(\La, \Ra) \leq (\La', \Ra')$ --- if $\Ra \subseteq \Ra'$.
\end{defn}

\begin{lem}\label{lem:slice.modality}
If $(\La, \Ra)$ is a modality on $\Ca$, then there is an induced modality $(\La_X,
\Ra_X)$ on $\Ca_{/X}$ where $\La_X$ (resp. $\Ra$) consists of those maps in $\Ca_{/X}$
whose image under the forgetful functor to $\Ca$ is in $\La$ (resp. $\Ra$).

If $(\La, \Ra)$ is lex, then so is $(\La_X, \Ra_X)$.
\end{lem}
\begin{proof}
\jaz{That this forms an orthogonal factorization system is claimed without proof
as Lemma 3.1.7 in \cite{ABFJ:Blakers.Massey}. TODO would be to prove this
fully.}

Recall that the forgetful functor $\Ca_{/X} \to \Ca$ creates pullbacks. Therefore,
$(\La_X, \Ra_X)$ is a modality --- $\La_X$ is closed under pullback since $\La$
is. Furthermore, if $(\La, \Ra)$ is lex, then so is $(\La_X, \Ra_X)$ because the
necessary diagram is a pullback if and only if its underlying diagram in $\Ca$
is one. 
\end{proof}

\begin{prop}\label{prop:lex.modalities.subtoposes}
  For any lex modality $(\La, \Ra)$ on an $\infty$-topos $\Ca$, we get a subtopos
  consisting of those objects $X \in \Ca$ for which the terminal map $!_X : X
  \to \ast$ is in $\Ra$. This includes the order of lex modalities into the
  order of subcategories of $\Ca$ whose image consists of precisely the subtoposes.
\end{prop}
\begin{proof}
\jaz{TODO. I
  think I can find a citation for this --- it is certainly folklore. I'll check \cite{RSS:Modalities.in.HoTT}.}
\end{proof}

\begin{lem}\label{lem:cartesian.modality}
The orthogonal factorization system $(\term{vertical}, \term{cartesian})$ on
$\Ha^{\downarrow}$ (given by the cartesian fibration $\Ha\op \to \Ha$) is a
lex modality.
\end{lem}
\begin{proof}
\jaz{TODO: Cite a proof that this is an orthogonal factorization system.}

  Vertical morphisms of bundles are closed under pullback since pullbacks are
computed pointwise and the pullback of an equivalence is an equivalence. The
modality is lex because in the following cube:
\[
    \begin{tikzcd}[row sep=1.5em, column sep = 1.5em]
    A_1 \arrow[rr] \arrow[dr, crossing over] \arrow[dd,swap] \arrow[ddrr, phantom, "\ulcorner"
    very near start] &&
    C_1 \arrow[dd] \arrow[dr] \\
    & B_1 \arrow[rr, crossing over]\arrow[dd, crossing over] \arrow[ddrr,
    phantom, "\ulcorner" very near start]&&
    D_1 \arrow[dd,"h"] \\
    A_2 \arrow[rr,] \arrow[dr, "\sim"'] && C_2 \arrow[dr, "\sim"] \\
    & B_2 \arrow[rr] && D_2 
    \end{tikzcd}
\]

The bottom square is a pullback since its opposite faces are equivalences, and
therefore the top face is also a pullback, so that the cube is a pullback in $\Ha^{\down}$.
\end{proof}

\begin{thm}
The left exact modality $(\term{vertical}_{\pi}, \term{cartesian}_{\pi})$ on
$\Ha^{\downarrow}_{/\pi}$ exhibits $\Ha^{\downarrow}_{/_{\ulcorner} \pi}$ as a
subtopos.

As a corollary, we have a subtopos inclusion $\Dir_{/_{\ulcorner} D}
\hookrightarrow \Dir_{/D}$. 
\end{thm}
\begin{proof}
This follows immediately from Proposition \ref{prop:lex.modalities.subtoposes} by
noting that the objects of $\Ha^{\down}_{/_{\ulcorner} \pi}$ are precisely those objects
in $\Ha^{\down}_{/\pi}$ whose terminal morphism is in $\term{cartesian}_{\pi}$.
\end{proof}

\begin{rmk}
Note that $\const : \Ha \to \Ha^{\downarrow}$ induces an equivalence $\Ha \simeq
\Ha^{\down}_{/_{\ulcorner} \ast}$. Therefore, we see that the above subtopos
inclusion coincides with that of $\const : \Ha \hookrightarrow \Ha^{\down}$ in
the case that $\pi = \ast$. In particular, note that $\Ha^{\down}_{\ulcorner}
\neq \Ha^{\down}_{/_{\ulcorner} \ast}$.
\end{rmk}

\section{Ordinary Dirichlet Functors} \label{sec:ordinary.dirichlet.functors}

In this section, we will categorify Dirichlet series
$$\sum_{n \in \Nb} a_n n^{-s}.$$

First, we review the notion of \emph{homotopy cardinality}.

\begin{defn}
Let $B$ be a homotopy type. We define the \emph{homotopy cardinality} $\#B$ to be
the following sum:
$$\#B := \sum_{[b] \in \pi_0(B)} \prod_{n = 1}^{\infty} |\pi_n(B, b)|^{(-1)^n}$$

We note that
$$\#B = \sum_{[b] \in \pi_0(B)} \frac{1}{\#\Omega(B, b)}$$
\end{defn}

We will leave questions concerning the convergence and well-definedness of the
homotopy cardinality of a type, noting only that if a type $B$ is totally finite in
that it has finitely many connected components, its homotopy groups are finite,
and they eventually vanish, then $\#B$ is a finite sum of a finite product and so
is well defined.

The main lemma concerning homotopy cardinality is its behavior with respect to
fibrations.
\begin{lem}
Let $\pi : E \to B$ be a map of homotopy types, and let $E_b$ denote the fiber
over $b : B$. Then
$$\#E = \sum_{[b] \in \pi_0(B)}\frac{\#E_b}{\#\Omega(B, b)}.$$
As a corollary:
\begin{enumerate}
\item $\#(A \times B) = \#A \cdot \#B$ and so $\#(B^n) = (\#B)^n$.
\item If $B$ is pointed and connected and $F$ is the fiber of $\pi$ over the
  basepoint, then $\#E = \#F \cdot \#B$.
\item If $A_n$ is a family of types for $n : \Nb$, then $\#(\sum_n A_n) = \sum_n \#A_n$.
\end{enumerate}
\end{lem}
\begin{proof}
  We note that by the long exact sequence of homotopy groups, we have that
  $$|\pi_n(E, e)| = |\pi_n(E_{\pi e}, e)|\cdot |\pi_n(B, \pi e)|$$
  Therefore, we may calculate
  \begin{align*}
    \#E &= \sum_{[e] \in \pi_0(E)}\prod_{n=1}^{\infty} |\pi_n(E, e)|^{(-1)^n}\\
    &= \sum_{[b] \in \pi_0(B)} \sum_{[e] \in \pi_0(E_b)} \prod_{n=1}^{\infty} (|\pi_n(E_{b}, e)|\cdot |\pi_n(B, b)|)^{(-1)^n}\\
    &= \sum_{[b] \in \pi_0(B)}\prod_{n=1}^{\infty} |\pi_n(B, b)|^{(-1)^n} \sum_{[e] \in \pi_0(E_b)} \prod_{n=1}^{\infty} |\pi_n(E_{b}, e)|^{(-1)^n}\\
    &= \sum_{[b] \in \pi_0(B)}\frac{\#E_b}{\#\Omega(B, b)}.
  \end{align*}

  We may then take various maps $\pi : E \to B$ to recover the corollaries:
  \begin{enumerate}
  \item Take the projection $A \times B \to B$.
  \item Take the map $\pi : E \to B$, noting that if $B$ is pointed connected then $\#B =
    \frac{1}{\Omega B}$.
  \item Take the projection $\sum_n A_n \to \Nb$.
  \end{enumerate}
\end{proof}

Now, we note that if $B$ is connected, then $\#B = \frac{1}{\#\Omega(B, b)}$ for
any point $b : B$. Therefore, if $B$ is connected with finite homs of
cardinality $n$, then $\#B = \frac{1}{n}$ and so $\#(B^s) = n^{-s}$. This is the
observation --- originally due to Baez and Dolan in \emph{This Weeks Finds}
(cite) --- that we will use to categorify Dirichlet series.

\begin{defn}
A homotopy type $B$ is \emph{locally finite and connected}, or \emph{lfc}, if it
is $0$-connected and its homs are finite.

We denote by $\type{lfc}$ the homotopy type of lfc types, and note that the
bundle $\fst : \type{lfc}_{\ast} \to \type{lfc}$ forgetting the point of a
pointed lfc type classifies maps with lfc fibers.
\end{defn}

\begin{defn}
An \emph{ordinary Dirichlet functor} is a Dirichlet functor $D$ for which,
equivalently:
\begin{enumerate}
\item $D$ is cartesian over $\fst : \type{lfc}_{\ast} \to \type{lfc}$,
\item The fibers of $D!_0$ are locally finite and connected.
\end{enumerate}
\end{defn}

\section{Appendix}
\begin{lem}\label{lem:slice.cone.equiv}
There is an equivalence $S^{\triangleleft} \simeq \Hom_{\Ha}(!_0, S)$ over
$\down$, natural in $S$.
\end{lem}
\begin{proof}
\jaz{TODO}
\end{proof}

\begin{lem}\label{lem:cone.initial.equivalence}
Let $\Ca$ be an $\infty$-category with an initial object. For any simplicial set
$J$, let $\Ca^{J^{\triangleleft}}_{\ast}$ be the $\infty$-category of
  $J^{\triangleleft}$-shaped diagrams whose apex is at the initial object; that
  is, the following pullback:
  \[
    \begin{tikzcd}
      \Ca^{J} \arrow[drr, bend left] \arrow[ddr, bend right] \arrow[dr,
      dotted, "\sim"] & & \\
      & \Ca^{J^{\triangleleft}}_{\ast} \arrow[d] \arrow[r] \arrow[dr, phantom,
      "\ulcorner" very near start] & \Ca^{J^{\triangleleft}} \arrow[d,
      "\term{ev}_{\term{apex}}"] \\
      & \ast \arrow[r, "0"'] & \Ca
    \end{tikzcd}
  \]
The the dotted extension map  $\epsilon : \Ca^{J} \to \Ca^{J^{\triangleleft}}_{\ast}$ is an equivalence.
\end{lem}
\begin{proof}
\jaz{To Type}
\end{proof}

\begin{lem}\label{lem:kan.extending.cone.adds.initial}
If $\Ca$ is an $\infty$-category with an initial object, then the restriction
$\Ca^{J^{\triangleleft}} \to \Ca^{J}$ has a left adjoint right inverse $\epsilon
: \Ca^J \to \Ca^{J^{\triangleleft}}$ extending a diagram by adjoining the
initial object. 
\end{lem}
\begin{proof}
\jaz{TODO}
\end{proof}

\begin{lem}\label{lem:extending.diagram.with.initial.object.has.same.colimit}
If $\Ca$ is an $\infty$-category with an initial object $0$, and $d : D \to
\Ca^J$ a family of diagrams with colimit $\colim d : D \to \Ca$, then the family
$D \xto{d} \Ca^J \xto{\epsilon} \Ca^{J^{\triangleleft}}$ has colimit $\colim d$.
\end{lem}
\begin{proof}
For $\colim d : D \to \Ca$ to be the colimit of $d : D \to \Ca^J$ means that

\[
\begin{tikzcd}
\arrow[dr, phantom, "\scriptstyle\Uparrow\lambda" pos=.85] & B \arrow[d, "f"] & & X \arrow[dr, phantom, "\scriptstyle\Uparrow\chi"]\arrow[r, "b"] \arrow[d, "c"'] & B \arrow[d, "f"] & \arrow[d, phantom, "="] &  X \arrow[dr, phantom, "\scriptstyle\exists!\Uparrow\zeta" pos=.1,  "\scriptstyle\Uparrow\lambda" pos=.85 ]\arrow[r, "b"] \arrow[d, "c"'] & B \arrow[d, "f"]  \\ C \arrow[r, "g"'] \arrow[ur, "\ell"] & A & & C \arrow[r, "g"'] & A &~ & C \arrow[ur, "\ell" description] \arrow[r, "g"'] & A
\end{tikzcd}
\]

\end{proof}

\begin{lem}\label{lem:every.type.weakly.contractible.colimit}
Every homotopy type $S$ is the colimit of the weakly contractible diagram
$S^{\triangleleft} \to \ast^{\triangleleft} \xto{!_0} \Ha$.
\end{lem}
\begin{proof}
We note that $!_0$ is the extension of the diagram $\ast : \ast \to \Ha$ by an
initial object. Therefore, by Lemma
\ref{lem:extending.diagram.with.initial.object.has.same.colimit}, this diagram
has the same colimit as $S \to \ast \xto{\ast} \Ha$. The colimit of this diagram
is $S$, because $\Ha$ is generated by the point $\ast$ --- see (cite). 
\end{proof}

\begin{lem}\label{lem:hom.type.arrow}
  The following square is a pullback: 
  \[
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAB12AJCAWwH1gnLnQB6Q9lAgB3MAF85ACgC0pZQEoQc0uky58hFGQCMVWoxZthfQcLpLOU3qQAEjvpu27seAkWPkZvTMrIgc3DYSIg7sAMbQrpzxUJ46IBg+Bv6kptTBlmHWAlH2iu7ObnHQnmYwUADm8ESgAGYATnxIZCA4EEjGXiDtnYgBPX2IAMyDw7xIAEzUvUjTabNdSxPzchRyQA
\begin{tikzcd}
{\Hom_{\Ha^{\down}}(-,-)} \arrow[d] \arrow[r] \arrow[dr, phantom, "\ulcorner"
very near start] & {\Hom_{\Ha}(\cod, \cod)} \arrow[d] \\
{\Hom_{\Ha}(\dom, \dom)} \arrow[r]            & {\Hom_{\Ha}(\dom, \cod)}          
\end{tikzcd}
  \]
\end{lem}
\begin{proof}
We will give a presentation of this square in terms of cotensors by simplicial
sets. The square of simiplicial sets will be a pushout, and accordinly this
square will be a pullback.

We begin by noting that $\Hom_{\Ha}(\cod, \cod) \simeq \Ha^{\sqcup}$ where
\[
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAB1206AnPRzgBEYDHHQB6ARhABfUuky58hFGUlVajFm07c+WAe2GiJkgASc8AW3gWjIsVNnyQGbHgJFJ5DfWatEDnsTJzkFd2UvUnVqP21AzjgARwBjJjRZDRgoAHN4IlAAMx4IKyQyEBwIJAAmajgACyxCnHLqMSwGNgaICABrEGoGLDAAkDgIYahBkAaYOmnEMCYGBjCQYtLa9urEAGZ1zbLECqqkbxAGOgAjEQAFRQ8VEB4sHIbW2K0xgApOLCgpDMxAAlM4iiVjhczvtDpC2pVdgcKDIgA
\begin{tikzcd}
\partial\Delta^1 \arrow[r, hook] \arrow[d, "{(\id, 1)}"'] \arrow[rd, phantom, "\ulcorner" very near end] & \Delta^1 \arrow[d] \\
\partial\Delta^1 \times \Delta^1 \arrow[r]                           & \sqcup            
\end{tikzcd}
\]
and therefore we have a pullback square:
\[
\begin{tikzcd}
\Ha^{\sqcup} \arrow[r] \arrow[d] \arrow[rd, phantom, "\ulcorner" very near
start] & \Ha^{\Delta^1} \arrow[d] \\
\Ha^{\partial\Delta^1 \times \Delta^1} \arrow[r] & \Ha^{\partial \Delta^1}
\end{tikzcd}
\]
But the cospan in this pullback square is equivalently
\[
\begin{tikzcd}
\Ha^{\sqcup} \arrow[r] \arrow[d] \arrow[rd, phantom, "\ulcorner" very near
start] & \Ha^{\down} \arrow[d] \\
\Ha^{\down}\times \Ha^{\down} \arrow[r] & \Ha \times \Ha
\end{tikzcd}
\]
giving us the equivalent $\Hom_{\Ha}(\cod, \cod) \simeq \Ha^{\sqcup}$. We get
similar equivalences $\Hom_{\Ha}(\dom, \dom) \simeq \Ha^{\sqcap}$ and
$\Hom_{\Ha}(\dom, \cod) \simeq \Ha^{\term{N}}$ where
\[
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAB1206AnPRzgBEYDHHQB6ARhABfUuky58hFGUlVajFm07c+WAe2GiJkgASc8AW3gWjIsVNnyQGbHgJFJ5DfWatEDnsTJzkFd2UvUnVqP21AzjgARwBjJjRZDRgoAHN4IlAAMx4IKyQyEBwIJAAmajgACyxCnHLqMSwGNgaICABrEGoGLDAAkDgIYahBkAaYOmnEMCYGBjCQYtLa9urEAGZ1zbLECqqkbxAGOgAjEQAFRQ8VEB4sHIbW2K0xgApOLCgpDMxAAlM4iiVjhczvtDpC2pVdgcKDIgA
\begin{tikzcd}
\partial\Delta^1 \arrow[r, hook, "i"] \arrow[d, "{(\id, i)}"'] \arrow[rd, phantom, "\ulcorner" very near end] & \Delta^1 \arrow[d] \\
\partial\Delta^1 \times \Delta^1 \arrow[r]                           & \term{N}            
\end{tikzcd}
\]

Now, let $\underline{\term{N}}$ be the pushout
\[
\begin{tikzcd}
\Delta^0 \arrow[r, hook, "1"] \arrow[d, "2"'] \arrow[rd, phantom, "\ulcorner" very near end] & \Delta^1 \arrow[d] \\
\Delta^2 \arrow[r]                           & \underline{\term{N}}            
\end{tikzcd}
\]
We note that $\sqcup$ may also be constructed as the similar pushout
\[
\begin{tikzcd}
\Delta^0 \arrow[r, hook, "1"] \arrow[d, "2"'] \arrow[rd, phantom, "\ulcorner" very near end] & \Delta^1 \arrow[d] \\
\Lambda^2_{1} \arrow[r]                           & \underline{\term{N}}            
\end{tikzcd}
\]
and therefore $\sqcup \hookrightarrow \underline{\term{N}}$ is a trivial
cofibration in the Joyal model structure as it is a pushout of trivial
cofibrations. This tells us that the restriction map $\Ha^{\underline{\term{N}}}
\xto{\sim} \Ha^{\sqcup}$ is an equivalence. 
We have a similar story for $\Ha^{\overline{\term{N}}} \xto{\sim} \Ha^{\sqcap}$.
Thus, all things told, we may replace the square in the lemma statement by the
equivalent square:
\[
\begin{tikzcd}
\Ha^{\Delta^1 \times \Delta^1} \arrow[r] \arrow[d]  & \Ha^{\underline{\term{N}}} \arrow[d] \\
\Ha^{\overline{\term{N}}} \arrow[r] & \Ha^{\term{N}} 
\end{tikzcd}
\]
Finally, we note that the following square is a pushout of simplicial sets, so
that we get that our desired square is a pullback:
\[
\begin{tikzcd}
\term{N} \arrow[r, hook, "1"] \arrow[d, "2"'] \arrow[rd, phantom, "\ulcorner" very near end] & \underline{\term{N}} \arrow[d] \\
\overline{\term{N}} \arrow[r]                           & \Delta^1 \times \Delta^1            
\end{tikzcd}
\]
\end{proof}

%% Notes from Emily:
%
% Weber: 2-toposes, for learning about multivariable adjunctions with modules
%
% Arin Mazel-gee: wfs in oo-cats (check thesis or write to him)
%
% lifting orthogonal factorization from base to total space of cartesian
% fibration
%
% Emily says: the join of A and B is the Pi along * * >--> Delta^1 of A + B (up
% to iso)! So this gives a mapping in property to S^\triangleleft and so
% we can compare this mapping in property to the pullback property of Hom_H(!_0,
% S)
% 
% 5.3: the derivator proof should work. or: if C has an initial object, then C^J does
%

### 2020-04-07 draft.tex
fixed proofs

@@
+\begin{abstract}
+  Polynomial functors are sums of covariant representable functors from the
+  category of sets to itself. They have a robust theory with many applications
+  --- from operads and opetopes to combinatorial species. In this paper, we
+  define a contravariant analogue of polynomial functors: Dirichlet functors. We
+  develop the basic theory of Dirichlet functors, and relate them to their
+  covariant analogues.
+\end{abstract}
+
 \section{Introduction}
@@
 \]
-we will refer to it as a \emph{bundle}. We think of a bundle as a categorified
-Young diagram:
-
-\[
-[image]
-\]
-
-$B$ is the set of rows and $E_b$ is the set of boxes in row $b$ (possibly empty,
-for generalities sake). We can see the polynomial functor \eqref{eqn.poly}
-as sending a set $X$ to the set of ways to label a row of the correponding Young
-diagram with elements of $X$.
+we will refer to it as a \emph{bundle}.
 
@@
 \]
-noting that $f$ acts covariantly on \dis{columns, right?} and $f^\sharp$ acts contravariantly on
-boxes in each row. We refer to these special spans as \dis{can we say \emph{bivariant?}} \emph{contravariant} morphisms of bundles.
+noting that $f$ acts covariantly on the base and $f^\sharp$ acts contravariantly on
+fibers. 
 In terms of bundles, this is a diagram of the following sort:
@@
 \]
+We refer to these special spans as \emph{contravariant} morphisms of bundles.
 
@@
 This begs the question: what, then, are we to make of the more obvious,
-\emph{\dis{univariant?}} morphisms of bundles
+\emph{covariant} morphisms of bundles
 \[
@@
 \]
-for which $f$ is covariant in the rows and $f_\sharp$ is again covariant
-in each row.
-%which, in terms of Young diagrams, are covariant on both the rows and the boxes
-%in each row?
+for which $f_\sharp$ is covariant
+in each fibers.
 
@@
 representables:
-$$D(X) := \sum_{b \in B} E_b^X$$
-In terms of Young diagrams, such a functor takes a set $X$ to the set of ways to
-place the elements of $X$ in the boxes of a row.
+$$D(S) := \sum_{b \in B} E_b^S$$
 
-Polynomial functors as in \eqref{eqn.poly} get their name from the case in which $B$ and $E$ are finite sets.
-Consider the function $\term{card}~E_{(-)} : B \to \Nb$, which takes the cardinality of each column $E_b$.
-Letting $B_n := (\term{card}E_{(-)})\inv(n)$, i.e.\ $B_n$ is the set of columns with $n$ elements,
+Polynomial functors as in \eqref{eqn.poly} get their name from the case in which
+$B$ and $E$ are finite sets. Consider the function $\term{card}~E_{(-)} : B \to
+\Nb$, which takes the cardinality of each fiber $E_b$. Letting $B_n :=
+(\term{card}E_{(-)})\inv(n)$, i.e.\ $B_n$ is the set of elements whose fibers have $n$ elements,
 we find that the for any set $X$, the cardinality
@@
 is a polynomial in the cardinality of $X$. Similarly,
-$$|D(X)| = \sum_{n \in \Nb} |B_n|n^{|X|}$$
-resembles a Dirichlet series in the cardinality of $X$. Accordingly, we call such
+$$|D(S)| = \sum_{n \in \Nb} |B_n|n^{|S|}$$
+resembles a Dirichlet series in the cardinality of $S$ -- without the usual
+negative sign.\footnote{Future work of the first author will recover the
+  negative sign by generalizing the theory of Dirichlet functors to homotopy
+  types.} Accordingly, we call such
 sums of contravariant representables \emph{Dirichlet functors}.
-Readers who prefer more traditional algebraic notation can see \cite{SpivakMyers}, which was the set-theoretic inspiration for the present paper.\dis{Agree?
-Maybe there's a better place to put this?}
 
@@
     Or, equivalently, a natural isomorphism of $P$ with the composite
-    $$\Set \xto{\dis{\Delta_{!_E}}} \Set_{/E} \xto{\dis{\Pi_\pi}} \Set_{/B} \xto{\dis{\Sigma_{!_B}}} \Set.$$
+    $$\Set \xto{{\Delta_{!_E}}} \Set_{/E} \xto{{\Pi_\pi}} \Set_{/B} \xto{{\Sigma_{!_B}}} \Set.$$
   \item $P$ is accessible and preserves connected limits.
@@
 Analogously, we will prove the following theorem.
-\begin{thm}\label{thm:dirichlet.set.characterization}
+\begin{thm}
 Let $D : \Set\op \to \Set$ be a contravariant functor. Then the following are
@@
 than that of polynomials. In particular, a Dirichlet functor is determined by
-its action on the terminal morphism $!_0 : 0 \to \ast$ of the empty set \dis{also the terminal twisted arrow; any relation to GHK?}. As a corollary, Dirichlet functors form a topos.
+its action on the terminal morphism $!_0 : 0 \to \ast$ of the empty set. As a corollary, Dirichlet functors form a topos.
 
@@
 \]
-which preserve the number of boxes in each row --- we find that such a morphism
+which preserve the number of elements in each fiber --- we find that such a morphism
 is both a co- and contravariant morphism of bundles. It is well known that such
 \emph{cartesian} morphisms of bundles correspond to \emph{cartesian} natural
-transformations between polynomial functors (cite) --- those whose naturality
+transformations between polynomial functors \jaz{ (cite) } --- those whose naturality
 squares are pullbacks. This is true as well for Dirichlet functors.
@@
 
-This story occupies Section \ref{sec:set.level} of our paper.
-
-Polynomial functors play another very important role: they are \emph{generating
-  functors} for flat combinatorial species. That is, we have a (non-canonical)
-identification
-$$P(X) \cong \sum_{n \in \Nb} C_n \times X^n/n!$$
-for sets $C_n$ on which the symmetric groups $\Aut(\underline{n})$ act freely
-(for \emph{finitary} functors $P$, i.e.\ those that commute with filtered colimits).
-The generating functors for general combinatorial species --- the \emph{analytic
-functors} --- are not in general polynomial due to a loss of information when
-quotienting out by the action of the symmetric groups. This can be fixed by
-instead taking \emph{homotopy quotients} of these actions.
-
-In other words, we need to move to homotopy types to make sense of the
-fractional coefficients that arise in the exponential power series form
-$$\sum_{n \in \Nb} a_n \frac{x^n}{n!}.$$
-As we will see, moving to homotopy types also allows us to express the negative
-exponent in the Dirichlet series form
-$$\sum_{n \in \Nb} a_n n^{-s}.$$
-
-In \emph{$\infty$-Operads as Analytic Monads} \cite{GHK:Analytic.Monads},
-Gepner, Haugseng, and Kock take this approach and develop the theory of
-polynomial functors on homotopy types. In this setting, being analytic is a
-property of \dis{some?} polynomial functors, and is equivalent to admitting a cartesian
-map to the functor $\type{Sym}$ given by
-$$\type{Sym}X := \sum_{n : \Nb} X^n \sslash n!$$
-\dis{This is the homotopy quotient?}
-
-Let $\Ha$ be the $\infty$-category of homotopy types. GHK prove $\infty$-categorical analogues of the above Theorem
-\ref{thm:polynomial.set.characterization}.
-\begin{thm}[\cite{GHK:Analytic.Monads}]\label{thm:polynomial.type.characterization}
-For any functor $P : \Ha \to \Ha$, the following are equivalent:
-  \begin{enumerate}
-  \item $P$ is polynomial.
-  \item There is a bundle $\pi : E \to B$ of homotopy types together with a natural equivalence
-    $$P(X) \simeq \sum_{b : B} X^{E_b}.$$
-    Or, equivalently, a natural equivalence of $P$ with the composite
-    $$\Ha \xto{E^{\ast}} \Ha_{/E} \xto{\pi_!} \Ha_{/B} \xto{B_\ast} \Ha.$$
-  \item $P$ is accessible and preserves weakly contractible limits.
-  \end{enumerate}
-\end{thm}
-
-Note that while this is a strong analogue, it is not a direct generalization of \cref{thm:polynomial.set.characterization}:
-though it is true that in 1-categories all connected limits are weakly contractible, this is not true in general.
-
-In Section \ref{sec:type.level}, we will prove analogues of Theorems
-\ref{thm:dirichlet.set.characterization} and
-\ref{thm:dirichlet.set.equivalence}. \dis{What analogue of \ref{thm:dirichlet.set.equivalence} are we proving?} In particular, we will prove the following.
-
-\begin{thm}\label{thm:dirichlet.type.characterization}
-Let $D : \Set\op \to \Set$ \dis{Do you mean $\Ha$ here?} be a contravariant functor. Then the following are
-equivalent.
-\begin{enumerate}
-\item $D$ is Dirichlet. \dis{In what sense?}
-\item There is a bundle $\pi : E \to B$ of homotopy types together with a natural equivalence
-  $$D(X) \cong \sum_{b \in B} E_b^X.$$
-  Or, equivalently, a natural equivalence of $D$ with the composite
-  $$\Ha\op \xto{(B^{\ast})\op} (\Ha_{/B})\op \xto{[-, \pi]} \Ha_{/B}
-  \xto{B_{\ast}} \Ha.$$
-\item $D$ preserves weakly contractible limits.
-\end{enumerate}
-\end{thm}
-
-In Section \ref{sec:ordinary.dirichlet.functors}, we will introduce the notion
-of an \emph{ordinary} Dirichlet functor, a categorification of a Dirichlet
-series
-$$\sum_{n \in \Nb} a_n n^{-s}.$$
-In the last installment of his blog \emph{This Week's Finds} (cite), Baez (joint with
-Dolan) presents a functor of groupoids categorifying the Riemann Zeta function.
-In later, unpublished work (cite), Baez and Dolan give an analogous
-categorification of Hasse-Weil Zeta functions. We will recall some facts about
-homotopy cardinality and construct these Zeta functors as ordinary Dirichlet
-functors in our setting. We leave the investigation of Euler product formulas
-and functional equations on the objective level to future work.
-
 \begin{acknowledgements}
@@
 
-\section{Dirichlet Functors on Sets} \label{sec:set.level}
+\section{Dirichlet Functors} \label{sec:set.level}
 
@@
 
-\begin{prop}
-  There is an adjoint quintuple:
+\begin{prop}\label{prop:adjoint.sextuple}
+  There is an adjoint sextuple:
   \[
@@
       "\term{cod}"] \arrow[r, leftarrow, shift right = 5, "\term{dom}"]
-      \arrow[r, shift left = 10, "!^{(-)}"]  \arrow[r, shift right = 10, "!_{(-)}"] & \Set^{\down}
+      \arrow[r, shift left = 10, "!^{(-)}"]  \arrow[r, shift right = 10,
+      "!_{(-)}"] \arrow[r, leftarrow, shift left = 15, "\term{ZC}"]& \Set^{\down}
     \end{tikzcd}
   \]
-  All three functors $\Set \to \Set^{\down}$ are fully faithful.\dis{I had six; why leave one off?}
+  All three functors $\Set \to \Set^{\down}$ are fully faithful.
 \end{prop}
@@
   \end{equation}
-\dis{Shouldn't the notation $!^X$ and $!_X$ be switched, so that $X$ is contravariant in $X\to \ast$ and covariant in $0\to X$?
-It also matches the side of the arrow that $X$ is on in \eqref{eqn.bangbang}.} It is easy to see that the unit $X \to \term{dom} !_{X}$ is an isomorphism (it is in
+ It is easy to see that the unit $X \to \term{dom} !_{X}$ is an isomorphism (it is in
 fact an identity), so $!_{(-)}$ is fully faithful. Therefore, all three functors
 going from $\Set \to \Set^{\down}$ are fully faithful.
+
+The existence of the final adjoint can be deduced from the fact that $!^{(-)}$ preserves all
+limits. It sends a bundle $\pi : E \to B$ to the largest subset $\term{ZC}(B)$ of $B$ for
+which the following square is a pullback
+\[
+  \begin{tikzcd}[column sep=large]
+0 \arrow[r] \arrow[d] \arrow[dr, phantom,
+"\ulcorner" very near start] & E \arrow[d, "\pi"] \\
+\term{ZC}(B) \arrow[r, hookrightarrow]                                       & B
+\end{tikzcd}
+\]
 \end{proof}
@@
 \begin{defn}\label{def.extent}
-  Consider the functor $!_0 : \down \to \Set\op$ picking out the unique morphism $1\to 0$ in $\Set\op$. Sending a functor $\Set\op\to\Set$ to its precomposition with $!_0$ gives an evaluation functor
+  Consider the functor $!_0\op \circ \sigma : \down \to \Set\op$ picking out the
+  unique morphism $1\to 0$ in $\Set\op$. Sending a functor $\Set\op\to\Set$ to
+  its precomposition with $!_0\op \sigma$ gives an evaluation functor
   $$\Set^{\down} \xleftarrow{\ev_{!_0}} \Fun(\Set\op, \Set).$$
-  \dis{I worry about the size of $\Fun(\Set\op,\Set)$.}\jaz{No need to worry,
-    you are extending functors with small domains along a functor with small
-    domains. Limits in any functor category (regardless of size) are calculated
-    pointwise, and we are taking small limits.} 
   This functor admits a right adjoint by right Kan extension along $!_0\op \circ
@@
 \end{defn}
-
-\begin{prop}
-  The functor $\ext$ is fully faithful, giving an equivalence
-  $$\Set^{\down} \simeq \Dir$$
-  where $\Dir$ is the category of Dirichlet functors and natural transformations.
-\end{prop}
-\begin{proof}
-Since $!_0 : \down \to \Set\op$ is fully faithful, the counit of the
-$\ev_{!_0} \vdash \ext$ adjunction --- which is the universal cell defining the
-right Kan extension --- is an isomorphism. 
-\end{proof}
 
@@
   \xto{B_{\ast}} \Set.$$
-\item \dis{Add this?} The pullback functor sending a set $S$ to 
+\item The pullback in $\Fun(\Set\op, \Set)$:  
 \[
 \begin{tikzcd}
-	\ext_\pi(S)\ar[r]\ar[d]\arrow[dr, phantom,
+	\ext_\pi \ar[r]\ar[d]\arrow[dr, phantom,
       "\ulcorner" very near start]&
 	B\ar[d]\\
-	\Set(S,E)\ar[r]&
-	\Set(S,B)
+	\Set(-,E)\ar[r]&
+	\Set(-,B)
 \end{tikzcd}
@@
 \item The functor
-  $$S \mapsto \lim(\Hom_{\Set}(!_0, S) \to \down \xto{\pi} \Set)$$
+  $$S \mapsto \lim(\Hom_{\Set}(!_0, S)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Set)$$
   where $\Hom_{\Set}(!_0, S)$ is the slice category of $!_0 : \down \to
-  \Set$ over $S$.\dis{Is this Emily's notation for comma category?}\jaz{yes in
-    her Elements}
+  \Set$ over $S$.
 \item The functor
-  $$S \mapsto \lim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft}
+  $$S \mapsto \lim(( S^{\triangleleft} )\op \xto{( !^{\triangleleft} )\op}
+  (\ast^{\triangleleft})\op \xto{\sigma\op} \down
   \xto{\pi} \Set)$$
@@
 First, we note that 
-$$S \mapsto \lim(\Hom_{\Set\op}(S, !_0) \to \down \xto{\pi} \Set)$$
-is the standard right Kan extension formula for $\ext_{\pi} \equiv
-\term{ran}_{!_0} \pi$ as a conical limit. Noting that $\Hom_{\Set}(!_0, S) = \Hom_{\Set\op}(S,
-!_0)$, we see that (1) is equivalent to (4). Furthermore, noting that
-$\Hom_{\Set}(!_0, S)$ simply adjoins an initial object to (the discrete
-category) $S$, we see that (4) is equivalent to (5).
+$$S \mapsto \lim(\Hom_{\Set\op}(S, !_0\op \circ \sigma) \to \down \xto{\pi} \Set)$$
+is the right Kan extension formula for $\ext_{\pi} \equiv
+\term{ran}_{!_0} \pi$ --- see Corollary 9.5.3 of \cite{RV:Elements}. Now,
+$\Hom_{\Set\op}(S, !_0\op \circ \sigma) \simeq \Hom_{\Set}(!_0 \circ \sigma\op,
+S)\op$ over $\down$, which we may see by noting that $(-)\op : {\infty}\Cat \to {\infty}\Cat^{\term{co}}$ is a cosmological equivalence and therefore preserves
+comma squares. Furthermore, we have the following equivalence:
+\[
+% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAB12AJCAWwH1gnLnQC+ACgCE-YgAJOAYywAnBfPbYA5rzqcIaUrIDKASj1oQo0uky58hFGQCMVWoxZthfQcLFSZhqbmltYgGNh4BERO5K70zKyIHOxQEADuhFY2EfbRpC7U8R5JnKkZwaKuMFCa8ESgAGbKfEhkIDgQSDEgDHQARjAMAAq2kQ4gyliaABY4IIXuicnYvCGNzauIbR1IAExZIE0tiLvUO4gAzAsJnhpTOmuHG11nnZeVokA
+\begin{tikzcd}
+{\Hom_{\Set}(!_0 \circ \sigma\op, S)\op} \arrow[d, "\sim"'] \arrow[r] & \down \arrow[d, "\sigma"] \\
+{\Hom_{\Set}(!_0, S)\op} \arrow[r]                                    & \down\op                 
+\end{tikzcd}
+\]
+and therefore we may equivalently calculate this limit as 
+$$\lim(\Hom_{\Set}(!_0, S)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Set).$$
+This gives us the equivalence between (1) and (5).
+
+Now, the comma category $\Hom_{\Set}(!_0, S)$ simply adjoins an initial object
+to (the discrete category) $S$. Therefore, we find that (5) and (6) are equivalent.
 
@@
 Since, by Lemma \ref{lem:bang.preserves.connected.colimits}, $!_{(-)}$
-preserves connected colimits, {\color{red} TODO}.
+preserves connected colimits, we may make the following identification of (4)
+with (6) using Lemma \ref{lem:set.bundle.yoneda}: 
+\begin{align*}
+  \Set^{\down}(!_S, \pi) &= \Set^{\down}(!_{\colim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft} \xto{!_0} \Set)}, \pi) \\
+  &\simeq \Set^{\down}(\colim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft} \xto{!_0} \Set \xto{!_{(-)}} \Set^{\down}), \pi)\\
+&\simeq \lim((S^{\down})\op \xto{(!^{\triangleleft})\op} (\ast^{\triangleleft})\op \xto{!_0\op} \Set\op \xto{!_{(-)}} (\Set^{\down})\op \xto{\Set^{\down}(-, \pi)} \Set) \\
+&\simeq \lim((S^{\down})\op \xto{(!^{\triangleleft})\op} (\ast^{\triangleleft})\op \xto{\sigma\op} \down \xto{\pi} \Set).
+\end{align*}
 
-Finally, we note that the set $\Set^{\down}(!_X, \pi)$ is naturally
-isomorphic to the set $\sum_{b \in B} E_b^X$.\dis{add pullback?}
+We see that (3) is equivalent to (4) by noting that the following square of
+natural transformations is a pullback:
+\[
+\begin{tikzcd}
+{\Set^{\downarrow}(-, -)} \arrow[d] \arrow[r] \arrow[rd, phantom, "\ulcorner" very near start] & {\Set(\cod(-), \cod(-))} \arrow[d] \\
+{\Set(\dom(-), \dom(-))} \arrow[r]                       & {\Set(\dom(-), \cod(-))}          
+\end{tikzcd}
+\]
+and restricting the right side to $\pi$ and the left side to $!_{(-)}$.
+
+Finally, we note that the set $\Set^{\down}(!_S, \pi)$ is naturally
+isomorphic to the set $\sum_{b \in B} E_b^S$, letting us identify (4) with (2).
 \end{proof}
@@
 Now we are ready to intrinsically characterize the Dirichlet functors.
-\begin{thm}
-A functor $D : \Set\op \to \Set$ is Dirichlet if and only if it preserves
-connected limits. 
+\begin{defn}
+A \emph{Dirichlet functor} is a contravariant functor $D : \Set\op \to \Set$
+which preserves connected limits. We denote by $\Dir$ the category of Dirichlet functors and natural transformations.
+\end{defn}
+
+\begin{thm}\label{thm:dirichlet.set.characterization}
+  The functor $\ext$ is fully faithful, and gives an equivalence
+  $$\Set^{\down} \simeq \Dir.$$
+
+  As a corollary, the category of Dirichlet functors is a topos.
 \end{thm}
 \begin{proof}
-First, we show that Dirichlet functors preserve connected limits. If $D$ is
-Dirichlet, then by Prop \ref{prop:set.characterizing.extent}, $D$ is naturally
-isomorphic to the composite
-$$\Set\op \xto{(B^{\ast})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
-\xto{B_\ast} \Set.$$
-As $(B^{\ast})\op$ is a right adjoint, it commutes with all limits, and as $[-,\pi]$
-is part of a multivariable adjunction, it also commutes with all limits.
-Finally, we note that $B_{\ast}$ commutes with connected limits.
+Since $!_0 : \down \to \Set\op$ is fully faithful, the counit of the
+$\ev_{!_0} \vdash \ext$ adjunction --- which is the universal cell defining the
+right Kan extension --- is an isomorphism.
 
-Now, we show that if $D$ commutes with connected limits, then the unit
+Now, we show that a functor is Dirichlet if and only if it is the extent of a bundle. If $D$ is
+the extent of a bundle, then by Prop \ref{prop:set.characterizing.extent}, $D$ is naturally
+isomorphic to the restricted representable $\Set^{\down}(!_{(-)})$. By Lemma
+\ref{lem:bang.preserves.connected.colimits}, this sends connected colimits in $\Set$ to
+connected limits.
+
+Now, we show that if $D$ is Dirichlet, then the unit
 $D \to \ext_{D!_0}$ is an isomorphism. By Prop
@@
 
-Next, we turn to cartesian morphisms.
+\begin{rmk}
+The six adjoints of Proposition \ref{prop:adjoint.sextuple} correspond, under
+the equivalence of Theorem \ref{thm:dirichlet.set.characterization}, to
+\begin{align*}
+  \term{ZC}(D) &\sim \mbox{the coefficient of $0^S$ in $D$.}\\
+  !^{C} &\sim S \mapsto C \times 0^S \\
+  \cod(D) &\sim D(0) \\
+  \const(C) &\sim S \mapsto C \\
+  \dom(D) &\sim D(1) \\
+  !_{C} &\sim S \mapsto C^S \\
+\end{align*}
+In particular, $!_{(-)}$ corresponds to the Yoneda embedding.
+\end{rmk}
+
+\section{Cartesian Transformations between Dirichlet Functors}
+In this section, we turn to cartesian transformations between Dirichlet
+functors. We will show that the category of Dirichlet functors and cartesian
+transfromations are equivalent to the category of Polynomial functors and
+cartesian transformations.
+
 \begin{prop}
@@
 \begin{proof}
-\jaz{We could slickly do this using the fact that vertical maps are orthogonal
-  to horizontal maps.}
-
 We want to show that for any $f\colon D\to D'$ the square
@@
 \end{equation}
-is a pullback in $\Ha$ iff for all functions $g\colon X\to X'$, the naturality square
+is a pullback in $\Set$ iff for all functions $g\colon X\to X'$, the naturality square
 \begin{equation}\label{eqn.cart2}
@@
 \end{proof}
-\dis{How does this topos compare to the topos $\Dir_{/D}$?}
-\jaz{See the $\infty$-categorical case. The same story can be told for
-  1-categories, but perhaps we should tell it some other way?}
+
+Now, since $\Dir$ is a topos, so is $\Dir_{/D}$. And, as we saw above,
+$\Dir_{/_{\ulcorner} D}$ is a topos as well. What is the relationship between
+$\Dir_{/D}$ and $\Dir_{/_{\ulcorner} D}$?
+
+We will show that $\Dir_{/_{\ulcorner} D}$ is a subtopos of $\Dir_{/D}$ with the
+lex localization given by the vertical / cartesian factorization system on $\Set^{\down}$.
+
+\begin{thm}
+  For any $\pi : \down \to \Set$, we have a subtopos inclusion
+  $$\Set^{\down}_{/_{\ulcorner} \pi} \hookrightarrow \Set^{\down}_{/\pi}$$
+
+  with lex localization given by:
+  \[
+\begin{tikzcd}
+E' \arrow[r] \arrow[d] & E \arrow[d, "\pi"] \\
+B' \arrow[r]           & B                 
+\end{tikzcd} \quad\quad\mapsto\quad\quad
+\begin{tikzcd}
+E' \arrow[d] \arrow[r, dashed]    & \bullet \arrow[d] \arrow[r] \arrow[rd, phantom, "\ulcorner" very near start] & E \arrow[d, "\pi"] \\
+B' \arrow[r, equals] & B' \arrow[r]                           & B                 
+\end{tikzcd}
+  \]
+  As a corollary, $\Dir_{/_{\ulcorner} D} \hookrightarrow \Dir_{D}$ is a
+  subtopos inclusion.
+\end{thm}
+\begin{proof}
+We have displayed both the action of the left localization and its unit. The
+counit is always an isomorphism since pullbacks are unique up to unique
+isomorphism.
+
+That this is lex follows quickly from the fact that taking pullbacks commutes
+with taking limits. 
+\end{proof}

### 2020-04-08 draft.tex
MEs

@@
 \to P'$ corresponds to a pair of functions%
-\footnote{We use dependent type syntax, in particular Idris$^?$.}
+\footnote{We use dependent type syntax, e.g.\ as used in Idris.}
 \[
@@
 fibers. 
-In terms of bundles, this is a diagram of the following sort:
+In terms of bundles, a map $\pi\to\pi'$ is a diagram of the following sort:
 \[
@@
 for which $f_\sharp$ is covariant
-in each fibers.
+in each fibers?
 
@@
 representables:
-$$D(S) := \sum_{b \in B} E_b^S$$
+$$D(S) := \sum_{b \in B} E_b^S.$$
 
@@
 \begin{acknowledgements}
-
+Joyal, Kock(!), AFOSR.
 \end{acknowledgements}
@@
 Before diving in to the theory of Dirichlet functors, let's first consider the
-category $\Set^{\down}$ of bundles of sets and univariant bundle maps. For our
+category $\Set^{\down}$ of bundles of sets and covariant bundle maps. For our
 proofs to go smoothly, we will need to explicitly keep track of the
-self-dualizing isomorphism $\downarrow \xto{\sim} \downarrow\op$ on the walking arrow.
+self-dualizing isomorphism $\downarrow \xto{\sim} (\downarrow)\op$ on the walking arrow.
 
@@
   \term{cod}$ consisting of a single morphism. We denote by $\sigma : \downarrow
-  \to \downarrow\op$ the self-dualizing isomorphism of $\downarrow$, and note
+  \to (\downarrow)\op$ the self-dualizing isomorphism of $\downarrow$, and note
   that $\sigma\inv = \sigma\op$.
@@
   bend left] \arrow[r, bend right] & \down \end{tikzcd}$. The middle three
-functors---$\term{cod}$, $\const$, and $\term{dom}$---are given by restricting along this adjoint triple; the outer two are
+functors---$\term{cod}$, $\const$, and $\term{dom}$---are given by restricting along this adjoint triple. The next two, $!_{(-)}$ and $!^{(-)}$, are
 given by Kan extending, or more concretely:
@@
 "\ulcorner" very near start] & E \arrow[d, "\pi"] \\
-\term{ZC}(B) \arrow[r, hookrightarrow]                                       & B
+\term{ZC}(\pi) \arrow[r, hookrightarrow]                                       & B
 \end{tikzcd}
@@
 \end{proof}
-
+\dis{Shall we say that $\term{ZC}(\pi)$ is also the coefficient of $0^X$ in the extent?}
 We prove a few quick facts we will use later.
@@
 \begin{lem}\label{lem:set.bundle.yoneda}
-The Yoneda embedding $\yo : \downarrow\op \to \Set^{\downarrow}$ is equal to the
-composite $$\downarrow\op \xto{\sigma\op} \downarrow \xto{!_{0}} \Set
+The Yoneda embedding $\yo : (\downarrow)\op \to \Set^{\downarrow}$ is equal to the
+composite $$(\downarrow)\op \xto{\sigma\op} \,\downarrow\, \xto{!_{0}} \Set
 \xto{!_{(-)}} \Set^{\downarrow}.$$
@@
 As a corollary, any $\pi : \downarrow \to \Set$ equals the composite
-$$\downarrow \xto{\sigma} \downarrow\op \xto{!_0\op} \Set\op \xto{!_{(-)}\op}
+$$\downarrow \xto{\sigma} (\downarrow)\op \xto{!_0\op} \Set\op \xto{!_{(-)}\op}
 (\Set^{\downarrow})\op \xto{\Set^{\downarrow}(-, \pi)} \Set$$

### 2020-04-08 draft.tex
whatever I did

--- 2020-04-07 draft.tex
@@
 \]
-which preserve the number of elements in each fiber --- we find that such a morphism
+which preserve the number of elements in each row --- we find that such a morphism
 is both a co- and contravariant morphism of bundles. It is well known that such
 \emph{cartesian} morphisms of bundles correspond to \emph{cartesian} natural
-transformations between polynomial functors \jaz{ (cite) } --- those whose naturality
+transformations between polynomial functors (cite) --- those whose naturality
 squares are pullbacks. This is true as well for Dirichlet functors.

### 2020-04-08 draft.tex
acknowledgements
MEs

@@
 \emph{cartesian} morphisms of bundles correspond to \emph{cartesian} natural
-transformations between polynomial functors (cite) --- those whose naturality
+transformations between polynomial functors \cite[Theorem 3.8]{GambinoKock} --- those whose naturality
 squares are pullbacks. This is true as well for Dirichlet functors.
@@
 \begin{acknowledgements}
-Joyal, Kock(!), AFOSR.
+Joyal, Kock(!), AFOSR. David Jaz Myers was supported by the National Science Foundation grant DMS-1652600.
+Spivak acknowledges support from AFOSR grants FA9550-19-1-0113 and FA9550-17-1-0058.
 \end{acknowledgements}
@@
 \end{proof}
-\dis{Shall we say that $\term{ZC}(\pi)$ is also the coefficient of $0^X$ in the extent?}
 We prove a few quick facts we will use later.
@@
   \dom(D) &\sim D(1) \\
-  !_{C} &\sim S \mapsto C^S \\
+  !_{C} &\sim S \mapsto C^S 
 \end{align*}
@@
 \begin{proof}
-  \jaz{Need to find a good citation for this result --- that polynomial functors
-  and cartesian transforms are bundles and cartesian maps (for 1-cats).}
+  \cite[Proposition 3.14]{GambinoKock}.,....
 \end{proof}

### 2020-04-08 draft.tex
thm poly dir cart equiv
removed cosmos

@@
 $\Hom_{\Set\op}(S, !_0\op \circ \sigma) \simeq \Hom_{\Set}(!_0 \circ \sigma\op,
-S)\op$ over $\down$, which we may see by noting that $(-)\op : {\infty}\Cat \to {\infty}\Cat^{\term{co}}$ is a cosmological equivalence and therefore preserves
-comma squares. Furthermore, we have the following equivalence:
+S)\op$ over $\down$. Furthermore, we have the following equivalence:
 \[
@@
 \begin{proof}
-  \cite[Proposition 3.14]{GambinoKock}.,....
+This follows by composing the equivalence of $\Dir_{\ulcorner}$ with
+$\Ha^{\down}$ from Prop
+\ref{prop:set.dirichlet.cartesian.iff.bundle.cartesian} with that of
+\cite[Proposition 3.14]{GambinoKock}, noting that
+$\Set^{\down}_{\ulcorner}$ is the category of $(\ast,\ast)$-polynomials. 
 \end{proof}

### 2020-04-08 draft.tex
another thing
MEs

@@
 where the family of sets $E_b$ depends on $b\in B$. This data is known
-in the computer science literature as a ``container'', but since such an indexed
+in the computer science literature as a ``container'' \cite{Abbott}, but since such an indexed
 family of sets can be represented by as a function
@@
 \begin{acknowledgements}
-Joyal, Kock(!), AFOSR. David Jaz Myers was supported by the National Science Foundation grant DMS-1652600.
-Spivak acknowledges support from AFOSR grants FA9550-19-1-0113 and FA9550-17-1-0058.
+Joyal, Kock(!), AFOSR. David Jaz Myers was supported by the National Science Foundation grant DMS-1652600 and Spivak was supported by AFOSR grants FA9550-19-1-0113 and FA9550-17-1-0058.
 \end{acknowledgements}
@@
 \end{tikzcd}
+\qedhere
 \]
@@
 
-As a corollary, any $\pi : \downarrow \to \Set$ equals the composite
+As a corollary, any $\pi : \downarrow \to \Set$ is naturally isomorphic to the composite
 $$\downarrow \xto{\sigma} (\downarrow)\op \xto{!_0\op} \Set\op \xto{!_{(-)}\op}
@@
 is the right Kan extension formula for $\ext_{\pi} \equiv
-\term{ran}_{!_0} \pi$ --- see Corollary 9.5.3 of \cite{RV:Elements}. Now,
+\term{ran}_{!_0} \pi$. Now,
 $\Hom_{\Set\op}(S, !_0\op \circ \sigma) \simeq \Hom_{\Set}(!_0 \circ \sigma\op,

### 2020-04-08 draft.tex
edits

@@
 represented in terms of their associated bundles. A natural transformation $P
-\to P'$ corresponds to a pair of functions%
-\footnote{We use dependent type syntax, e.g.\ as used in Idris.}
+\to P'$ corresponds to a dependent pair of functions
 \[
@@
 representables:
-$$D(S) := \sum_{b \in B} E_b^S.$$
+$$D(X) := \sum_{b \in B} E_b^X.$$
 
@@
 is a polynomial in the cardinality of $X$. Similarly,
-$$|D(S)| = \sum_{n \in \Nb} |B_n|n^{|S|}$$
-resembles a Dirichlet series in the cardinality of $S$ -- without the usual
+$$|D(X)| = \sum_{n \in \Nb} |B_n|n^{|X|}$$
+resembles a Dirichlet series in the cardinality of $X$ -- without the usual
 negative sign.\footnote{Future work of the first author will recover the
@@
   Or, equivalently, a natural isomorphism of $D$ with the composite
-  $$\Set\op \xto{(\Delta_{!_B})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
+  $$\Set\op \xto{(\Delta_{!_B})\op} (\Set_{/B})\op \xto{\Set_{/B}(-, \pi)} \Set_{/B}
   \xto{\Sigma_{!_B}} \Set.$$
@@
 than that of polynomials. In particular, a Dirichlet functor is determined by
-its action on the terminal morphism $!_0 : 0 \to \ast$ of the empty set. As a corollary, Dirichlet functors form a topos.
+its action on the terminal morphism $!_0 : 0 \to 1$ of the empty set. As a corollary, Dirichlet functors form a topos.
 
@@
 between the topos of bundles and the category of Dirichlet functors, with inverse given by evalutation at
-$!_0 : 0 \to \ast$.
+$!_0 : 0 \to 1$.
 \end{thm}
@@
 \begin{acknowledgements}
-Joyal, Kock(!), AFOSR. David Jaz Myers was supported by the National Science Foundation grant DMS-1652600 and Spivak was supported by AFOSR grants FA9550-19-1-0113 and FA9550-17-1-0058.
+We appreciate helpful comments from Andr\'e Joyal and Joachim Kock on an early draft of this paper.
+Myers was supported by the National Science Foundation grant DMS-1652600, and Spivak was supported by AFOSR grants FA9550-19-1-0113 and FA9550-17-1-0058.
 \end{acknowledgements}
@@
 \begin{proof}
-There is an adjoint triple $\begin{tikzcd} \ast \arrow[r,leftarrow] \arrow[r,
+There is an adjoint triple $\begin{tikzcd} 1 \arrow[r,leftarrow] \arrow[r,
   bend left] \arrow[r, bend right] & \down \end{tikzcd}$. The middle three
@@
   \qquad\text{and}\qquad
-  X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}
+  X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ 1 \end{tikzcd}
   \end{equation}
@@
     \begin{tikzcd}
-    \colim S_i \arrow[r, equals] \arrow[d] & \colim S_i \arrow[d] \\
-    \colim \ast \arrow[r] & \ast 
+    \colim X_i \arrow[r, equals] \arrow[d] & \colim X_i \arrow[d] \\
+    \colim 1 \arrow[r] & 1 
     \end{tikzcd}
@@
   is an isomorphism in $\Set^{\down}$, for which it suffices to show that
-  $\colim \ast$ is terminal. But the colimit of a diagram of terminal objects is the set
+  $\colim 1$ is terminal. But the colimit of a diagram of terminal objects is the set
   of connected components of its indexing category. Since we assumed the
@@
 
-Now we will define the \emph{extent} of a bundle $\pi$ to be the Dirichlet functor $\ext_\pi: \Set\to\Set$ that it
+Now we will define the \emph{extent} of a bundle $\pi$ to be the Dirichlet functor $\ext_\pi: \Set\op\to\Set$ that it
 corresponds to. This sends a bundle
 $\pi : E \to B$ to the functor
-$$X \mapsto \sum_{b \in B} E_b^X.$$
+$$\ext_\pi(X)\coloneqq \sum_{b \in B} E_b^X.$$
 We will, however, give a more abstract definition of the extent, and then
@@
   unique morphism $1\to 0$ in $\Set\op$. Sending a functor $\Set\op\to\Set$ to
-  its precomposition with $!_0\op \sigma$ gives an evaluation functor
-  $$\Set^{\down} \xleftarrow{\ev_{!_0}} \Fun(\Set\op, \Set).$$
+  its precomposition with $!_0\op \circ\sigma$ gives an evaluation functor
+  $$\Fun(\Set\op, \Set)\xto{\ev_{!_0}} \Set^{\down}.$$
   This functor admits a right adjoint by right Kan extension along $!_0\op \circ
-  \sigma : \downarrow \to \Set\op$; we define the
+  \sigma : \down \to \Set\op$; we define the
   \emph{Dirichlet extent} functor $\ext : \Set^{\down} \to \Fun(\Set\op,
@@
   \item The functor
-    $$S \mapsto \sum_{b \in B} E_b^S,$$
+    $$X \mapsto \sum_{b \in B} E_b^X,$$
     or equivalently the composite
-  $$\Set\op \xto{(B^{\ast})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
-  \xto{B_{\ast}} \Set.$$
+  $$\Set\op \xto{(\Delta_B)\op} (\Set_{/B})\op \xto{\Set_{/B}(-, \pi)} \Set_{/B}
+  \xto{\Sigma_B} \Set.$$
 \item The pullback in $\Fun(\Set\op, \Set)$:  
@@
 \item The functor
-  $$S \mapsto \lim(\Hom_{\Set}(!_0, S)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Set)$$
-  where $\Hom_{\Set}(!_0, S)$ is the slice category of $!_0 : \down \to
-  \Set$ over $S$.
+  $$X \mapsto \lim(\Hom_{\Set}(!_0, X)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Set)$$
+  where $\Hom_{\Set}(!_0, X)$ is the comma category of $!_0 : \down \to
+  \Set$ over $X:\ast\to\Set$.
 \item The functor
-  $$S \mapsto \lim(( S^{\triangleleft} )\op \xto{( !^{\triangleleft} )\op}
-  (\ast^{\triangleleft})\op \xto{\sigma\op} \down
+  $$X \mapsto \lim(( X^{\triangleleft} )\op \xto{( !^{\triangleleft} )\op}
+  (1^{\triangleleft})\op \xto{\sigma\op} \down
   \xto{\pi} \Set)$$
@@
 
-First, we note that 
-$$S \mapsto \lim(\Hom_{\Set\op}(S, !_0\op \circ \sigma) \to \down \xto{\pi} \Set)$$
-is the right Kan extension formula for $\ext_{\pi} \equiv
-\term{ran}_{!_0} \pi$. Now,
-$\Hom_{\Set\op}(S, !_0\op \circ \sigma) \simeq \Hom_{\Set}(!_0 \circ \sigma\op,
-S)\op$ over $\down$. Furthermore, we have the following equivalence:
+First, we note that the conical limit formula for $\ext_{\pi} \equiv
+\term{ran}_{!_0} \pi$ as a right Kan extension says
+$$\ext_\pi(X)= \lim(\Hom_{\Set\op}(X, !_0\op \circ \sigma) \to \down \xto{\pi} \Set).$$
+Now,
+$\Hom_{\Set\op}(X, !_0\op \circ \sigma) \simeq \Hom_{\Set}(!_0 \circ \sigma\op,
+X)\op$ over $\down$. Furthermore, we have the following equivalence:
 \[
@@
 \begin{tikzcd}
-{\Hom_{\Set}(!_0 \circ \sigma\op, S)\op} \arrow[d, "\sim"'] \arrow[r] & \down \arrow[d, "\sigma"] \\
-{\Hom_{\Set}(!_0, S)\op} \arrow[r]                                    & \down\op                 
+{\Hom_{\Set}(!_0 \circ \sigma\op, X)\op} \arrow[d, "\sim"'] \arrow[r] & \down \arrow[d, "\sigma"] \\
+{\Hom_{\Set}(!_0, X)\op} \arrow[r]                                    & \down\op                 
 \end{tikzcd}
@@
 and therefore we may equivalently calculate this limit as 
-$$\lim(\Hom_{\Set}(!_0, S)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Set).$$
+$$\lim(\Hom_{\Set}(!_0, X)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Set).$$
 This gives us the equivalence between (1) and (5).
 
-Now, the comma category $\Hom_{\Set}(!_0, S)$ simply adjoins an initial object
-to (the discrete category) $S$. Therefore, we find that (5) and (6) are equivalent.
+The comma category $\Hom_{\Set}(!_0, X)$ simply adjoins an initial object
+to (the discrete category) $X$. Therefore, we find that (5) and (6) are equivalent.
 
-Now, we note that every set $S$ is the colimit of the diagram $S^{\triangleleft}
-\xto{\ast^{\triangleleft}}\down \xto{!_0} \Set$, namely:
+Every set $X$ is the colimit of the diagram $X^{\triangleleft}
+\xto{1^{\triangleleft}}\down \xto{!_0} \Set$, namely:
 \[
@@
 \begin{tikzcd}
-              &              & S                                               &              &               \\
+              &              & X                                               &              &               \\
 1 \arrow[rru] & 1 \arrow[ru] & \cdots                                          & 1 \arrow[lu] & 1 \arrow[llu] \\
@@
 \begin{align*}
-  \Set^{\down}(!_S, \pi) &= \Set^{\down}(!_{\colim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft} \xto{!_0} \Set)}, \pi) \\
-  &\simeq \Set^{\down}(\colim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft} \xto{!_0} \Set \xto{!_{(-)}} \Set^{\down}), \pi)\\
-&\simeq \lim((S^{\down})\op \xto{(!^{\triangleleft})\op} (\ast^{\triangleleft})\op \xto{!_0\op} \Set\op \xto{!_{(-)}} (\Set^{\down})\op \xto{\Set^{\down}(-, \pi)} \Set) \\
-&\simeq \lim((S^{\down})\op \xto{(!^{\triangleleft})\op} (\ast^{\triangleleft})\op \xto{\sigma\op} \down \xto{\pi} \Set).
+  \Set^{\down}(!_X, \pi) &= \Set^{\down}(!_{\colim(X^{\triangleleft} \xto{!^{\triangleleft}} 1^{\triangleleft} \xto{!_0} \Set)}, \pi) \\
+  &\simeq \Set^{\down}(\colim(X^{\triangleleft} \xto{!^{\triangleleft}} 1^{\triangleleft} \xto{!_0} \Set \xto{!_{(-)}} \Set^{\down}), \pi)\\
+&\simeq \lim((X^{\triangleleft})\op \xto{(!^{\triangleleft})\op} (1^{\triangleleft})\op \xto{!_0\op} \Set\op \xto{!_{(-)}\op} (\Set^{\down})\op \xto{\Set^{\down}(-, \pi)} \Set) \\
+&\simeq \lim((X^{\triangleleft})\op \xto{(!^{\triangleleft})\op} (1^{\triangleleft})\op \xto{\sigma\op} \down \xto{\pi} \Set).
 \end{align*}
@@
 
-Finally, we note that the set $\Set^{\down}(!_S, \pi)$ is naturally
-isomorphic to the set $\sum_{b \in B} E_b^S$, letting us identify (4) with (2).
+Finally, we note that the set $\Set^{\down}(!_X, \pi)$ is naturally
+isomorphic to the set $\sum_{b \in B} E_b^X$, letting us identify (4) with (2).
 \end{proof}
@@
 Since $!_0 : \down \to \Set\op$ is fully faithful, the counit of the
-$\ev_{!_0} \vdash \ext$ adjunction --- which is the universal cell defining the
-right Kan extension --- is an isomorphism.
+$\ev_{!_0} \vdash \ext$ adjunction, the universal cell defining the
+right Kan extension $\ext_-$, is an isomorphism.
+Thus $\ext$ is fully faithful.
+In what follows we show that a functor is Dirichlet---preserves connected limits---if and only if it is the extent of a bundle, proving the equivalence of $\Dir$ with $\Set^{\down}$.
 
-Now, we show that a functor is Dirichlet if and only if it is the extent of a bundle. If $D$ is
-the extent of a bundle, then by Prop \ref{prop:set.characterizing.extent}, $D$ is naturally
-isomorphic to the restricted representable $\Set^{\down}(!_{(-)})$. By Lemma
+If $D$ is
+the extent of a bundle $\pi$, then by Prop \ref{prop:set.characterizing.extent}, $D$ is naturally
+isomorphic to the restricted representable $\Set^{\down}(!_{(-)},\pi)$. By Lemma
 \ref{lem:bang.preserves.connected.colimits}, this sends connected colimits in $\Set$ to
@@
 \ref{prop:set.characterizing.extent}, 
-  $$\ext_{D!_0}(S) = \lim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft}
+  $$\ext_{D!_0}(X) = \lim(X^{\triangleleft} \xto{!^{\triangleleft}} 1^{\triangleleft}
   \xto{D!_0} \Set).$$
-
-Every set $S$ is the connected colimit of the diagram $S^{\triangleleft} \to
+  Every set $X$ is the connected colimit of the diagram $X^{\triangleleft} \to
 \down \xto{!_0} \Set$, and therefore if $D$ preserves this limit, then
-$D(S)$ is precisely the above limit $\ext_{D!_0}(S)$.
+$D(X)$ is precisely the above limit $\ext_{D!_0}(X)$.
 \end{proof}
@@
 \begin{rmk}
-The six adjoints of Proposition \ref{prop:adjoint.sextuple} correspond, under
-the equivalence of Theorem \ref{thm:dirichlet.set.characterization}, to
+The six adjoints of \cref{prop:adjoint.sextuple} correspond, under
+the equivalence of \cref{thm:dirichlet.set.characterization}, to
 \begin{align*}
-  \term{ZC}(D) &\sim \mbox{the coefficient of $0^S$ in $D$.}\\
-  !^{C} &\sim S \mapsto C \times 0^S \\
+  \term{ZC}(D) &\sim \mbox{the coefficient of $0^X$ in $D$.}\\
+  !^{C} &\sim X \mapsto C \times 0^X \\
   \cod(D) &\sim D(0) \\
-  \const(C) &\sim S \mapsto C \\
+  \const(C) &\sim X \mapsto C \\
   \dom(D) &\sim D(1) \\
-  !_{C} &\sim S \mapsto C^S 
+  !_{C} &\sim X \mapsto C^X 
 \end{align*}
-In particular, $!_{(-)}$ corresponds to the Yoneda embedding.
+\dis{If we're using \cref{thm:dirichlet.set.characterization}, shouldn't we be thinking in terms of bundles?} In particular, $!_{(-)}$ corresponds to the Yoneda embedding.
 \end{rmk}
@@
 functors. We will show that the category of Dirichlet functors and cartesian
-transfromations are equivalent to the category of Polynomial functors and
+transfromations is equivalent to the category of polynomial functors and
 cartesian transformations.
 
-\begin{prop}
+\begin{prop}\label{prop:set.dirichlet.cartesian.iff.bundle.cartesian}
 A natural transformation $\phi : D \to D'$ between Dirichlet functors is
@@
 
-As a corllary, the equivalence $\Dir \simeq \Set^{\down}$ restricts to an
+As a corollary, the equivalence $\Dir \simeq \Set^{\down}$ restricts to an
 equivalence
@@
 \begin{proof}
-We want to show that for any $f\colon D\to D'$ the square
+We want to show that for any $f\colon D\to D'$, the square
 \begin{equation}\label{eqn.cart1}
@@
 $D(X)\cong\Set^{\down}(!_X, D!_0)$ from
-\ref{prop:set.characterizing.extent}, which allows us to identify Diagram
-\ref{eqn.cart2} with
+\cref{prop:set.characterizing.extent}, which allows us to identify Diagram
+\eqref{eqn.cart2} with
 \begin{equation}\label{eqn.cart3}
 \begin{tikzcd}
- \Set^{\down}(!_{X'}, D!_0)     \ar[r, "f_{!_0,\ast}"]\ar[d, "!_g^{\ast}"']& \Set^{\down}(!_{X'}, D'!_0)
-  \ar[d, "!_{g}^{\ast}"]\\
-  \Set^{\down}(!_{X}, D!_0)\ar[r, "f_{!_0, \ast}"']&
+ \Set^{\down}(!_{X'}, D!_0)     \ar[r, "f_{!_0,1}"]\ar[d, "!_g^{1}"']& \Set^{\down}(!_{X'}, D'!_0)
+  \ar[d, "!_{g}^{1}"]\\
+  \Set^{\down}(!_{X}, D!_0)\ar[r, "f_{!_0, 1}"']&
  \Set^{\down}(!_X, D'!_0) 
@@
 
-The square in Diagram \ref{eqn.cart1} is a
-special case of that in Diagram \ref{eqn.cart2}, namely for $g\coloneqq !_0$;
+The square in Diagram \eqref{eqn.cart1} is a
+special case of that in Diagram \eqref{eqn.cart2}, namely for $g\coloneqq !_0$;
 this establishes the only-if direction.
 
-To complete the proof, suppose that Diagram \ref{eqn.cart1} is a pullback, take an arbitrary $g\colon X\to X'$, and suppose given a commutative solid-arrow diagram as shown:
+To complete the proof, suppose that Diagram \eqref{eqn.cart1} is a pullback, take an arbitrary $g\colon X\to X'$, and suppose given a commutative solid-arrow diagram as shown:
 \[
@@
 \]
-We can interpret the statement that Diagram \ref{eqn.cart3} is a pullback as
+We can interpret the statement that Diagram \eqref{eqn.cart3} is a pullback as
 saying that there are unique dotted arrows making the diagram commute.
@@
 This follows by composing the equivalence of $\Dir_{\ulcorner}$ with
-$\Ha^{\down}$ from Prop
-\ref{prop:set.dirichlet.cartesian.iff.bundle.cartesian} with that of
+$\Set^{\down}$ from
+\cref{prop:set.dirichlet.cartesian.iff.bundle.cartesian} with that of
 \cite[Proposition 3.14]{GambinoKock}, noting that
-$\Set^{\down}_{\ulcorner}$ is the category of $(\ast,\ast)$-polynomials. 
+$\Set^{\down}_{\ulcorner}$ is the category of $(1,1)$-polynomials. 
 \end{proof}
@@
   Let $D$ be a Dirichlet functor. Then the category
-  $\Dir_{/_{\ulcorner} D}$
+  $\Dir_{\ulcorner/D}$
   of Dirichlet functors with a cartesian map to $D$ is a topos.
@@
 By Theorem \ref{thm:set.poly.cart.equiv.dir.cart}, this category is equivalent
-to $\type{Poly}_{/_{\ulcorner} P}$ for a polynomial $P$. But this is a topos as
+to $\type{Poly}_{\ulcorner/P}$ for a polynomial $P$. But this is a topos as
 observed in Remark 2.6.2 of \cite{GHK:Analytic.Monads}.
@@
 Now, since $\Dir$ is a topos, so is $\Dir_{/D}$. And, as we saw above,
-$\Dir_{/_{\ulcorner} D}$ is a topos as well. What is the relationship between
-$\Dir_{/D}$ and $\Dir_{/_{\ulcorner} D}$?
+$\Dir_{\ulcorner/D}$ is a topos as well. What is the relationship between
+$\Dir_{/D}$ and $\Dir_{\ulcorner/D}$?
 
 We will show that $\Dir_{/_{\ulcorner} D}$ is a subtopos of $\Dir_{/D}$ with the
-lex localization given by the vertical / cartesian factorization system on $\Set^{\down}$.
+lex localization (``inverse image functor'') given by the vertical / cartesian factorization system on $\Set^{\down}$.
 
@@
   For any $\pi : \down \to \Set$, we have a subtopos inclusion
-  $$\Set^{\down}_{/_{\ulcorner} \pi} \hookrightarrow \Set^{\down}_{/\pi}$$
-
-  with lex localization given by:
+  $$\Set^{\down}_{\ulcorner/ \pi} \hookrightarrow \Set^{\down}_{/\pi}$$
+  with lex localization given by vertical-cartesian factorization:
   \[
@@
   \]
-  As a corollary, $\Dir_{/_{\ulcorner} D} \hookrightarrow \Dir_{D}$ is a
+  As a corollary, $\Dir_{\ulcorner/D} \hookrightarrow \Dir_{D}$ is a
   subtopos inclusion.
@@
 That this is lex follows quickly from the fact that taking pullbacks commutes
-with taking limits. 
+with taking (finite) limits. 
 \end{proof}

### 2020-04-08 draft.tex
small edits

--- 2020-04-08 draft.tex
@@
 We will show that $\Dir_{/_{\ulcorner} D}$ is a subtopos of $\Dir_{/D}$ with the
-lex localization given by the vertical / cartesian factorization system on $\Set^{\down}$.
+left exact left adjoint to the inclusion given by the vertical / cartesian factorization system on $\Set^{\down}$.
 
@@
 
-  with lex localization given by:
+  with left exact left adjoint given by the vertical / cartesian factorization system:
   \[

### 2020-04-08 draft.tex

--- 2020-04-08 draft.tex
@@
 We will show that $\Dir_{/_{\ulcorner} D}$ is a subtopos of $\Dir_{/D}$ with the
-lex localization (``inverse image functor'') given by the vertical / cartesian factorization system on $\Set^{\down}$.
+left exact left adjoint to the inclusion given by the vertical / cartesian factorization system on $\Set^{\down}$.
 
@@
   For any $\pi : \down \to \Set$, we have a subtopos inclusion
-  $$\Set^{\down}_{\ulcorner/ \pi} \hookrightarrow \Set^{\down}_{/\pi}$$
-  with lex localization given by vertical-cartesian factorization:
+  $$\Set^{\down}_{/_{\ulcorner} \pi} \hookrightarrow \Set^{\down}_{/\pi}$$
+
+  with left exact left adjoint given by the vertical / cartesian factorization system:
   \[

### 2020-04-08 draft.tex
latest

@@
 where the family of sets $E_b$ depends on $b\in B$. This data is known
-in the computer science literature as a ``container'' \cite{Abbott}, but since such an indexed
+in the computer science literature as a ``container'' \cites{abbott2003categories}{abbott2005containers}{abbot2003categoriesthesis}, but since such an indexed
 family of sets can be represented by as a function
@@
 
-\begin{thm}[cite]
+\begin{thm}[Theorem 2.17 of \cite{kock2012polynomial}]
 The category of polynomial functors and natural transformations is equivalent to
@@
 say that a functor is polynomial have contravariant analogues.
-\begin{thm}[cite]\label{thm:polynomial.set.characterization}
+\begin{thm}[See discussion in 1.18 of \cite{kock2012polynomial}]\label{thm:polynomial.set.characterization}
   Let $P : \Set \to \Set$ be a functor. Then the following are equivalent.
@@
 \emph{cartesian} morphisms of bundles correspond to \emph{cartesian} natural
-transformations between polynomial functors \cite[Theorem 3.8]{GambinoKock} --- those whose naturality
+transformations between polynomial functors \cite[Theorem 3.8]{kock2012polynomial} --- those whose naturality
 squares are pullbacks. This is true as well for Dirichlet functors.
@@
 \begin{defn}
-  We let $\downarrow$ be the walking arrow --- the category $\term{dom} \to
-  \term{cod}$ consisting of a single morphism. We denote by $\sigma : \downarrow
-  \to (\downarrow)\op$ the self-dualizing isomorphism of $\downarrow$, and note
+  We let $\down$ be the walking arrow --- the category $\term{dom} \to
+  \term{cod}$ consisting of a single morphism. We denote by $\sigma : \down
+  \to (\downarrow)\op$ the self-dualizing isomorphism of $\down$, and note
   that $\sigma\inv = \sigma\op$.
@@
 The existence of the final adjoint can be deduced from the fact that $!^{(-)}$ preserves all
-limits. It sends a bundle $\pi : E \to B$ to the largest subset $\term{ZC}(B)$ of $B$ for
+limits. It sends a bundle $\pi : E \to B$ to the largest subset $\term{ZC}(\pi)$ of $B$ for
 which the following square is a pullback
@@
 \begin{rmk}
+ Since polynomial functors preserve connected limits, the composite $P \circ D$
+ of a polynomial functor after a Dirichlet functor is Dirichlet. On the other
+ hand, the composite $D' \circ D\op$ of two Dirichlet functors does not in
+ general preserve connected limits, since $D\op$ sends connected colimits in
+ $\Set$ to connected colimits in $\Set\op$, and $D'$ does not necessarily
+ preserve these. Furthermore, composites of Dirichlet functors are not in
+ general accessible.   
+\end{rmk}
+
+\begin{rmk}
 The six adjoints of \cref{prop:adjoint.sextuple} correspond, under
@@
 \begin{align*}
-  \term{ZC}(D) &\sim \mbox{the coefficient of $0^X$ in $D$.}\\
-  !^{C} &\sim X \mapsto C \times 0^X \\
-  \cod(D) &\sim D(0) \\
-  \const(C) &\sim X \mapsto C \\
-  \dom(D) &\sim D(1) \\
-  !_{C} &\sim X \mapsto C^X 
+  \term{ZC}(D!_0) &\cong \mbox{the coefficient of $0^X$ in $D$.}\\
+  \ext(!^{C}) &\cong X \mapsto C \times 0^X \\
+  \cod(D!_0) &\cong D(0) \\
+  \ext( \const(C) ) &\cong X \mapsto C \\
+  \dom(D!_0) &\cong D(1) \\
+  \ext( !_{C} ) &\cong X \mapsto C^X 
 \end{align*}
-\dis{If we're using \cref{thm:dirichlet.set.characterization}, shouldn't we be thinking in terms of bundles?} In particular, $!_{(-)}$ corresponds to the Yoneda embedding.
+ In particular, $!_{(-)}$ corresponds to the Yoneda embedding.
 \end{rmk}
@@
 \cref{prop:set.dirichlet.cartesian.iff.bundle.cartesian} with that of
-\cite[Proposition 3.14]{GambinoKock}, noting that
+\cite[Proposition 3.14]{kock2012polynomial}, noting that
 $\Set^{\down}_{\ulcorner}$ is the category of $(1,1)$-polynomials. 
@@
 to $\type{Poly}_{\ulcorner/P}$ for a polynomial $P$. But this is a topos as
-observed in Remark 2.6.2 of \cite{GHK:Analytic.Monads}.
+observed in \cite[Remark 2.6.2]{GHK:Analytic.Monads}.
 \end{proof}
@@
 \begin{proof}
-We have displayed both the action of the left localization and its unit. The
+We have displayed both the action of the left adjoint and its unit --- the
+universal map into the pullback. The
 counit is always an isomorphism since pullbacks are unique up to unique
